#### Stimuli distinctiveness
```{r, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.show='hide'}
##################################################################################################################
##  Exp4 Hits:                                                                                                  ##
##################################################################################################################
##  Two-way mixed ANOVA:
    exp4__prop.hit.aov <- afex::aov_ez('id', 'prop.hit', fun_aggregate = mean, exp4__prop.hit, 
                                       between = "resp_option", within = 'stim',
                                       anova_table=list(correction = "none", es = "ges"))
##  Mauchlys test of sphericity:
    exp4__prop.hit.aov__sphericity <- test_sphericity(exp4__prop.hit.aov)
##  Assumption of sphericity violated (p<.05), so apply Greenhouse-Geisser correction:
    exp4__prop.hit.aov <- afex::aov_ez('id', 'prop.hit', fun_aggregate = mean, exp4__prop.hit, 
                                       between = "resp_option", within = 'stim',
                                       anova_table=list(correction = "GG", es = "ges"))
##-----------------------------------------------------------------------------------------------------------------
##  No significant main effect of RESPONSE OPTION.
##-----------------------------------------------------------------------------------------------------------------
##  Significant main effect of STIMULI FORMAT, so perform paired contrasts:
    exp4__prop.hit__pairwise__stim.format <- exp4__prop.hit %>% 
        pairwise_t_test(prop.hit ~ stim, paired = TRUE, p.adjust.method = "bonferroni")
##  Calculate effect size:      
    exp4__prop.hit__pairwise__stim.format__eff.size <- exp4__prop.hit %>% 
        rstatix::cohens_d(prop.hit ~ stim, paired = TRUE, ci = TRUE, conf.level = 0.95)   
##  Format for report (colour photos vs. words t-test):
    temp <- exp4__prop.hit__pairwise__stim.format %>% filter(group1 == "col.photo" & group2 == "word")
    exp4__prop.hit__ttest__col.photo.vs.word <- str_c(ttest.writeup(temp), "; *d* = ", 
        round(as.vector(exp4__prop.hit__pairwise__stim.format__eff.size %>% 
                          filter(group1 == "col.photo" & group2 == "word") %>% pull(effsize)), 2),
        ", 95% CI [", 
        exp4__prop.hit__pairwise__stim.format__eff.size %>%
            filter(group1 == "col.photo" & group2 == "word") %>% pull(conf.low), ", ",
                    exp4__prop.hit__pairwise__stim.format__eff.size %>%
                        filter(group1 == "col.photo" & group2 == "word") %>% pull(conf.high), "]")
    
##  Format for report (colour drawings vs. words t-test):
    temp <- exp4__prop.hit__pairwise__stim.format %>% filter(group1 == "col.drawing" & group2 == "word")
    exp4__prop.hit__ttest__col.drawing.vs.word <- str_c(ttest.writeup(temp), "; *d* = ", 
        round(as.vector(exp4__prop.hit__pairwise__stim.format__eff.size %>% 
                          filter(group1 == "col.drawing" & group2 == "word") %>% pull(effsize)), 2),
        ", 95% CI [", 
        exp4__prop.hit__pairwise__stim.format__eff.size %>%
            filter(group1 == "col.drawing" & group2 == "word") %>% pull(conf.low), ", ",
                    exp4__prop.hit__pairwise__stim.format__eff.size %>%
                        filter(group1 == "col.drawing" & group2 == "word") %>% pull(conf.high), "]")                                                         
##  Format for report (colour drawings vs. colour photos t-test):
    temp <- exp4__prop.hit__pairwise__stim.format %>% filter(group1 == "col.drawing" & group2 == "col.photo")
    exp4__prop.hit__ttest__col.photo.vs.col.drawing <- str_c(ttest.writeup(temp), "; *d* = ", 
        round(as.vector(exp4__prop.hit__pairwise__stim.format__eff.size %>% 
                          filter(group1 == "col.drawing" & group2 == "col.photo") %>% pull(effsize)), 2),
        ", 95% CI [", 
        exp4__prop.hit__pairwise__stim.format__eff.size %>%
            filter(group1 == "col.drawing" & group2 == "col.photo") %>% pull(conf.low), ", ",
                    exp4__prop.hit__pairwise__stim.format__eff.size %>%
                        filter(group1 == "col.drawing" & group2 == "col.photo") %>% pull(conf.high), "]")         
##-----------------------------------------------------------------------------------------------------------------
##  Get all means:
    exp4__prop.hit__stim.means <- as.tibble(summary(emmeans(exp4__prop.hit.aov, ~stim)))
    exp4__prop.hit__resp.option.means <- as.tibble(summary(emmeans(exp4__prop.hit.aov, ~resp_option)))

##################################################################################################################
##  Exp4 Prop FAs:                                                                                             ##
##################################################################################################################
##  Two-way mixed ANOVA:
    exp4__prop.FA.aov <- afex::aov_ez('id', 'prop.FA', fun_aggregate = mean, exp4__prop.FA, 
                                       between = "resp_option", within = 'stim',
                                       anova_table=list(correction = "none", es = "ges"))
##  Mauchlys test of sphericity:
    exp4__prop.FA.aov__sphericity <- test_sphericity(exp4__prop.FA.aov)
##  Assumption of sphericity violated (p<.05), so apply Greenhouse-Geisser correction:
    exp4__prop.FA.aov <- afex::aov_ez('id', 'prop.FA', fun_aggregate = mean, exp4__prop.FA, 
                                       between = "resp_option", within = 'stim',
                                       anova_table=list(correction = "GG", es = "ges"))
##-----------------------------------------------------------------------------------------------------------------
##  Significant main effect of RESPONSE OPTION, so first check if variances are equal using Levene's test:
    exp4__prop.FA__levene.test__rfg.rfbg <- exp4__prop.FA %>% leveneTest(prop.FA ~ resp_option, data = .)
##  Levene's test significant (variances not equal), so perform corrected Welch two-sample t-test: 
    exp4__prop.FA__ttest__rfg.rfbg <- exp4__prop.FA %>%
        t_test(prop.FA ~ resp_option, paired = FALSE, data = ., var.equal = FALSE)
##  Calculate effect size:
    exp4__prop.FA__ttest__rfg.rfbg__eff.size <- exp4__prop.FA %>% 
        rstatix::cohens_d(prop.FA ~ resp_option, var.equal = FALSE, paired = FALSE, ci = TRUE, conf.level = 0.95)  ##-----------------------------------------------------------------------------------------------------------------
##  No significant main effect of RESPONSE OPTION.
##----------------------------------------------------------------------------------------------------------------- ##  Significant main effect of STIMULI FORMAT, so perform paired contrasts:
    exp4__prop.FA__pairwise__stim.format <- exp4__prop.FA %>% 
        pairwise_t_test(prop.FA ~ stim, paired = TRUE, p.adjust.method = "bonferroni")
##  Calculate effect size:      
    exp4__prop.FA__pairwise__stim.format__eff.size <- exp4__prop.FA %>% 
        rstatix::cohens_d(prop.FA ~ stim, paired = TRUE, ci = TRUE, conf.level = 0.95)       
    
##  Format for report (colour photos vs. words t-test):    
    temp <- exp4__prop.FA__pairwise__stim.format %>% filter(group1 == "col.photo" & group2 == "word")
    exp4__prop.FA__ttest__col.photo.vs.word <- str_c(ttest.writeup(temp), "; *d* = ", 
        round(as.vector(exp4__prop.FA__pairwise__stim.format__eff.size %>% 
                          filter(group1 == "col.photo" & group2 == "word") %>% pull(effsize)), 2),
        ", 95% CI [", 
        exp4__prop.FA__pairwise__stim.format__eff.size %>%
            filter(group1 == "col.photo" & group2 == "word") %>% pull(conf.low), ", ",
                    exp4__prop.FA__pairwise__stim.format__eff.size %>%
                        filter(group1 == "col.photo" & group2 == "word") %>% pull(conf.high), "]")                                                         
##  Format for report (colour drawings vs. words t-test):
    temp <- exp4__prop.FA__pairwise__stim.format %>% filter(group1 == "col.drawing" & group2 == "word")
    exp4__prop.FA__ttest__col.drawing.vs.word <- str_c(ttest.writeup(temp), "; *d* = ", 
        round(as.vector(exp4__prop.FA__pairwise__stim.format__eff.size %>% 
                          filter(group1 == "col.drawing" & group2 == "word") %>% pull(effsize)), 2),
        ", 95% CI [", 
        exp4__prop.FA__pairwise__stim.format__eff.size %>%
            filter(group1 == "col.drawing" & group2 == "word") %>% pull(conf.low), ", ",
                    exp4__prop.FA__pairwise__stim.format__eff.size %>%
                        filter(group1 == "col.drawing" & group2 == "word") %>% pull(conf.high), "]")                                                           
##  Format for report (colour drawings vs. colour photos t-test):
    temp <- exp4__prop.FA__pairwise__stim.format %>% filter(group1 == "col.drawing" & group2 == "col.photo")
    exp4__prop.FA__ttest__col.photo.vs.col.drawing <- str_c(ttest.writeup(temp), "; *d* = ", 
        round(as.vector(exp4__prop.FA__pairwise__stim.format__eff.size %>% 
                          filter(group1 == "col.drawing" & group2 == "col.photo") %>% pull(effsize)), 2),
        ", 95% CI [", 
        exp4__prop.FA__pairwise__stim.format__eff.size %>%
            filter(group1 == "col.drawing" & group2 == "col.photo") %>% pull(conf.low), ", ",
                    exp4__prop.FA__pairwise__stim.format__eff.size %>%
                        filter(group1 == "col.drawing" & group2 == "col.photo") %>% pull(conf.high), "]")         
##-----------------------------------------------------------------------------------------------------------------     ##  Get all means:
    exp4__prop.FA__stim.means <- as.tibble(summary(emmeans(exp4__prop.FA.aov, ~stim)))
    exp4__prop.FA__resp.option.means <- as.tibble(summary(emmeans(exp4__prop.FA.aov, ~resp_option)))

##################################################################################################################
##  Exp4 d':                                                                                                    ##
##################################################################################################################
##  Two-way mixed ANOVA:
    exp4__d.prime.aov <- afex::aov_ez('id', 'd.prime', fun_aggregate = mean, exp4__d.prime, 
                                       between = "resp_option", within = 'stim',
                                       anova_table=list(correction = "none", es = "ges"))
##  Mauchlys test of sphericity:
    exp4__d.prime.aov__sphericity <- test_sphericity(exp4__d.prime.aov)
##  Assumption of sphericity NOT violated (p>.05), so Greenhouse-Geisser correction NOT applied.
##-----------------------------------------------------------------------------------------------------------------
##  No significant main effect of RESPONSE OPTION.
##-----------------------------------------------------------------------------------------------------------------
##  Significant main effect of STIMULI FORMAT, so perform paired contrasts:
    exp4__d.prime__pairwise__stim.format <- exp4__d.prime %>% 
        pairwise_t_test(d.prime ~ stim, paired = TRUE, p.adjust.method = "bonferroni")
##  Calculate effect size:      
    exp4__d.prime__pairwise__stim.format__eff.size <- exp4__d.prime %>% 
        rstatix::cohens_d(d.prime ~ stim, paired = TRUE, ci = TRUE, conf.level = 0.95)       
    
##  Format for report (colour photos vs. words t-test):    
    temp <- exp4__d.prime__pairwise__stim.format %>% filter(group1 == "col.photo" & group2 == "word")
    exp4__d.prime__ttest__col.photo.vs.word <- str_c(ttest.writeup(temp), "; *d* = ", 
        round(as.vector(exp4__d.prime__pairwise__stim.format__eff.size %>% 
                          filter(group1 == "col.photo" & group2 == "word") %>% pull(effsize)), 2),
        ", 95% CI [", 
        exp4__d.prime__pairwise__stim.format__eff.size %>%
            filter(group1 == "col.photo" & group2 == "word") %>% pull(conf.low), ", ",
                    exp4__d.prime__pairwise__stim.format__eff.size %>%
                        filter(group1 == "col.photo" & group2 == "word") %>% pull(conf.high), "]")                                                         
##  Format for report (colour drawings vs. words t-test):
    temp <- exp4__d.prime__pairwise__stim.format %>% filter(group1 == "col.drawing" & group2 == "word")
    exp4__d.prime__ttest__col.drawing.vs.word <- str_c(ttest.writeup(temp), "; *d* = ", 
        round(as.vector(exp4__d.prime__pairwise__stim.format__eff.size %>% 
                          filter(group1 == "col.drawing" & group2 == "word") %>% pull(effsize)), 2),
        ", 95% CI [", 
        exp4__d.prime__pairwise__stim.format__eff.size %>%
            filter(group1 == "col.drawing" & group2 == "word") %>% pull(conf.low), ", ",
                    exp4__d.prime__pairwise__stim.format__eff.size %>%
                        filter(group1 == "col.drawing" & group2 == "word") %>% pull(conf.high), "]")                                                           
##  Format for report (colour drawings vs. colour photos t-test):
    temp <- exp4__d.prime__pairwise__stim.format %>% filter(group1 == "col.drawing" & group2 == "col.photo")
    exp4__d.prime__ttest__col.photo.vs.col.drawing <- str_c(ttest.writeup(temp), "; *d* = ", 
        round(as.vector(exp4__d.prime__pairwise__stim.format__eff.size %>% 
                          filter(group1 == "col.drawing" & group2 == "col.photo") %>% pull(effsize)), 2),
        ", 95% CI [", 
        exp4__d.prime__pairwise__stim.format__eff.size %>%
            filter(group1 == "col.drawing" & group2 == "col.photo") %>% pull(conf.low), ", ",
                    exp4__d.prime__pairwise__stim.format__eff.size %>%
                        filter(group1 == "col.drawing" & group2 == "col.photo") %>% pull(conf.high), "]")
##  Get all means:
    exp4__d.prime__stim.means <- as.tibble(summary(emmeans(exp4__d.prime.aov, ~stim)))
    exp4__d.prime__resp.option.means <- as.tibble(summary(emmeans(exp4__d.prime.aov, ~resp_option)))
    
##################################################################################################################
##  exp4 Hits, FAs, d' table:                                                                                   ##
##################################################################################################################
    exp4__prop.hit.FA.d.prime__table <- tribble(
        ~"Stim", ~Hits,  ~FAs, ~"d'",
        "Words",
            round(exp4__prop.hit__stim.means %>% filter(stim == "word") %>% pull(emmean),2),
            round(exp4__prop.FA__stim.means %>% filter(stim == "word") %>% pull(emmean),2),
            round(exp4__d.prime__stim.means %>% filter(stim == "word") %>% pull(emmean),2),
        "Colour drawings",  
            round(exp4__prop.hit__stim.means %>% filter(stim == "col.drawing") %>% pull(emmean),2),
            round(exp4__prop.FA__stim.means %>% filter(stim == "col.drawing") %>% pull(emmean),2),
            round(exp4__d.prime__stim.means %>% filter(stim == "col.drawing") %>% pull(emmean),2),
        "Colour photographs",  
            round(exp4__prop.hit__stim.means %>% filter(stim == "col.photo") %>% pull(emmean),2),
            round(exp4__prop.FA__stim.means %>% filter(stim == "col.photo") %>% pull(emmean),2),
            round(exp4__d.prime__stim.means %>% filter(stim == "col.photo") %>% pull(emmean),2),
        "RFG",
            round(exp4__prop.hit__resp.option.means %>% filter(resp_option == "RFG") %>% pull(emmean),2),
            round(exp4__prop.FA__resp.option.means %>% filter(resp_option == "RFG") %>% pull(emmean),2),
            round(exp4__d.prime__resp.option.means %>% filter(resp_option == "RFG") %>% pull(emmean),2),
        "RFBG",
            round(exp4__prop.hit__resp.option.means %>% filter(resp_option == "RFBG") %>% pull(emmean),2),
            round(exp4__prop.FA__resp.option.means %>% filter(resp_option == "RFBG") %>% pull(emmean),2),
            round(exp4__d.prime__resp.option.means %>% filter(resp_option == "RFBG") %>% pull(emmean),2)) %>%
        column_to_rownames(var = "Stim")
```

```{r echo=FALSE, results = FALSE, cache=FALSE}
table_numbering(name = "exp4__prop.hit.FA.d.prime__table", caption = "Mean proportion of hits, FAs, and mean *d'* scores, by stimuli format and response option condition.")
```

&nbsp;
`r table_numbering("exp4__prop.hit.FA.d.prime__table")`
```{r, echo=FALSE, cache=TRUE}
    exp4__prop.hit.FA.d.prime__table %>%
        kable("latex", booktabs = T) %>%
        kable_styling(latex_options = "hold_position") %>%
        pack_rows("Stimuli format", 1, 3) %>%
        pack_rows("Response option", 4, 5) %>%
        column_spec(1, width = "4cm")
```

Mean proportions of hits and FAs, and mean *d'* scores are presented in `r table_numbering("exp3__prop.hit.FA.d.prime__table", display = "cite")`. Results from the ANOVA on the mean proportion of hits showed a significant main effect of stimuli format, `r apa::anova_apa(exp4__prop.hit.aov, effect = "stim", format = "rmarkdown", print = FALSE)`. Paired samples t-tests showed that colour photographs (*M*= `r round(exp4__prop.hit__stim.means %>% filter(stim == "col.photo") %>% pull(emmean),2)`) produced a significantly higher proportion of hits than both words (*M*= `r round(exp4__prop.hit__stim.means %>% filter(stim == "word") %>% pull(emmean),2)`), `r exp4__prop.hit__ttest__col.photo.vs.word`, and colour drawings (*M*= `r round(exp4__prop.hit__stim.means %>% filter(stim == "col.drawing") %>% pull(emmean),2)`), `r exp4__prop.hit__ttest__col.photo.vs.col.drawing`. A significantly higher proportion of hits was also evident for colour drawings (*M*= `r round(exp4__prop.hit__stim.means %>% filter(stim == "col.drawing") %>% pull(emmean),2)`) compared to words (*M*= `r round(exp4__prop.hit__stim.means %>% filter(stim == "word") %>% pull(emmean),2)`), `r exp4__prop.hit__ttest__col.drawing.vs.word`). There were no significant interaction effects between stimuli format and response option condition, `r apa::anova_apa(exp4__prop.hit.aov, effect = "resp_option:stim", format = "rmarkdown", print = FALSE)`.

The ANOVA on the mean proportion of FAs also demonstrated a significant main effect of stimuli format `r apa::anova_apa(exp4__prop.FA.aov, effect = "stim", format = "rmarkdown", print = FALSE)`. Colour photographs (*M*= `r round(exp4__prop.FA__stim.means %>% filter(stim == "col.photo") %>% pull(emmean),2)`) produced significantly fewer FAs in comparison to both words (*M*= `r round(exp4__prop.FA__stim.means %>% filter(stim == "word") %>% pull(emmean),2)`), `r exp4__prop.FA__ttest__col.photo.vs.word`, and colour drawings (*M*= `r round(exp4__prop.FA__stim.means %>% filter(stim == "col.drawing") %>% pull(emmean),2)`), `r exp4__prop.FA__ttest__col.photo.vs.col.drawing`). The colour drawings (*M*= `r round(exp4__prop.FA__stim.means %>% filter(stim == "col.drawing") %>% pull(emmean),2)`) also showed a significantly lower proportion of FAs compared to words (*M*= `r round(exp4__prop.FA__stim.means %>% filter(stim == "word") %>% pull(emmean),2)`), `r exp4__prop.FA__ttest__col.drawing.vs.word`. Interaction effects between stimuli format and response option condition did not reach significance, `r apa::anova_apa(exp4__prop.FA.aov, effect = "resp_option:stim", format = "rmarkdown", print = FALSE)`.

Results from the ANOVA on mean *d'* scores again showed a significant main effect of stimuli format `r apa::anova_apa(exp4__d.prime.aov, effect = "stim", format = "rmarkdown", print = FALSE)`. Colour photographs (*M*= `r round(exp4__d.prime__stim.means %>% filter(stim == "col.photo") %>% pull(emmean),2)`) produced significantly higher *d'* scores in comparison to both words (*M*= `r round(exp4__d.prime__stim.means %>% filter(stim == "word") %>% pull(emmean),2)`), `r exp4__d.prime__ttest__col.photo.vs.word`, and colour drawings (*M*= `r round(exp4__d.prime__stim.means %>% filter(stim == "col.drawing") %>% pull(emmean),2)`), `r exp4__d.prime__ttest__col.photo.vs.col.drawing`. The colour drawings (*M*= `r round(exp4__d.prime__stim.means %>% filter(stim == "col.drawing") %>% pull(emmean),2)`) also showed significantly higher *d'* scores compared to words (*M*= `r round(exp4__d.prime__stim.means %>% filter(stim == "word") %>% pull(emmean),2)`), `r exp4__d.prime__ttest__col.drawing.vs.word`. There were no significant interaction effects between stimuli format and response option condition, `r apa::anova_apa(exp4__d.prime.aov, effect = "resp_option:stim", format = "rmarkdown", print = FALSE)`.

##### Hits assigned Recollection, Familiarity, and Guessing
```{r, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.show='hide'}
##################################################################################################################
##  Exp4 Prop R Hits:                                                                                           ##
##################################################################################################################
##  Two-way mixed ANOVA:
    exp4__prop.hit.R.aov <- afex::aov_ez('id', 'prop.hit.R', fun_aggregate = mean, exp4__prop.hit.R, 
                                       between = "resp_option", within = 'stim',
                                       anova_table=list(correction = "none", es = "ges"))
##  Mauchlys test of sphericity:
    exp4__prop.hit.R.aov__sphericity <- test_sphericity(exp4__prop.hit.R.aov)
##  Assumption of sphericity violated (p<.05), so apply Greenhouse-Geisser correction:
    exp4__prop.hit.R.aov <- afex::aov_ez('id', 'prop.hit.R', fun_aggregate = mean, exp4__prop.hit.R, 
                                       between = "resp_option", within = 'stim',
                                       anova_table=list(correction = "GG", es = "ges"))
##----------------------------------------------------------------------------------------------------------------- ##  Significant INTERACTION, so perform paired contrasts:
    exp4__prop.hit.R__pairs__interaction <- 
        pairs(emmeans(exp4__prop.hit.R.aov, ~ resp_option:stim), adjust = "bonferroni")
##  Get all means:
    exp4__prop.hit.R__stim.means <- as.tibble(summary(emmeans(exp4__prop.hit.R.aov, ~stim)))
    exp4__prop.hit.R__resp.option.means <- as.tibble(summary(emmeans(exp4__prop.hit.R.aov, ~resp_option)))    
    exp4__prop.hit.R__interaction.means <- as.tibble(summary(emmeans(exp4__prop.hit.R.aov, ~stim:resp_option))) %>%
        mutate(stim = str_replace(stim, "word", "Words")) %>%
        mutate(stim = str_replace(stim, "col.drawing", "Colour drawings")) %>%
        mutate(stim = str_replace(stim, "col.photo", "Colour photographs")) %>%
        transform(stim = factor(stim, levels=c("Words","Colour drawings","Colour photographs")))
##################################################################################################################
##  Prop R Hits interaction figure:                                                                             ##
################################################################################################################## ##  Create labels for figure (replaces plot legend):
    exp4__prop.hit.R__interaction.figure.labels <- exp4__prop.hit.R__interaction.means %>%
        select(stim, resp_option, emmean) %>%
        filter(stim == "Colour photographs") %>%
        mutate(label = case_when(
                  resp_option == "RFG" ~ "RFG",
                  resp_option == "RFBG" ~ "RFBG")) %>%
        group_by(stim, resp_option, label)
##  Interaction figure:
    exp4__prop.hit.R__interaction.figure <- exp4__prop.hit.R__interaction.means %>%
        select(stim, resp_option, emmean) %>%
        ggplot() +
            aes(x = stim, color = resp_option, group = resp_option, y = emmean) +
            stat_summary(fun.y = mean, geom = "point", size = 2.4, shape = 15) +
            stat_summary(fun.y = mean, geom = "line", size = 1.2) +
            geom_text(size = 4, aes(label = label, color = resp_option), nudge_x = 0.08, hjust = 0,
                      data = exp4__prop.hit.R__interaction.figure.labels) +
            scale_color_manual(values = c('#8ec6c5', '#7d9ab5', '#8566aa')) +
            labs(x = "Stimuli format", y = "Mean proportion of hits assigned Recollection") +
            scale_y_continuous(limits = c(0, 3.5),
                               breaks = c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5),
                               expand = c(0, 0)) +
            theme_classic() +
            theme(legend.position = "none",
                  axis.title.x = element_text(size = 10, vjust = -4),
                  axis.text.x = element_text(size = 10),
                  axis.title.y = element_text(size = 10, vjust = 6),
                  axis.text.y = element_text(size = 10),
                  plot.background = element_rect(size = 0.5, linetype = 'solid', colour = "black"),
                  plot.margin = margin(20, 20, 24, 30))
```    
```{r echo=FALSE, results = FALSE, cache=FALSE}
figure_numbering(name = "exp4__prop.hit.R__interaction.figure", caption = "Interaction plot between stimuli format and response option for the mean proportion of hits assigned Recollection.")
```

##### Recollection (hits)
Results from the ANOVA on the mean proportion of hits assigned Recollection showed a significant interaction between stimuli format and response option condition, `r apa::anova_apa(exp4__prop.hit.R.aov, effect = "resp_option:stim", format = "rmarkdown", print = FALSE)` (see `r figure_numbering("exp4__prop.hit.R__interaction.figure", display = "cite")`).

```{r fig.width=7, fig.height=4, echo=FALSE, cache=FALSE}
    exp4__prop.hit.R__interaction.figure
```
`r figure_numbering("exp4__prop.hit.R__interaction.figure")`
&nbsp;&nbsp;

Comparisons across stimuli formats showed colour photographs produced a significantly higher proportion of R hits than both words and colour drawings in both the RFG group (colour photographs [*M*= `r round(exp4__prop.hit.R__interaction.means %>% filter(resp_option == "RFG" & stim == "Colour photographs") %>% pull(emmean),2)`] vs. words [*M*= `r round(exp4__prop.hit.R__interaction.means %>% filter(resp_option == "RFG" & stim == "Words") %>% pull(emmean),2)`], `r papaja::apa_print(exp4__prop.hit.R__pairs__interaction)$statistic$RFGword_RFGcolphoto%>% str_remove_all("[$*]") %>% str_replace("t", "*t*") %>% str_replace("p", "*p*")`; colour photographs [*M*= `r round(exp4__prop.hit.R__interaction.means %>% filter(resp_option == "RFG" & stim == "Colour photographs") %>% pull(emmean),2)`] vs. colour drawings [*M*= `r round(exp4__prop.hit.R__interaction.means %>% filter(resp_option == "RFG" & stim == "Colour drawings") %>% pull(emmean),2)`], `r papaja::apa_print(exp4__prop.hit.R__pairs__interaction)$statistic$RFGcoldrawing_RFGcolphoto%>% str_remove_all("[$*]") %>% str_replace("t", "*t*") %>% str_replace("p", "*p*")`) and the RFBG group (colour photographs [*M*= `r round(exp4__prop.hit.R__interaction.means %>% filter(resp_option == "RFBG" & stim == "Colour photographs") %>% pull(emmean),2)`] vs. words [*M*= `r round(exp4__prop.hit.R__interaction.means %>% filter(resp_option == "RFBG" & stim == "Words") %>% pull(emmean),2)`], `r papaja::apa_print(exp4__prop.hit.R__pairs__interaction)$statistic$RFBGword_RFBGcolphoto%>% str_remove_all("[$*]") %>% str_replace("t", "*t*") %>% str_replace("p", "*p*")`; colour photographs [*M*= `r round(exp4__prop.hit.R__interaction.means %>% filter(resp_option == "RFBG" & stim == "Colour photographs") %>% pull(emmean),2)`] vs. colour drawings [*M*= `r round(exp4__prop.hit.R__interaction.means %>% filter(resp_option == "RFBG" & stim == "Colour drawings") %>% pull(emmean),2)`], `r papaja::apa_print(exp4__prop.hit.R__pairs__interaction)$statistic$RFBGcoldrawing_RFBGcolphoto%>% str_remove_all("[$*]") %>% str_replace("t", "*t*") %>% str_replace("p", "*p*")`). Likewise, colour drawings produced a significantly higher proportion of R hits in comparison to Words in both the RFG (colour drawings [*M*= `r round(exp4__prop.hit.R__interaction.means %>% filter(resp_option == "RFG" & stim == "Colour drawings") %>% pull(emmean),2)`] vs. words [*M*= `r round(exp4__prop.hit.R__interaction.means %>% filter(resp_option == "RFG" & stim == "Words") %>% pull(emmean),2)`], `r papaja::apa_print(exp4__prop.hit.R__pairs__interaction)$statistic$RFGword_RFGcoldrawing%>% str_remove_all("[$*]") %>% str_replace("t", "*t*") %>% str_replace("p", "*p*")`) and RFBG conditions (colour drawings [*M*= `r round(exp4__prop.hit.R__interaction.means %>% filter(resp_option == "RFBG" & stim == "Colour drawings") %>% pull(emmean),2)`] vs. words [*M*= `r round(exp4__prop.hit.R__interaction.means %>% filter(resp_option == "RFBG" & stim == "Words") %>% pull(emmean),2)`], `r papaja::apa_print(exp4__prop.hit.R__pairs__interaction)$statistic$RFBGword_RFBGcoldrawing%>% str_remove_all("[$*]") %>% str_replace("t", "*t*") %>% str_replace("p", "*p*")`).

The interaction is evident following comparisons of the same stimuli format across response option conditions. The RFG group produced a significantly higher proportion of R hits than the RFBG group for colour photographs (RFG [*M* = `r round(exp4__prop.hit.R__interaction.means %>% filter(resp_option == "RFG" & stim == "Colour photographs") %>% pull(emmean),2)`] vs. RFBG [*M* = `r round(exp4__prop.hit.R__interaction.means %>% filter(resp_option == "RFBG" & stim == "Colour photographs") %>% pull(emmean),2)`], `r papaja::apa_print(exp4__prop.hit.R__pairs__interaction)$statistic$RFBGcolphoto_RFGcolphoto %>% str_remove_all("[$*]") %>% str_replace("t", "*t*") %>% str_replace("p", "*p*")`) and for colour drawings (RFG [*M* = `r round(exp4__prop.hit.R__interaction.means %>% filter(resp_option == "RFG" & stim == "Colour drawings") %>% pull(emmean),2)`] vs. RFBG [*M* = `r round(exp4__prop.hit.R__interaction.means %>% filter(resp_option == "RFBG" & stim == "Colour drawings") %>% pull(emmean),2)`], `r papaja::apa_print(exp4__prop.hit.R__pairs__interaction)$statistic$RFBGcoldrawing_RFGcoldrawing %>% str_remove_all("[$*]") %>% str_replace("t", "*t*") %>% str_replace("p", "*p*")`). However, this was not the case for words, where there was no difference in the proportion of R hits between the RFG (*M* = `r round(exp4__prop.hit.R__interaction.means %>% filter(resp_option == "RFG" & stim == "Words") %>% pull(emmean),2)`) and RFBG groups (*M* = `r round(exp4__prop.hit.R__interaction.means %>% filter(resp_option == "RFBG" & stim == "Words") %>% pull(emmean),2)`; `r papaja::apa_print(exp4__prop.hit.R__pairs__interaction)$statistic$RFBGword_RFGword %>% str_remove_all("[$*]") %>% str_replace("t", "*t*") %>% str_replace("p", "*p*")`).

```{r, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.show='hide'}
##################################################################################################################
##  exp4 Prop F Hits:                                                                                           ##
##################################################################################################################
##  Two-way mixed ANOVA:
    exp4__prop.hit.F.aov <- afex::aov_ez('id', 'prop.hit.F', fun_aggregate = mean, exp4__prop.hit.F, 
                                       between = "resp_option", within = 'stim',
                                       anova_table=list(correction = "none", es = "ges"))
##  Mauchlys test of sphericity:
    exp4__prop.hit.F.aov__sphericity <- test_sphericity(exp4__prop.hit.F.aov)
##  Assumption of sphericity violated (p<.05), so apply Greenhouse-Geisser correction:
    exp4__prop.hit.F.aov <- afex::aov_ez('id', 'prop.hit.F', fun_aggregate = mean, exp4__prop.hit.F, 
                                       between = "resp_option", within = 'stim',
                                       anova_table=list(correction = "GG", es = "ges"))
##----------------------------------------------------------------------------------------------------------------- ##  Significant main effect of RESPONSE OPTION, so first check if variances are equal using Levene's test:
    exp4__prop.hit.F__levene.test__rfg.rfbg <- exp4__prop.hit.F %>% leveneTest(prop.hit.F ~ resp_option, data = .)
##  Levene's test significant (variances not equal), so perform corrected Welch two-sample t-test: 
    exp4__prop.hit.F__ttest__rfg.rfbg <- exp4__prop.hit.F %>%
        t_test(prop.hit.F ~ resp_option, paired = FALSE, data = ., var.equal = FALSE)
##  Calculate effect size:
    exp4__prop.hit.F__ttest__rfg.rfbg__eff.size <- exp4__prop.hit.F %>% 
        rstatix::cohens_d(prop.hit.F ~ resp_option, var.equal = FALSE, paired = FALSE, ci = TRUE, 
                          conf.level = 0.95)
##-----------------------------------------------------------------------------------------------------------------
##  Significant main effect of STIMULI FORMAT, so perform paired contrasts:
    exp4__prop.hit.F__pairwise__stim.format <- exp4__prop.hit.F %>% 
        pairwise_t_test(prop.hit.F ~ stim, paired = TRUE, p.adjust.method = "bonferroni")
##  Calculate effect size:      
    exp4__prop.hit.F__pairwise__stim.format__eff.size <- exp4__prop.hit.F %>% 
        rstatix::cohens_d(prop.hit.F ~ stim, paired = TRUE, ci = TRUE, conf.level = 0.95)       
    
##  Format for report (colour photos vs. words t-test):    
    temp <- exp4__prop.hit.F__pairwise__stim.format %>% filter(group1 == "col.photo" & group2 == "word")
    exp4__prop.hit.F__ttest__col.photo.vs.word <- str_c(ttest.writeup(temp), "; *d* = ", 
        round(as.vector(exp4__prop.hit.F__pairwise__stim.format__eff.size %>% 
                          filter(group1 == "col.photo" & group2 == "word") %>% pull(effsize)), 2),
        ", 95% CI [", 
        exp4__prop.hit.F__pairwise__stim.format__eff.size %>%
            filter(group1 == "col.photo" & group2 == "word") %>% pull(conf.low), ", ",
                    exp4__prop.hit.F__pairwise__stim.format__eff.size %>%
                        filter(group1 == "col.photo" & group2 == "word") %>% pull(conf.high), "]")                                                         
##  Format for report (colour drawings vs. words t-test):
    temp <- exp4__prop.hit.F__pairwise__stim.format %>% filter(group1 == "col.drawing" & group2 == "word")
    exp4__prop.hit.F__ttest__col.drawing.vs.word <- str_c(ttest.writeup(temp), "; *d* = ", 
        round(as.vector(exp4__prop.hit.F__pairwise__stim.format__eff.size %>% 
                          filter(group1 == "col.drawing" & group2 == "word") %>% pull(effsize)), 2),
        ", 95% CI [", 
        exp4__prop.hit.F__pairwise__stim.format__eff.size %>%
            filter(group1 == "col.drawing" & group2 == "word") %>% pull(conf.low), ", ",
                    exp4__prop.hit.F__pairwise__stim.format__eff.size %>%
                        filter(group1 == "col.drawing" & group2 == "word") %>% pull(conf.high), "]")                                                           
##  Format for report (colour drawings vs. colour photos t-test):
    temp <- exp4__prop.hit.F__pairwise__stim.format %>% filter(group1 == "col.drawing" & group2 == "col.photo")
    exp4__prop.hit.F__ttest__col.photo.vs.col.drawing <- str_c(ttest.writeup(temp), "; *d* = ", 
        round(as.vector(exp4__prop.hit.F__pairwise__stim.format__eff.size %>% 
                          filter(group1 == "col.drawing" & group2 == "col.photo") %>% pull(effsize)), 2),
        ", 95% CI [", 
        exp4__prop.hit.F__pairwise__stim.format__eff.size %>%
            filter(group1 == "col.drawing" & group2 == "col.photo") %>% pull(conf.low), ", ",
                    exp4__prop.hit.F__pairwise__stim.format__eff.size %>%
                        filter(group1 == "col.drawing" & group2 == "col.photo") %>% pull(conf.high), "]")
##  Get all means:
    exp4__prop.hit.F__stim.means <- as.tibble(summary(emmeans(exp4__prop.hit.F.aov, ~stim)))
    exp4__prop.hit.F__resp.option.means <- as.tibble(summary(emmeans(exp4__prop.hit.F.aov, ~resp_option)))
```    
  
    
##### Familiarity (hits)
Results from the ANOVA on the mean proportion of hits assigned Familiarity again showed a significant main effect of stimuli format `r apa::anova_apa(exp4__prop.hit.F.aov, effect = "stim", format = "rmarkdown", print = FALSE)`. Colour photographs (*M*= `r round(exp4__prop.hit.F__stim.means %>% filter(stim == "col.photo") %>% pull(emmean),2)`) produced significantly fewer F hits than both words (*M*= `r round(exp4__prop.hit.F__stim.means %>% filter(stim == "word") %>% pull(emmean),2)`), `r exp4__prop.hit.F__ttest__col.photo.vs.word`, and colour drawings (*M*= `r round(exp4__prop.hit.F__stim.means %>% filter(stim == "col.drawing") %>% pull(emmean),2)`), `r exp4__prop.hit.F__ttest__col.photo.vs.col.drawing`. The colour drawings (*M*= `r round(exp4__prop.hit.F__stim.means %>% filter(stim == "col.drawing") %>% pull(emmean),2)`) also showed significantly fewer F hits compared to words (*M*= `r round(exp4__prop.hit.F__stim.means %>% filter(stim == "word") %>% pull(emmean),2)`), `r exp4__prop.hit.F__ttest__col.drawing.vs.word`. There were no significant interaction effects between stimuli format and response option condition, `r apa::anova_apa(exp4__prop.hit.F.aov, effect = "resp_option:stim", format = "rmarkdown", print = FALSE)`.


```{r, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.show='hide'}
##################################################################################################################
##  Exp4 Prop G Hits:                                                                                           ##
##################################################################################################################
##  Two-way mixed ANOVA:
    exp4__prop.hit.G.aov <- afex::aov_ez('id', 'prop.hit.G', fun_aggregate = mean, exp4__prop.hit.G, 
                                       between = "resp_option", within = 'stim',
                                       anova_table=list(correction = "none", es = "ges"))
##  Mauchlys test of sphericity:
    exp4__prop.hit.G.aov__sphericity <- test_sphericity(exp4__prop.hit.G.aov)
##  Assumption of sphericity violated (p<.05), so apply Greenhouse-Geisser correction:
    exp4__prop.hit.G.aov <- afex::aov_ez('id', 'prop.hit.G', fun_aggregate = mean, exp4__prop.hit.G, 
                                       between = "resp_option", within = 'stim',
                                       anova_table=list(correction = "GG", es = "ges"))
##----------------------------------------------------------------------------------------------------------------- ##  No significant main effect of RESPONSE OPTION.
##----------------------------------------------------------------------------------------------------------------- ##  Significant main effect of STIMULI FORMAT, so perform paired contrasts:
    exp4__prop.hit.G__pairwise__stim.format <- exp4__prop.hit.G %>% 
        pairwise_t_test(prop.hit.G ~ stim, paired = TRUE, p.adjust.method = "bonferroni")
##  Calculate effect size:      
    exp4__prop.hit.G__pairwise__stim.format__eff.size <- exp4__prop.hit.G %>% 
        rstatix::cohens_d(prop.hit.G ~ stim, paired = TRUE, ci = TRUE, conf.level = 0.95)  
##  t-test - col photos vs. words:
    temp <- exp4__prop.hit.G__pairwise__stim.format %>% filter(group1 == "col.photo" & group2 == "word")
    exp4__prop.hit.G__ttest__col.photo.vs.word <- str_c(ttest.writeup(temp), "; *d* = ", 
        round(as.vector(exp4__prop.hit.G__pairwise__stim.format__eff.size %>% 
                          filter(group1 == "col.photo" & group2 == "word") %>% pull(effsize)), 2),
        ", 95% CI [", 
        exp4__prop.hit.G__pairwise__stim.format__eff.size %>%
            filter(group1 == "col.photo" & group2 == "word") %>% pull(conf.low), ", ",
                    exp4__prop.hit.G__pairwise__stim.format__eff.size %>%
                        filter(group1 == "col.photo" & group2 == "word") %>% pull(conf.high), "]")      
    
##  t-test - col drawings vs. words:    
    temp <- exp4__prop.hit.G__pairwise__stim.format %>% filter(group1 == "col.drawing" & group2 == "word")
    exp4__prop.hit.G__ttest__col.drawing.vs.word <- str_c(ttest.writeup(temp), "; *d* = ", 
        round(as.vector(exp4__prop.hit.G__pairwise__stim.format__eff.size %>% 
                          filter(group1 == "col.drawing" & group2 == "word") %>% pull(effsize)), 2),
        ", 95% CI [", 
        exp4__prop.hit.G__pairwise__stim.format__eff.size %>%
            filter(group1 == "col.drawing" & group2 == "word") %>% pull(conf.low), ", ",
                    exp4__prop.hit.G__pairwise__stim.format__eff.size %>%
                        filter(group1 == "col.drawing" & group2 == "word") %>% pull(conf.high), "]")
    
##  t-test - col drawings vs. col photos:    
    temp <- exp4__prop.hit.G__pairwise__stim.format %>% filter(group1 == "col.drawing" & group2 == "col.photo")
    exp4__prop.hit.G__ttest__col.photo.vs.col.drawing <- ttest.writeup(temp)
    
    exp4__prop.hit.G__ttest__col.photo.vs.col.drawing <- str_c(ttest.writeup(temp), "; *d* = ", 
        round(as.vector(exp4__prop.hit.G__pairwise__stim.format__eff.size %>% 
                          filter(group1 == "col.drawing" & group2 == "col.photo") %>% pull(effsize)), 2),
        ", 95% CI [", 
        exp4__prop.hit.G__pairwise__stim.format__eff.size %>%
            filter(group1 == "col.drawing" & group2 == "col.photo") %>% pull(conf.low), ", ",
                    exp4__prop.hit.G__pairwise__stim.format__eff.size %>%
                        filter(group1 == "col.drawing" & group2 == "col.photo") %>% pull(conf.high), "]")    
##----------------------------------------------------------------------------------------------------------------- ##  Get all means:
    exp4__prop.hit.G__stim.means <- as.tibble(summary(emmeans(exp4__prop.hit.G.aov, ~stim)))
    exp4__prop.hit.G__resp.option.means <- as.tibble(summary(emmeans(exp4__prop.hit.G.aov, ~resp_option)))
```

##### Guessing (hits)
The ANOVA on the mean proportion of hits assigned Guessing demonstrated a significant main effect of stimuli format `r apa::anova_apa(exp4__prop.hit.G.aov, effect = "stim", format = "rmarkdown", print = FALSE)`. Colour photographs (*M*= `r round(exp4__prop.hit.G__stim.means %>% filter(stim == "col.photo") %>% pull(emmean),2)`) produced significantly fewer G hits in comparison to both words (*M*= `r round(exp4__prop.hit.G__stim.means %>% filter(stim == "word") %>% pull(emmean),2)`; `r exp4__prop.hit.G__ttest__col.photo.vs.word`) and colour drawings (*M*= `r round(exp4__prop.hit.G__stim.means %>% filter(stim == "col.drawing") %>% pull(emmean),2)`; `r exp4__prop.hit.G__ttest__col.photo.vs.col.drawing`). The colour drawings (*M*= `r round(exp4__prop.hit.G__stim.means %>% filter(stim == "col.drawing") %>% pull(emmean),2)`) also showed a significantly lower proportion of G hits compared to words (*M*= `r round(exp4__prop.hit.G__stim.means %>% filter(stim == "word") %>% pull(emmean),2)`; `r exp4__prop.hit.G__ttest__col.drawing.vs.word`. There were no significant interaction effects between stimuli format and response option condition `r apa::anova_apa(exp4__prop.hit.G.aov, effect = "resp_option:stim", format = "rmarkdown", print = FALSE)`.

```{r, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.show='hide'}
##################################################################################################################
##  Exp4 Prop R FAs:                                                                                            ##
##################################################################################################################
##  Two-way mixed ANOVA:
    exp4__prop.FA.R.aov <- afex::aov_ez('id', 'prop.FA.R', fun_aggregate = mean, exp4__prop.FA.R, 
                                       between = "resp_option", within = 'stim',
                                       anova_table=list(correction = "none", es = "ges"))
##  Mauchlys test of sphericity:
    exp4__prop.FA.R.aov__sphericity <- test_sphericity(exp4__prop.FA.R.aov)
##  Assumption of sphericity not violated (p>.05), so no correction applied.
##----------------------------------------------------------------------------------------------------------------- ##  No significant main effect of RESPONSE OPTION. 
##-----------------------------------------------------------------------------------------------------------------
##  No significant main effect of STIMULI FORMAT.
##-----------------------------------------------------------------------------------------------------------------
##  Get all means:
    exp4__prop.FA.R__stim.means <- as.tibble(summary(emmeans(exp4__prop.FA.R.aov, ~stim)))
    exp4__prop.FA.R__resp.option.means <- as.tibble(summary(emmeans(exp4__prop.FA.R.aov, ~resp_option)))
```

##### FAs assigned Recollection, Familiarity, and Guessing

For FAs assigned *Recollection*, there was no significant main effect of stimuli format [`r apa::anova_apa(exp4__prop.FA.R.aov, effect = "stim", format = "rmarkdown", print = FALSE)` or interaction [`r apa::anova_apa(exp4__prop.FA.R.aov, effect = "resp_option:stim", format = "rmarkdown", print = FALSE)`].

```{r, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.show='hide'}
##################################################################################################################
##  exp4 Prop F FAs:                                                                                            ##
##################################################################################################################
##  Two-way mixed ANOVA:
    exp4__prop.FA.F.aov <- afex::aov_ez('id', 'prop.FA.F', fun_aggregate = mean, exp4__prop.FA.F, 
                                       between = "resp_option", within = 'stim',
                                       anova_table=list(correction = "none", es = "ges"))
##  Mauchlys test of sphericity:
    exp4__prop.FA.F.aov__sphericity <- test_sphericity(exp4__prop.FA.F.aov)
##  Assumption of sphericity not violated (p>.05). Greenhouse-Geisser correction not applied.
##----------------------------------------------------------------------------------------------------------------- ##  Significant main effect of RESPONSE OPTION, so first check if variances are equal using Levene's test:
    exp4__prop.FA.F__levene.test__rfg.rfbg <- exp4__prop.FA.F %>% leveneTest(prop.FA.F ~ resp_option, data = .)
##  Levene's test significant (variances not equal), so perform corrected Welch two-sample t-test: 
    exp4__prop.FA.F__ttest__rfg.rfbg <- exp4__prop.FA.F %>%
        t_test(prop.FA.F ~ resp_option, paired = FALSE, data = ., var.equal = FALSE)
##  Calculate effect size:
    exp4__prop.FA.F__ttest__rfg.rfbg__eff.size <- exp4__prop.FA.F %>% 
        rstatix::cohens_d(prop.FA.F ~ resp_option, var.equal = FALSE, paired = FALSE, ci = TRUE, conf.level = 0.95)
##----------------------------------------------------------------------------------------------------------------- ##  Significant main effect of STIMULI FORMAT, so perform paired contrasts:
    exp4__prop.FA.F__pairwise__stim.format <- exp4__prop.FA.F %>% 
        pairwise_t_test(prop.FA.F ~ stim, paired = TRUE, p.adjust.method = "bonferroni")
##  Calculate effect size:      
    exp4__prop.FA.F__pairwise__stim.format__eff.size <- exp4__prop.FA.F %>% 
        rstatix::cohens_d(prop.FA.F ~ stim, paired = TRUE, ci = TRUE, conf.level = 0.95)      
##  t-test - colour photos vs. words:
    temp <- exp4__prop.FA.F__pairwise__stim.format %>% filter(group1 == "col.photo" & group2 == "word")
    exp4__prop.FA.F__ttest__col.photo.vs.word <- str_c(ttest.writeup(temp), "; *d* = ", 
        round(as.vector(exp4__prop.FA.F__pairwise__stim.format__eff.size %>% 
                          filter(group1 == "col.photo" & group2 == "word") %>% pull(effsize)), 2),
        ", 95% CI [", 
        exp4__prop.FA.F__pairwise__stim.format__eff.size %>%
            filter(group1 == "col.photo" & group2 == "word") %>% pull(conf.low), ", ",
                    exp4__prop.FA.F__pairwise__stim.format__eff.size %>%
                        filter(group1 == "col.photo" & group2 == "word") %>% pull(conf.high), "]")          
    
##  t-test - col drawings vs. words:    
    temp <- exp4__prop.FA.F__pairwise__stim.format %>% filter(group1 == "col.drawing" & group2 == "word")
    exp4__prop.FA.F__ttest__col.drawing.vs.word <- str_c(ttest.writeup(temp), "; *d* = ", 
        round(as.vector(exp4__prop.FA.F__pairwise__stim.format__eff.size %>% 
                          filter(group1 == "col.drawing" & group2 == "word") %>% pull(effsize)), 2),
        ", 95% CI [", 
        exp4__prop.FA.F__pairwise__stim.format__eff.size %>%
            filter(group1 == "col.drawing" & group2 == "word") %>% pull(conf.low), ", ",
                    exp4__prop.FA.F__pairwise__stim.format__eff.size %>%
                        filter(group1 == "col.drawing" & group2 == "word") %>% pull(conf.high), "]")       
    
##  t-test - col drawings vs. col photos:    
    temp <- exp4__prop.FA.F__pairwise__stim.format %>% filter(group1 == "col.drawing" & group2 == "col.photo")
    exp4__prop.FA.F__ttest__col.photo.vs.col.drawing <- str_c(ttest.writeup(temp), "; *d* = ", 
        round(as.vector(exp4__prop.FA.F__pairwise__stim.format__eff.size %>% 
                          filter(group1 == "col.drawing" & group2 == "col.photo") %>% pull(effsize)), 2),
        ", 95% CI [", 
        exp4__prop.FA.F__pairwise__stim.format__eff.size %>%
            filter(group1 == "col.drawing" & group2 == "col.photo") %>% pull(conf.low), ", ",
                    exp4__prop.FA.F__pairwise__stim.format__eff.size %>%
                        filter(group1 == "col.drawing" & group2 == "col.photo") %>% pull(conf.high), "]")         
##----------------------------------------------------------------------------------------------------------------- ##  Get all means:
    exp4__prop.FA.F__stim.means <- as.tibble(summary(emmeans(exp4__prop.FA.F.aov, ~stim)))
    exp4__prop.FA.F__resp.option.means <- as.tibble(summary(emmeans(exp4__prop.FA.F.aov, ~resp_option)))
```

The ANOVA for FAs assigned *Familiarity* showed a significant main effect of stimuli format, `r apa::anova_apa(exp4__prop.FA.F.aov, effect = "stim", format = "rmarkdown", print = FALSE)`. Colour photographs (*M*= `r round(exp4__prop.FA.F__stim.means %>% filter(stim == "col.photo") %>% pull(emmean),2)`) produced significantly fewer F FAs than words (*M*= `r round(exp4__prop.FA.F__stim.means %>% filter(stim == "word") %>% pull(emmean),2)`), `r exp4__prop.FA.F__ttest__col.photo.vs.word`. Likewise, colour drawings (*M*= `r round(exp4__prop.FA.F__stim.means %>% filter(stim == "col.drawing") %>% pull(emmean),2)`) also showed a significantly lower proportion of FAs compared to words (*M*= `r round(exp4__prop.FA.F__stim.means %>% filter(stim == "word") %>% pull(emmean),2)`), `r exp4__prop.FA.F__ttest__col.drawing.vs.word`. However, there was no significant difference in the proportion of FAs assigned Familiarity between colour photographs (*M*= `r round(exp4__prop.FA.F__stim.means %>% filter(stim == "col.photo") %>% pull(emmean),2)`) and colour drawings
(*M*= `r round(exp4__prop.FA.F__stim.means %>% filter(stim == "colour.drawing") %>% pull(emmean),2)`), `r exp4__prop.FA.F__ttest__colour.photo.vs.colour.drawing`. There were no significant interaction effects between stimuli format and response option condition, `r apa::anova_apa(exp4__prop.FA.F.aov, effect = "resp_option:stim", format = "rmarkdown", print = FALSE)`.