---
title: "R Notebook"
output: html_notebook
---








\newpage
## Results

```{r echo=FALSE, results = FALSE, cache=FALSE}
    table_numbering("exp1__hit_and_FA_caption", "Mean proportion of hits and FAs 
                    by stimuli-format and response-option condition.", display = FALSE)
```


```{r, include=FALSE, warning = FALSE, message=FALSE, cache=TRUE}
###################################################################################################################
##    Hits figure:                                                                                               ##
###################################################################################################################
      exp1__hit_figure_data <- tribble(~"ResponseOption", ~"StimuliFormat", ~"rfg", ~"emmean", ~"SE",
          as.character(pull(exp1__rec_hit_figure_data[1,1])), 
          as.character(pull(exp1__rec_hit_figure_data[1,2])), "Recollection",
          as.double(pull(exp1__rec_hit_figure_data[1,3])), as.double(pull(exp1__rec_hit_figure_data[1,4])),
          as.character(pull(exp1__rec_hit_figure_data[2,1])), 
          as.character(pull(exp1__rec_hit_figure_data[2,2])), "Recollection",
          as.double(pull(exp1__rec_hit_figure_data[2,3])), as.double(pull(exp1__rec_hit_figure_data[2,4])),
          as.character(pull(exp1__rec_hit_figure_data[3,1])), 
          as.character(pull(exp1__rec_hit_figure_data[3,2])), "Recollection",
          as.double(pull(exp1__rec_hit_figure_data[3,3])), as.double(pull(exp1__rec_hit_figure_data[3,4])),
          as.character(pull(exp1__rec_hit_figure_data[4,1])), 
          as.character(pull(exp1__rec_hit_figure_data[4,2])), "Recollection",
          as.double(pull(exp1__rec_hit_figure_data[4,3])), as.double(pull(exp1__rec_hit_figure_data[4,4])),
          as.character(pull(exp1__rec_hit_figure_data[5,1])), 
          as.character(pull(exp1__rec_hit_figure_data[5,2])), "Recollection",
          as.double(pull(exp1__rec_hit_figure_data[5,3])), as.double(pull(exp1__rec_hit_figure_data[5,4])),
          as.character(pull(exp1__rec_hit_figure_data[6,1])), 
          as.character(pull(exp1__rec_hit_figure_data[6,2])), "Recollection",
          as.double(pull(exp1__rec_hit_figure_data[6,3])), as.double(pull(exp1__rec_hit_figure_data[6,4])),
          as.character(pull(exp1__fam_hit_figure_data[1,1])), 
          as.character(pull(exp1__fam_hit_figure_data[1,2])), "Familiarity",
          as.double(pull(exp1__fam_hit_figure_data[1,3])), as.double(pull(exp1__fam_hit_figure_data[1,4])),
          as.character(pull(exp1__fam_hit_figure_data[2,1])), 
          as.character(pull(exp1__fam_hit_figure_data[2,2])), "Familiarity",
          as.double(pull(exp1__fam_hit_figure_data[2,3])), as.double(pull(exp1__fam_hit_figure_data[2,4])),
          as.character(pull(exp1__fam_hit_figure_data[3,1])), 
          as.character(pull(exp1__fam_hit_figure_data[3,2])), "Familiarity",
          as.double(pull(exp1__fam_hit_figure_data[3,3])), as.double(pull(exp1__fam_hit_figure_data[3,4])),
          as.character(pull(exp1__fam_hit_figure_data[4,1])), 
          as.character(pull(exp1__fam_hit_figure_data[4,2])), "Familiarity",
          as.double(pull(exp1__fam_hit_figure_data[4,3])), as.double(pull(exp1__fam_hit_figure_data[4,4])),
          as.character(pull(exp1__fam_hit_figure_data[5,1])), 
          as.character(pull(exp1__fam_hit_figure_data[5,2])), "Familiarity",
          as.double(pull(exp1__fam_hit_figure_data[5,3])), as.double(pull(exp1__fam_hit_figure_data[5,4])),
          as.character(pull(exp1__fam_hit_figure_data[6,1])), 
          as.character(pull(exp1__fam_hit_figure_data[6,2])), "Familiarity",
          as.double(pull(exp1__fam_hit_figure_data[6,3])), as.double(pull(exp1__fam_hit_figure_data[6,4])),
          as.character(pull(exp1__guess_hit_figure_data[1,1])),
          as.character(pull(exp1__guess_hit_figure_data[1,2])), "Guessing",
          as.double(pull(exp1__guess_hit_figure_data[1,3])), as.double(pull(exp1__guess_hit_figure_data[1,4])),
          as.character(pull(exp1__guess_hit_figure_data[2,1])),
          as.character(pull(exp1__guess_hit_figure_data[2,2])), "Guessing",
          as.double(pull(exp1__guess_hit_figure_data[2,3])), as.double(pull(exp1__guess_hit_figure_data[2,4])),
          as.character(pull(exp1__guess_hit_figure_data[3,1])),
          as.character(pull(exp1__guess_hit_figure_data[3,2])), "Guessing",
          as.double(pull(exp1__guess_hit_figure_data[3,3])), as.double(pull(exp1__guess_hit_figure_data[3,4])),
          as.character(pull(exp1__guess_hit_figure_data[4,1])),
          as.character(pull(exp1__guess_hit_figure_data[4,2])), "Guessing",
          as.double(pull(exp1__guess_hit_figure_data[4,3])), as.double(pull(exp1__guess_hit_figure_data[4,4])),
          as.character(pull(exp1__guess_hit_figure_data[5,1])),
          as.character(pull(exp1__guess_hit_figure_data[5,2])), "Guessing",
          as.double(pull(exp1__guess_hit_figure_data[5,3])), as.double(pull(exp1__guess_hit_figure_data[5,4])),
          as.character(pull(exp1__guess_hit_figure_data[6,1])),
          as.character(pull(exp1__guess_hit_figure_data[6,2])), "Guessing",
          as.double(pull(exp1__guess_hit_figure_data[6,3])), as.double(pull(exp1__guess_hit_figure_data[6,4]))) %>%
          transform(ResponseOption = factor(ResponseOption, levels=c("RFG","RFBG","RF_Ratings"))) %>%
          transform(rfg = factor(rfg, levels=c("Recollection","Familiarity","Guessing"))) %>%
          transform(StimuliFormat = factor(StimuliFormat, levels=c("Words","Pictures")))




##    Hit figure:
      exp1__hit_figure <- ggplot(exp1__hit_figure_data, aes(x = StimuliFormat, y = emmean, fill = rfg)) +
          scale_fill_manual("legend", values = c("Recollection" = "#1B4251", "Familiarity" = "#6A6C93",
                                                 "Guessing" = "#D491CA")) + 
          geom_col(position = position_dodge()) +
          geom_errorbar(aes(ymin = pmax(emmean-SE, 0), ymax = emmean+SE), width = 0.2, size = 0.3, 
                        position = position_dodge(0.9)) +
          facet_wrap(~ResponseOption, strip.position = "bottom") +
          labs(x = "Response-option condition", y = "Mean proportion of hits") +
          scale_y_continuous(expand = c(0, 0), limits = c(0, 1)) +
          theme_classic() +    # Removes grey background and grid lines. 
          theme(
              strip.placement = "outside",
              strip.background = element_rect(fill = "white", size = 0.5, linetype = "solid", colour = "black"),
              axis.title.x = element_text(vjust=-4),    # Move x-axis label further away from the figure.
              axis.title.y = element_text(vjust=6),     # Move y-axis label further away from the figure.
              axis.text.x = element_text(size = 9),
              axis.text.y = element_text(size = 9),
              legend.background = element_rect(fill = "white", size = 0.2, linetype = "solid", colour = "black"),
              legend.title = element_blank(),
              legend.position = c(0.5, 0.896),
              legend.margin = margin(6, 6, 6, 6),
              legend.spacing.y = unit(-1, "pt"),
              plot.background = element_rect(size = 0.5, linetype = 'solid', colour = "black"),
              plot.margin = margin(20, 20, 24, 30))

##    Prep data for figures:  
      exp1__total_prop_hit_figure_data <- as.tibble(exp1__anova_prop_hit_interaction_mmeans) %>%
          select(-df, -lower.CL, -upper.CL)
          dput(exp1__total_prop_hit_figure_data)
          
##    Hit / FA figure:
      exp1__rfg_totals <- exp1__full_data %>%
          filter(ResponseOption == "RFG") %>%
          mutate(total_hit = word_hit + pic_hit) %>%
          mutate(total_FA = word_FA + pic_FA)
      exp1__rfbg_totals <- exp1__full_data %>%
          filter(ResponseOption == "RFBG") %>%
          mutate(total_hit = word_hit + pic_hit) %>%
          mutate(total_FA = word_FA + pic_FA)
      exp1__rf_r_totals <- exp1__full_data %>%
          filter(ResponseOption == "RF_Ratings") %>%
          mutate(total_hit = word_hit + pic_hit) %>%
          mutate(total_FA = word_FA + pic_FA)

      exp1__table_hits_and_FAs <- tribble(
          ~"Stim", ~Hits,  ~FAs,
          "Words", mean(exp1__full_data$prop_word_hit), mean(exp1__full_data$prop_word_FA),
          "Pictures", mean(exp1__full_data$prop_pic_hit), mean(exp1__full_data$prop_pic_FA),
          "RFG", mean(exp1__rfg_totals$total_hit) / 60, mean(exp1__rfg_totals$total_FA) / 60,
          "RFBG", mean(exp1__rfbg_totals$total_hit) / 60, mean(exp1__rfbg_totals$total_FA) / 60,
          "RF-Ratings", mean(exp1__rf_r_totals$total_hit) / 60, mean(exp1__rf_r_totals$total_FA) / 60) %>%
          mutate_if(is.numeric, round, 2) %>%
          column_to_rownames(var = "Stim")
      
      
      
      
##    d' and c table:
      exp1__rfg_dprime <- as.data.frame(emmeans(exp1__anova_prop_dprime, ~ ResponseOption)) %>% 
          filter(ResponseOption == "RFG") %>% pull(emmean)
      exp1__rfbg_dprime <- as.data.frame(emmeans(exp1__anova_prop_dprime, ~ ResponseOption)) %>% 
          filter(ResponseOption == "RFBG") %>% pull(emmean)
      exp1__rfr_dprime <- as.data.frame(emmeans(exp1__anova_prop_dprime, ~ ResponseOption)) %>% 
          filter(ResponseOption == "RF_Ratings") %>% pull(emmean)
      exp1__rfg_c <- as.data.frame(emmeans(exp1__anova_prop_c, ~ ResponseOption)) %>% 
          filter(ResponseOption == "RFG") %>% pull(emmean)
      exp1__rfbg_c <- as.data.frame(emmeans(exp1__anova_prop_c, ~ ResponseOption)) %>% 
          filter(ResponseOption == "RFBG") %>% pull(emmean)
      exp1__rfr_c <- as.data.frame(emmeans(exp1__anova_prop_c, ~ ResponseOption)) %>% 
          filter(ResponseOption == "RF_Ratings") %>% pull(emmean)

      exp1__table_dprime_and_c <- tribble(
          ~"Stim", ~"d'",  ~"c",
          "Words", mean(exp1__full_data$exp1__word_d_prime), mean(exp1__full_data$word_c),
          "Pictures", mean(exp1__full_data$exp1__pic_d_prime), mean(exp1__full_data$pic_c),
          "RFG", exp1__rfg_dprime, exp1__rfg_c,
          "RFBG", exp1__rfbg_dprime, exp1__rfbg_c,
          "RF-Ratings", exp1__rfr_dprime, exp1__rfr_c) %>%
          mutate_if(is.numeric, round, 2) %>%
          column_to_rownames(var = "Stim")
      
      
      
##    Rec hits interaction figure:
      exp1__rec_hit_figure_data <- as.tibble(exp1__anova_prop_rec_hit_interaction_mmeans) %>%
          select(-df, -lower.CL, -upper.CL)
##    Labels (replaces plot legend):
      exp1__rec_hit_interaction_figure_labels <- exp1__rec_hit_figure_data %>%
          select(StimuliFormat, ResponseOption, emmean) %>%
          filter(StimuliFormat == "Pictures") %>%
          mutate(label = case_when(
              ResponseOption == "RFG" ~ "RFG",
              ResponseOption == "RFBG" ~ "RFBG",
              ResponseOption == "RF_Ratings" ~ "RF Ratings")) %>%
          group_by(StimuliFormat, ResponseOption, label) %>%
          mutate(emmean=replace(emmean, ResponseOption=="RFG", 0.62)) %>%
          mutate(emmean=replace(emmean, ResponseOption=="RFBG", 0.41))
##    Figure:
      exp1__rec_hit_interaction_figure <- exp1__rec_hit_figure_data %>%
          ggplot() +
          aes(x = StimuliFormat, color = ResponseOption, group = ResponseOption, y = emmean) +
          stat_summary(fun.y = mean, geom = "point", size = 2.4, shape = 15) +
          stat_summary(fun.y = mean, geom = "line", size = 1.2) +
          geom_text(size = 4, aes(label = label, color = ResponseOption), nudge_x = 0.08, hjust = 0,
                    data = exp1__rec_hit_interaction_figure_labels) +
          scale_color_manual(values = c('#8ec6c5', '#7d9ab5', '#8566aa')) +
          labs(x = "Stimuli-format", y = "Mean proportion of hits assigned:  'Recollection'") +
          scale_y_continuous(limits = c(0, 1),
                             breaks = c(0, 0.10, 0.20, 0.30, 0.40, 0.50, 0.60, 0.70, 0.80, 0.90, 1),
                             expand = c(0, 0)) +
          theme_classic() +
          theme(legend.position = "none",
                axis.title.x = element_text(size = 10, vjust = -4),
                axis.text.x = element_text(size = 10),
                axis.title.y = element_text(size = 10, vjust = 6),
                axis.text.y = element_text(size = 10),
                plot.background = element_rect(size = 0.5, linetype = 'solid', colour = "black"),
                plot.margin = margin(20, 20, 24, 30))
      
##    Fam hits interaction figure:
      exp1__fam_hit_figure_data <- as.tibble(exp1__anova_prop_fam_hit_interaction_mmeans) %>%
          select(-df, -lower.CL, -upper.CL)
##    Labels (replaces plot legend):
      exp1__fam_hit_interaction_figure_labels <- exp1__fam_hit_figure_data %>%
          select(StimuliFormat, ResponseOption, emmean) %>%
          filter(StimuliFormat == "Pictures") %>%
          mutate(label = case_when(
              ResponseOption == "RFG" ~ "RFG",
              ResponseOption == "RFBG" ~ "RFBG",
              ResponseOption == "RF_Ratings" ~ "RF Ratings")) %>%
          group_by(StimuliFormat, ResponseOption, label)
##    Figure:
      exp1__fam_hit_interaction_figure <- exp1__fam_hit_figure_data %>%
          ggplot() +
          aes(x = StimuliFormat, color = ResponseOption, group = ResponseOption, y = emmean) +
          stat_summary(fun.y = mean, geom = "point", size = 2.4, shape = 15) +
          stat_summary(fun.y = mean, geom = "line", size = 1.2) +
          geom_text(size = 4, aes(label = label, color = ResponseOption), nudge_x = 0.08, hjust = 0,
                    data = exp1__fam_hit_interaction_figure_labels) +
          scale_color_manual(values = c('#8ec6c5', '#7d9ab5', '#8566aa')) +
          labs(x = "Stimuli-format", y = "Mean proportion of hits assigned:  'Familiarity'") +
          scale_y_continuous(limits = c(0, 1),
                             breaks = c(0, 0.10, 0.20, 0.30, 0.40, 0.50, 0.60, 0.70, 0.80, 0.90, 1),
                             expand = c(0, 0)) +
          theme_classic() +
          theme(legend.position = "none",
                axis.title.x = element_text(size = 10, vjust = -4),
                axis.text.x = element_text(size = 10),
                axis.title.y = element_text(size = 10, vjust = 6),
                axis.text.y = element_text(size = 10),
                plot.background = element_rect(size = 0.5, linetype = 'solid', colour = "black"),
                plot.margin = margin(20, 20, 24, 30))
      
      
##    Guess hits interaction figure:
      exp1__guess_hit_figure_data <- as.tibble(exp1__anova_prop_guess_hit_interaction_mmeans) %>%
          select(-df, -lower.CL, -upper.CL)
##    Labels (replaces plot legend):
      exp1__guess_hit_interaction_figure_labels <- exp1__guess_hit_figure_data %>%
          select(StimuliFormat, ResponseOption, emmean) %>%
          filter(StimuliFormat == "Pictures") %>%
          mutate(label = case_when(
              ResponseOption == "RFG" ~ "RFG",
              ResponseOption == "RFBG" ~ "RFBG",
              ResponseOption == "RF_Ratings" ~ "RF Ratings")) %>%
          group_by(StimuliFormat, ResponseOption, label)
##    Figure:
      exp1__guess_hit_interaction_figure <- exp1__guess_hit_figure_data %>%
          ggplot() +
          aes(x = StimuliFormat, color = ResponseOption, group = ResponseOption, y = emmean) +
          stat_summary(fun.y = mean, geom = "point", size = 2.4, shape = 15) +
          stat_summary(fun.y = mean, geom = "line", size = 1.2) +
          geom_text(size = 4, aes(label = label, color = ResponseOption), nudge_x = 0.08, hjust = 0,
                    data = exp1__guess_hit_interaction_figure_labels) +
          scale_color_manual(values = c('#8ec6c5', '#7d9ab5', '#8566aa')) +
          labs(x = "Stimuli-format", y = "Mean proportion of hits assigned:  'Guessing'") +
          scale_y_continuous(limits = c(0, 1),
                             breaks = c(0, 0.10, 0.20, 0.30, 0.40, 0.50, 0.60, 0.70, 0.80, 0.90, 1),
                             expand = c(0, 0)) +
          theme_classic() +
          theme(legend.position = "none",
                axis.title.x = element_text(size = 10, vjust = -4),
                axis.text.x = element_text(size = 10),
                axis.title.y = element_text(size = 10, vjust = 6),
                axis.text.y = element_text(size = 10),
                plot.background = element_rect(size = 0.5, linetype = 'solid', colour = "black"),
                plot.margin = margin(20, 20, 24, 30))
```






```{r, include=FALSE, warning = FALSE, message=FALSE, cache=TRUE}
###################################################################################################################
##    Analysis - Prop Hits ANOVA:                                                                                ##
###################################################################################################################
      exp1__hit_anova_data <- exp1__full_data %>%
          select(id, ResponseOption, prop_pic_hit, prop_word_hit) %>%
          rename(picture = "prop_pic_hit", word = "prop_word_hit") %>%
          gather(key = "StimuliFormat", value = "hit", picture, word) %>%
          ungroup() %>%
          mutate_at(vars("id", "ResponseOption", "StimuliFormat"), factor) %>%
          mutate(StimuliFormat = str_replace(StimuliFormat, "word", "Words")) %>%
          mutate(StimuliFormat = str_replace(StimuliFormat, "picture", "Pictures")) %>%
          transform(StimuliFormat = factor(StimuliFormat, levels=c("Words","Pictures"))) %>%
          transform(ResponseOption = factor(ResponseOption, levels=c("RFG","RFBG", "RF_Ratings")))
##    2-way mixed ANOVA:
      exp1__anova_prop_hit <- aov_ez("id", "hit", exp1__hit_anova_data, 
                                     between = "ResponseOption", within = "StimuliFormat")
##    Post-hoc contrasts:
##    Stimuli-format:
      exp1__anova_prop_hit_stim_format_mmeans <- emmeans(exp1__anova_prop_hit, ~ StimuliFormat)
      exp1__anova_prop_hit_stim_format_pairwise <- pairs(exp1__anova_prop_hit_stim_format_mmeans)
##    Response-option:
      exp1__anova_prop_hit_resp_option_mmeans <- emmeans(exp1__anova_prop_hit, ~ ResponseOption)
      exp1__anova_prop_hit_resp_option_pairwise <- pairs(exp1__anova_prop_hit_resp_option_mmeans)
##    Interaction means (for figure): 
      exp1__anova_prop_hit_interaction_mmeans <- 
        emmeans(exp1__anova_prop_hit, c("ResponseOption", "StimuliFormat"))
###################################################################################################################
##    Analysis - Prop FA ANOVA:                                                                                  ##
###################################################################################################################
      exp1__FA_anova_data <- exp1__full_data %>%
          select(id, ResponseOption, prop_pic_FA, prop_word_FA) %>%
          rename(picture = "prop_pic_FA", word = "prop_word_FA") %>%
          gather(key = "StimuliFormat", value = "FA", picture, word) %>%
          ungroup() %>%
          mutate_at(vars("id", "ResponseOption", "StimuliFormat"), factor) %>% 
          mutate(StimuliFormat = str_replace(StimuliFormat, "word", "Words")) %>%
          mutate(StimuliFormat = str_replace(StimuliFormat, "picture", "Pictures")) %>%
          transform(StimuliFormat = factor(StimuliFormat, levels=c("Words","Pictures"))) %>%
          transform(ResponseOption = factor(ResponseOption, levels=c("RFG","RFBG", "RF_Ratings")))
##    2-way mixed ANOVA:
      exp1__anova_prop_FA <- aov_ez("id", "FA", exp1__FA_anova_data, 
                                    between = "ResponseOption", within = "StimuliFormat")
##    Post-hoc contrasts:
##    Stimuli-format:
      exp1__anova_prop_FA_stim_format_mmeans <- emmeans(exp1__anova_prop_FA, ~ StimuliFormat)
      exp1__anova_prop_FA_stim_format_pairwise <- pairs(exp1__anova_prop_FA_stim_format_mmeans)
###################################################################################################################
##    Analysis - Overall recognition:                                                                            ##
###################################################################################################################
      exp1__overall_recog_anova_data <- exp1__full_data %>%
          select(id, ResponseOption, pic_recog, word_recog) %>%
          rename(picture = "pic_recog", word = "word_recog") %>%
          gather(key = "StimuliFormat", value = "recog", picture, word) %>%
          ungroup() %>%
          mutate_at(vars("id", "ResponseOption", "StimuliFormat"), factor) %>%
          mutate(StimuliFormat = str_replace(StimuliFormat, "word", "Words")) %>%
          mutate(StimuliFormat = str_replace(StimuliFormat, "picture", "Pictures")) %>%
          transform(StimuliFormat = factor(StimuliFormat, levels=c("Words","Pictures"))) %>%
          transform(ResponseOption = factor(ResponseOption, levels=c("RFG","RFBG", "RF_Ratings")))
##    2-way mixed ANOVA:
      exp1__anova_prop_recog <- aov_ez("id", "recog", exp1__overall_recog_anova_data, 
                                       between = "ResponseOption", within = "StimuliFormat")
##    Post-hoc contrasts:
##    Stimuli-format:
      exp1__anova_prop_recog_stim_format_mmeans <- emmeans(exp1__anova_prop_recog, ~ StimuliFormat)
      exp1__anova_prop_recog_stim_format_pairwise <- pairs(exp1__anova_prop_recog_stim_format_mmeans)
###################################################################################################################
##    Analysis - d' and c:                                                                                       ##
###################################################################################################################
      exp1__dprime_anova_data <- exp1__full_data %>%
          select(id, ResponseOption, exp1__pic_d_prime, exp1__word_d_prime) %>%
          rename(picture = "exp1__pic_d_prime", word = "exp1__word_d_prime") %>%
          gather(key = "StimuliFormat", value = "dprime", picture, word) %>%
          ungroup() %>%
          mutate_at(vars("id", "ResponseOption", "StimuliFormat"), factor) %>%
          mutate(StimuliFormat = str_replace(StimuliFormat, "word", "Words")) %>%
          mutate(StimuliFormat = str_replace(StimuliFormat, "picture", "Pictures")) %>%
          transform(StimuliFormat = factor(StimuliFormat, levels=c("Words","Pictures"))) %>%
          transform(ResponseOption = factor(ResponseOption, levels=c("RFG","RFBG", "RF_Ratings")))
##    2-way mixed ANOVA:
      exp1__anova_prop_dprime <- aov_ez("id", "dprime", exp1__dprime_anova_data, 
                                        between = "ResponseOption", within = "StimuliFormat")
##    Post-hoc contrasts:
##    Stimuli-format:
      exp1__anova_prop_dprime_stim_format_mmeans <- emmeans(exp1__anova_prop_dprime, ~ StimuliFormat)
      exp1__anova_prop_dprime_stim_format_pairwise <- pairs(exp1__anova_prop_dprime_stim_format_mmeans)
#------------------------------------------------------------------------------------------------------------------
      exp1__c_anova_data <- exp1__full_data %>%
          select(id, ResponseOption, pic_c, word_c) %>%
          rename(picture = "pic_c", word = "word_c") %>%
          gather(key = "StimuliFormat", value = "c", picture, word) %>%
          ungroup() %>%
          mutate_at(vars("id", "ResponseOption", "StimuliFormat"), factor) %>%
          mutate(StimuliFormat = str_replace(StimuliFormat, "word", "Words")) %>%
          mutate(StimuliFormat = str_replace(StimuliFormat, "picture", "Pictures")) %>%
          transform(StimuliFormat = factor(StimuliFormat, levels=c("Words","Pictures"))) %>%
          transform(ResponseOption = factor(ResponseOption, levels=c("RFG","RFBG", "RF_Ratings")))
##    2-way mixed ANOVA:
      exp1__anova_prop_c <- aov_ez("id", "c", exp1__c_anova_data, 
                                   between = "ResponseOption", within = "StimuliFormat")
##    Post-hoc contrasts:
##    Stimuli-format:
      exp1__anova_prop_c_resp_option_mmeans <- emmeans(exp1__anova_prop_c, ~ ResponseOption)
      exp1__anova_prop_c_resp_option_pairwise <- pairs(exp1__anova_prop_c_resp_option_mmeans)
###################################################################################################################
##    Analysis - Prop Rec hits ANOVA:                                                                            ##
###################################################################################################################
      exp1__rec_hit_anova_data <- exp1__full_data %>%
          select(id, ResponseOption, total_prop_pic_hit_rec, total_prop_word_hit_rec) %>%
          rename(picture = "total_prop_pic_hit_rec", word = "total_prop_word_hit_rec") %>%
          gather(key = "StimuliFormat", value = "rec_hit", picture, word) %>%
          ungroup() %>%
          mutate_at(vars("id", "ResponseOption", "StimuliFormat"), factor) %>%
          mutate(StimuliFormat = str_replace(StimuliFormat, "word", "Words")) %>%
          mutate(StimuliFormat = str_replace(StimuliFormat, "picture", "Pictures")) %>%
          transform(StimuliFormat = factor(StimuliFormat, levels=c("Words","Pictures"))) %>%
          transform(ResponseOption = factor(ResponseOption, levels=c("RFG","RFBG", "RF_Ratings")))

##    2-way mixed ANOVA:
      exp1__anova_prop_rec_hit <- aov_ez("id", "rec_hit", exp1__rec_hit_anova_data, between = "ResponseOption",
                                         within = "StimuliFormat")

##    Post-hoc contrasts:
##    Stimuli-format:
      exp1__anova_prop_rec_hit_stim_format_mmeans <- emmeans(exp1__anova_prop_rec_hit, ~ StimuliFormat)
      exp1__anova_prop_rec_hit_stim_format_pairwise <- pairs(exp1__anova_prop_rec_hit_stim_format_mmeans)

##    Response-options:
      exp1__anova_prop_rec_hit_resp_option_mmeans <- emmeans(exp1__anova_prop_rec_hit, ~ ResponseOption)
      exp1__anova_prop_rec_hit_resp_option_pairwise <- pairs(exp1__anova_prop_rec_hit_resp_option_mmeans)

##    Interaction: 
      exp1__anova_prop_rec_hit_interaction_mmeans <- 
        emmeans(exp1__anova_prop_rec_hit, c("ResponseOption", "StimuliFormat"))
      exp1__anova_prop_rec_hit_interaction_pairwise_respoption <- 
          emmeans(exp1__anova_prop_rec_hit, "ResponseOption", by = "StimuliFormat")
      exp1__anova_prop_rec_hit_interaction_pairwise_respoption <- 
          pairs(exp1__anova_prop_rec_hit_interaction_pairwise_respoption)
      exp1__anova_prop_rec_hit_interaction_pairwise_stimformat <- 
          emmeans(exp1__anova_prop_rec_hit, "StimuliFormat", by = "ResponseOption")
      exp1__anova_prop_rec_hit_interaction_pairwise_stimformat <- 
          pairs(exp1__anova_prop_rec_hit_interaction_pairwise_stimformat)
###################################################################################################################
##    Analysis - Prop Fam hits ANOVA:                                                                            ##
###################################################################################################################
      exp1__fam_hit_anova_data <- exp1__full_data %>%
          select(id, ResponseOption, total_prop_pic_hit_fam, total_prop_word_hit_fam) %>%
          rename(picture = "total_prop_pic_hit_fam", word = "total_prop_word_hit_fam") %>%
          gather(key = "StimuliFormat", value = "fam_hit", picture, word) %>%
          ungroup() %>%
          mutate_at(vars("id", "ResponseOption", "StimuliFormat"), factor) %>%
          mutate(StimuliFormat = str_replace(StimuliFormat, "word", "Words")) %>%
          mutate(StimuliFormat = str_replace(StimuliFormat, "picture", "Pictures")) %>%
          transform(StimuliFormat = factor(StimuliFormat, levels=c("Words","Pictures"))) %>%
          transform(ResponseOption = factor(ResponseOption, levels=c("RFG","RFBG", "RF_Ratings")))

##    2-way mixed ANOVA:
      exp1__anova_prop_fam_hit <- aov_ez("id", "fam_hit", exp1__fam_hit_anova_data, 
                                         between = "ResponseOption", within = "StimuliFormat")
##    Post-hoc contrasts:
##    Stimuli-format:
      exp1__anova_prop_fam_hit_stim_format_mmeans <- emmeans(exp1__anova_prop_fam_hit, ~ StimuliFormat)
      exp1__anova_prop_fam_hit_stim_format_pairwise <- pairs(exp1__anova_prop_fam_hit_stim_format_mmeans)
##    Response-options:
      exp1__anova_prop_fam_hit_resp_option_mmeans <- emmeans(exp1__anova_prop_fam_hit, ~ ResponseOption)
      exp1__anova_prop_fam_hit_resp_option_pairwise <- pairs(exp1__anova_prop_fam_hit_resp_option_mmeans)
##    Interaction: 
      exp1__anova_prop_fam_hit_interaction_mmeans <- 
          emmeans(exp1__anova_prop_fam_hit, c("ResponseOption", "StimuliFormat"))
      exp1__anova_prop_fam_hit_interaction_pairwise_respoption <- 
          emmeans(exp1__anova_prop_fam_hit, "ResponseOption", by = "StimuliFormat")
      exp1__anova_prop_fam_hit_interaction_pairwise_respoption <- 
          pairs(exp1__anova_prop_fam_hit_interaction_pairwise_respoption)
      exp1__anova_prop_fam_hit_interaction_pairwise_stimformat <- 
          emmeans(exp1__anova_prop_fam_hit, "StimuliFormat", by = "ResponseOption")
      exp1__anova_prop_fam_hit_interaction_pairwise_stimformat <- 
          pairs(exp1__anova_prop_fam_hit_interaction_pairwise_stimformat)
###################################################################################################################
##    Analysis - Prop Guess hits ANOVA:                                                                          ##
###################################################################################################################
      exp1__guess_hit_anova_data <- exp1__full_data %>%
          select(id, ResponseOption, prop_pic_hit_guess, prop_word_hit_guess) %>%
          rename(picture = "prop_pic_hit_guess", word = "prop_word_hit_guess") %>%
          gather(key = "StimuliFormat", value = "guess_hit", picture, word) %>%
          ungroup() %>%
          mutate_at(vars("id", "ResponseOption", "StimuliFormat"), factor) %>%
          mutate(StimuliFormat = str_replace(StimuliFormat, "word", "Words")) %>%
          mutate(StimuliFormat = str_replace(StimuliFormat, "picture", "Pictures")) %>%
          transform(StimuliFormat = factor(StimuliFormat, levels=c("Words","Pictures"))) %>%
          transform(ResponseOption = factor(ResponseOption, levels=c("RFG","RFBG", "RF_Ratings")))

##    2-way mixed ANOVA:
      exp1__anova_prop_guess_hit <- aov_ez("id", "guess_hit", exp1__guess_hit_anova_data, 
                                           between = "ResponseOption", within = "StimuliFormat")
##    Post-hoc contrasts:
##    Stimuli-format:
      exp1__anova_prop_guess_hit_stim_format_mmeans <- emmeans(exp1__anova_prop_guess_hit, ~ StimuliFormat)
      exp1__anova_prop_guess_hit_stim_format_pairwise <- pairs(exp1__anova_prop_guess_hit_stim_format_mmeans)
##    Response-options:
      exp1__anova_prop_guess_hit_resp_option_mmeans <- emmeans(exp1__anova_prop_guess_hit, ~ ResponseOption)
      exp1__anova_prop_guess_hit_resp_option_pairwise <- pairs(exp1__anova_prop_guess_hit_resp_option_mmeans)
##    Interaction (not significant, but used in bar chart):
      exp1__anova_prop_guess_hit_interaction_mmeans <- 
          emmeans(exp1__anova_prop_guess_hit, c("ResponseOption", "StimuliFormat"))
      exp1__anova_prop_guess_hit_interaction_pairwise_respoption <- 
          emmeans(exp1__anova_prop_guess_hit, "ResponseOption", by = "StimuliFormat")
      exp1__anova_prop_guess_hit_interaction_pairwise_respoption <- 
          pairs(exp1__anova_prop_guess_hit_interaction_pairwise_respoption)
      exp1__anova_prop_guess_hit_interaction_pairwise_stimformat <- 
          emmeans(exp1__anova_prop_guess_hit, "StimuliFormat", by = "ResponseOption")
      exp1__anova_prop_guess_hit_interaction_pairwise_stimformat <- 
          pairs(exp1__anova_prop_guess_hit_interaction_pairwise_stimformat)
###################################################################################################################
##    Analysis - Prop Rec FA ANOVA:                                                                              ##
###################################################################################################################
      exp1__anova_prop_rec_FA <- exp1__full_data %>%
          select(id, ResponseOption, total_prop_pic_FA_rec, total_prop_word_FA_rec) %>%
          rename(picture = "total_prop_pic_FA_rec", word = "total_prop_word_FA_rec") %>%
          gather(key = "StimuliFormat", value = "rec_FA", picture, word) %>%
          ungroup() %>%
          mutate_at(vars("id", "ResponseOption", "StimuliFormat"), factor) %>%
          mutate(StimuliFormat = str_replace(StimuliFormat, "word", "Words")) %>%
          mutate(StimuliFormat = str_replace(StimuliFormat, "picture", "Pictures")) %>%
          transform(StimuliFormat = factor(StimuliFormat, levels=c("Words","Pictures"))) %>%
          transform(ResponseOption = factor(ResponseOption, levels=c("RFG","RFBG", "RF_Ratings")))
##    2-way mixed ANOVA:
      exp1__anova_prop_rec_FA <- aov_ez("id", "rec_FA", exp1__anova_prop_rec_FA, 
                                        between = "ResponseOption", within = "StimuliFormat")
##    Post-hoc contrasts:
##    Response-options:
      exp1__anova_prop_rec_FA_resp_option_mmeans <- emmeans(exp1__anova_prop_rec_FA, ~ ResponseOption)
      exp1__anova_prop_rec_FA_resp_option_pairwise <- pairs(exp1__anova_prop_rec_FA_resp_option_mmeans)
##    Interaction:
      exp1__anova_prop_rec_FA_interaction_mmeans <- 
          emmeans(exp1__anova_prop_rec_FA, c("ResponseOption", "StimuliFormat"))
      exp1__anova_prop_rec_FA_interaction_pairwise <- pairs(exp1__anova_prop_rec_FA_interaction_mmeans)
      exp1__anova_prop_rec_FA_interaction_mmeans <- 
          emmeans(exp1__anova_prop_rec_FA, c("ResponseOption", "StimuliFormat"))
      exp1__anova_prop_rec_FA_interaction_pairwise_respoption <- 
          emmeans(exp1__anova_prop_rec_FA, "ResponseOption", by = "StimuliFormat")
      exp1__anova_prop_rec_FA_interaction_pairwise_respoption <-
          pairs(exp1__anova_prop_rec_FA_interaction_pairwise_respoption)
      exp1__anova_prop_rec_FA_interaction_pairwise_stimformat <- 
          emmeans(exp1__anova_prop_rec_FA, "StimuliFormat", by = "ResponseOption")
      exp1__anova_prop_rec_FA_interaction_pairwise_stimformat <-
          pairs(exp1__anova_prop_rec_FA_interaction_pairwise_stimformat)
###################################################################################################################
##    Analysis - Prop Fam FA ANOVA:                                                                              ##
###################################################################################################################
      exp1__anova_prop_fam_FA <- exp1__full_data %>%
          select(id, ResponseOption, total_prop_pic_FA_fam, total_prop_word_FA_fam) %>%
          rename(picture = "total_prop_pic_FA_fam", word = "total_prop_word_FA_fam") %>%
          gather(key = "StimuliFormat", value = "fam_FA", picture, word) %>%
          ungroup() %>%
          mutate_at(vars("id", "ResponseOption", "StimuliFormat"), factor) %>%
          mutate(StimuliFormat = str_replace(StimuliFormat, "word", "Words")) %>%
          mutate(StimuliFormat = str_replace(StimuliFormat, "picture", "Pictures")) %>%
          transform(StimuliFormat = factor(StimuliFormat, levels=c("Words","Pictures"))) %>%
          transform(ResponseOption = factor(ResponseOption, levels=c("RFG","RFBG", "RF_Ratings")))
##    2-way mixed ANOVA:
      exp1__anova_prop_fam_FA <- aov_ez("id", "fam_FA", exp1__anova_prop_fam_FA, 
                                        between = "ResponseOption", within = "StimuliFormat")
##    Interaction:
      exp1__anova_prop_fam_FA_interaction_mmeans <- 
          emmeans(exp1__anova_prop_fam_FA, c("ResponseOption", "StimuliFormat"))
      exp1__anova_prop_fam_FA_interaction_pairwise <- pairs(exp1__anova_prop_fam_FA_interaction_mmeans)
###################################################################################################################
##    Analysis - Prop Guess FA ANOVA:                                                                            ##
###################################################################################################################
      exp1__anova_prop_guess_FA <- exp1__full_data %>%
          select(id, ResponseOption, prop_pic_FA_guess, prop_word_FA_guess) %>%
          rename(picture = "prop_pic_FA_guess", word = "prop_word_FA_guess") %>% 
          gather(key = "StimuliFormat", value = "guess_FA", picture, word) %>%
          ungroup() %>%
          mutate_at(vars("id", "ResponseOption", "StimuliFormat"), factor) %>%
          mutate(StimuliFormat = str_replace(StimuliFormat, "word", "Words")) %>%
          mutate(StimuliFormat = str_replace(StimuliFormat, "picture", "Pictures")) %>%
          transform(StimuliFormat = factor(StimuliFormat, levels=c("Words","Pictures"))) %>%
          transform(ResponseOption = factor(ResponseOption, levels=c("RFG","RFBG", "RF_Ratings"))) 

##    2-way mixed ANOVA:
      exp1__anova_prop_guess_FA <- aov_ez("id", "guess_FA", exp1__anova_prop_guess_FA,
                                          between = "ResponseOption", within = "StimuliFormat")
##    Post-hoc contrasts:
##    Response-option:
      exp1__anova_prop_guess_FA_resp_option_mmeans <- emmeans(exp1__anova_prop_guess_FA, ~ ResponseOption)
      exp1__anova_prop_guess_FA_resp_option_pairwise <- pairs(exp1__anova_prop_guess_FA_resp_option_mmeans)
##    Interaction:
      exp1__anova_prop_guess_FA_interaction_mmeans <- 
          emmeans(exp1__anova_prop_guess_FA, c("ResponseOption", "StimuliFormat"))
      exp1__anova_prop_guess_FA_interaction_pairwise <- pairs(exp1__anova_prop_guess_FA_interaction_mmeans)
```


### Overall hits, false alarms (FAs), and recognition
Separate 2 (stimuli format: words, pictures) x 3 (response-option condition: RFG-judgements, RFBG-judgements, RF-ratings) mixed ANOVAs were conducted on the mean proportion of hits and false alarms (FAs; see `r table_numbering("exp1__hit_and_FA_caption", display = "cite")`).

`r table_numbering("exp1__hit_and_FA_caption")`
```{r, echo=FALSE, cache=FALSE}
    exp1__table_hits_and_FAs %>%
        kable("latex", booktabs = T) %>%
        kable_styling(latex_options = "hold_position") %>%
        pack_rows("Stimuli-format", 1, 2) %>%
        pack_rows("Response-option", 3, 5) %>%
        column_spec(1, width = "4cm")
```


```{r, echo=FALSE, cache=TRUE}
##    Total hits:
      exp1__apa_anova_prop_hit <-
          papaja:::apa_print.afex_aov(exp1__anova_prop_hit)
    
##    Main effects:
      exp1__apa_anova_prop_hit$full$StimuliFormat <- exp1__apa_anova_prop_hit$full$StimuliFormat
      exp1__apa_anova_prop_hit$full$ResponseOption <- exp1__apa_anova_prop_hit$full$ResponseOption
      exp1__apa_anova_prop_hit$full$ResponseOption_StimuliFormat <- 
          exp1__apa_anova_prop_hit$full$ResponseOption_StimuliFormat

##    Pairwise (stim-format):
      exp1__apa_anova_prop_hit_stim_format_mmeans <- 
          papaja:::apa_print.emmGrid(exp1__anova_prop_hit_stim_format_mmeans)
      exp1__pics_prop_hit_mean <- exp1__apa_anova_prop_hit_stim_format_mmeans$estimate$Pictures %>%
          str_remove("\\,.*")
      exp1__words_prop_hit_mean <- exp1__apa_anova_prop_hit_stim_format_mmeans$estimate$Words %>%
          str_remove("\\,.*")
      exp1__apa_anova_prop_hit_stim_format_pairwise <- 
          papaja:::apa_print.emmGrid(exp1__anova_prop_hit_stim_format_pairwise)
      exp1__pics_words_hit_ttest <- exp1__apa_anova_prop_hit_stim_format_pairwise$full %>%
          str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")

##    Pairwise (resp-option):
      exp1__apa_anova_prop_hit_resp_option_mmeans <-
          papaja:::apa_print.emmGrid(exp1__anova_prop_hit_resp_option_mmeans)
        exp1__rfg_prop_hit_mean <- exp1__apa_anova_prop_hit_resp_option_mmeans$estimate$RFG %>%
            str_remove("\\,.*")
        exp1__rfbg_prop_hit_mean <- exp1__apa_anova_prop_hit_resp_option_mmeans$estimate$RFBG %>%
            str_remove("\\,.*")
        exp1__rfratings_prop_hit_mean <- exp1__apa_anova_prop_hit_resp_option_mmeans$estimate$RF_Ratings %>%
            str_remove("\\,.*")
        exp1__apa_anova_prop_hit_resp_option_pairwise <- 
            papaja:::apa_print.emmGrid(exp1__anova_prop_hit_resp_option_pairwise)
        exp1__rfg_rfr_hit_ttest <- exp1__apa_anova_prop_hit_resp_option_pairwise$full$RFG_RF_Ratings %>%
            str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")
```
&nbsp;

In the ANOVA on the proportion of hits, there was a significant main effect of stimuli-format, `r exp1__apa_anova_prop_hit$full$StimuliFormat`;  pictures (`r exp1__pics_prop_hit_mean`) produced a higher number of hits than words (`r exp1__words_prop_hit_mean`), `r exp1__pics_words_hit_ttest`, supporting the notion that stimuli-format plays a role in item recognition. There was also a significant main effect of response-option condition, `r exp1__apa_anova_prop_hit$full$ResponseOption`, with the RFG group (`r exp1__rfg_prop_hit_mean`) showing more hits compared to the RF-Ratings group (`r exp1__rfratings_prop_hit_mean`), `r exp1__rfg_rfr_hit_ttest`, suggesting fewer available response-options may facilitate accurate recognition. There were no significant interaction effects, `r exp1__apa_anova_prop_hit$full$ResponseOption_StimuliFormat`. Click here to see output: [Appendix A - ANOVA Prop hits][].

\newpage
```{r, echo=FALSE, cache=TRUE}
##    Total FAs:
      exp1__apa_anova_prop_FA <- papaja:::apa_print.afex_aov(exp1__anova_prop_FA)
##    Main effects:
      exp1__apa_anova_prop_FA$full$StimuliFormat <- exp1__apa_anova_prop_FA$full$StimuliFormat
      exp1__apa_anova_prop_FA$full$ResponseOption <- exp1__apa_anova_prop_FA$full$ResponseOption
      exp1__apa_anova_prop_FA$full$ResponseOption_StimuliFormat <- 
          exp1__apa_anova_prop_FA$full$ResponseOption_StimuliFormat
##    Pairwise (stim-format):
      exp1__apa_anova_prop_FA_stim_format_mmeans <- 
          papaja:::apa_print.emmGrid(exp1__anova_prop_FA_stim_format_mmeans)
      exp1__pics_prop_FA_mean <- exp1__apa_anova_prop_FA_stim_format_mmeans$estimate$Pictures %>% 
          str_remove("\\,.*")
      exp1__words_prop_FA_mean <- exp1__apa_anova_prop_FA_stim_format_mmeans$estimate$Words %>% 
          str_remove("\\,.*")
      exp1__apa_anova_prop_FA_stim_format_pairwise <- 
          papaja:::apa_print.emmGrid(exp1__anova_prop_FA_stim_format_pairwise)
      exp1__pics_words_FA_ttest <- exp1__apa_anova_prop_FA_stim_format_pairwise$full %>% 
          str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")
```





```{r, include=FALSE, warning = FALSE, message=FALSE, cache=TRUE}



##    Prep data for figures:  
      exp1__rec_FA_figure_data <- as.tibble(exp1__anova_prop_rec_FA_interaction_mmeans) %>%
          select(-df, -lower.CL, -upper.CL)

##    Labels (replaces plot legend):
      exp1__rec_FA_interaction_figure_labels <- exp1__rec_FA_figure_data %>%
          select(StimuliFormat, ResponseOption, emmean) %>%
          filter(StimuliFormat == "Pictures") %>%
          mutate(label = case_when(
              ResponseOption == "RFG" ~ "RFG",
              ResponseOption == "RFBG" ~ "RFBG",
              ResponseOption == "RF_Ratings" ~ "RF Ratings")) %>%
          group_by(StimuliFormat, ResponseOption, label) %>%
          mutate(emmean=replace(emmean, ResponseOption=="RFG", 0.13)) %>%
          mutate(emmean=replace(emmean, ResponseOption=="RFBG", 0.16)) %>%
          mutate(emmean=replace(emmean, ResponseOption=="RF Ratings", 0.2))
      
      
##    Prep data for figures:  
      exp1__guess_FA_figure_data <- as.tibble(exp1__anova_prop_guess_FA_interaction_mmeans) %>%
          select(-df, -lower.CL, -upper.CL)
##    Prep data for figures:  
      exp1__fam_FA_figure_data <- as.tibble(exp1__anova_prop_fam_FA_interaction_mmeans) %>%
          select(-df, -lower.CL, -upper.CL)
      
###################################################################################################################
##    FA figure:                                                                                                 ##
###################################################################################################################
      exp1__FA_figure_data <- tribble(~"ResponseOption", ~"StimuliFormat", ~"rfg", ~"emmean", ~"SE",
          as.character(pull(exp1__rec_FA_figure_data[1,1])), 
          as.character(pull(exp1__rec_FA_figure_data[1,2])), "Recollection",
          as.double(pull(exp1__rec_FA_figure_data[1,3])), as.double(pull(exp1__rec_FA_figure_data[1,4])),
          as.character(pull(exp1__rec_FA_figure_data[2,1])), 
          as.character(pull(exp1__rec_FA_figure_data[2,2])), "Recollection",
          as.double(pull(exp1__rec_FA_figure_data[2,3])), as.double(pull(exp1__rec_FA_figure_data[2,4])),
          as.character(pull(exp1__rec_FA_figure_data[3,1])), 
          as.character(pull(exp1__rec_FA_figure_data[3,2])), "Recollection",
          as.double(pull(exp1__rec_FA_figure_data[3,3])), as.double(pull(exp1__rec_FA_figure_data[3,4])),
          as.character(pull(exp1__rec_FA_figure_data[4,1])), 
          as.character(pull(exp1__rec_FA_figure_data[4,2])), "Recollection",
          as.double(pull(exp1__rec_FA_figure_data[4,3])), as.double(pull(exp1__rec_FA_figure_data[4,4])),
          as.character(pull(exp1__rec_FA_figure_data[5,1])), 
          as.character(pull(exp1__rec_FA_figure_data[5,2])), "Recollection",
          as.double(pull(exp1__rec_FA_figure_data[5,3])), as.double(pull(exp1__rec_FA_figure_data[5,4])),
          as.character(pull(exp1__rec_FA_figure_data[6,1])), 
          as.character(pull(exp1__rec_FA_figure_data[6,2])), "Recollection",
          as.double(pull(exp1__rec_FA_figure_data[6,3])), as.double(pull(exp1__rec_FA_figure_data[6,4])),
          as.character(pull(exp1__fam_FA_figure_data[1,1])), 
          as.character(pull(exp1__fam_FA_figure_data[1,2])), "Familiarity",
          as.double(pull(exp1__fam_FA_figure_data[1,3])), as.double(pull(exp1__fam_FA_figure_data[1,4])),
          as.character(pull(exp1__fam_FA_figure_data[2,1])), 
          as.character(pull(exp1__fam_FA_figure_data[2,2])), "Familiarity",
          as.double(pull(exp1__fam_FA_figure_data[2,3])), as.double(pull(exp1__fam_FA_figure_data[2,4])),
          as.character(pull(exp1__fam_FA_figure_data[3,1])), 
          as.character(pull(exp1__fam_FA_figure_data[3,2])), "Familiarity",
          as.double(pull(exp1__fam_FA_figure_data[3,3])), as.double(pull(exp1__fam_FA_figure_data[3,4])),
          as.character(pull(exp1__fam_FA_figure_data[4,1])), 
          as.character(pull(exp1__fam_FA_figure_data[4,2])), "Familiarity",
          as.double(pull(exp1__fam_FA_figure_data[4,3])), as.double(pull(exp1__fam_FA_figure_data[4,4])),
          as.character(pull(exp1__fam_FA_figure_data[5,1])), 
          as.character(pull(exp1__fam_FA_figure_data[5,2])), "Familiarity",
          as.double(pull(exp1__fam_FA_figure_data[5,3])), as.double(pull(exp1__fam_FA_figure_data[5,4])),
          as.character(pull(exp1__fam_FA_figure_data[6,1])), 
          as.character(pull(exp1__fam_FA_figure_data[6,2])), "Familiarity",
          as.double(pull(exp1__fam_FA_figure_data[6,3])), as.double(pull(exp1__fam_FA_figure_data[6,4])),
          as.character(pull(exp1__guess_FA_figure_data[1,1])), 
          as.character(pull(exp1__guess_FA_figure_data[1,2])), "Guessing",
          as.double(pull(exp1__guess_FA_figure_data[1,3])), as.double(pull(exp1__guess_FA_figure_data[1,4])),
          as.character(pull(exp1__guess_FA_figure_data[2,1])), 
          as.character(pull(exp1__guess_FA_figure_data[2,2])), "Guessing",
          as.double(pull(exp1__guess_FA_figure_data[2,3])), as.double(pull(exp1__guess_FA_figure_data[2,4])),
          as.character(pull(exp1__guess_FA_figure_data[3,1])), 
          as.character(pull(exp1__guess_FA_figure_data[3,2])), "Guessing",
          as.double(pull(exp1__guess_FA_figure_data[3,3])), as.double(pull(exp1__guess_FA_figure_data[3,4])),
          as.character(pull(exp1__guess_FA_figure_data[4,1])), 
          as.character(pull(exp1__guess_FA_figure_data[4,2])), "Guessing",
          as.double(pull(exp1__guess_FA_figure_data[4,3])), as.double(pull(exp1__guess_FA_figure_data[4,4])),
          as.character(pull(exp1__guess_FA_figure_data[5,1])), 
          as.character(pull(exp1__guess_FA_figure_data[5,2])), "Guessing",
          as.double(pull(exp1__guess_FA_figure_data[5,3])), as.double(pull(exp1__guess_FA_figure_data[5,4])),
          as.character(pull(exp1__guess_FA_figure_data[6,1])), 
          as.character(pull(exp1__guess_FA_figure_data[6,2])), "Guessing",
          as.double(pull(exp1__guess_FA_figure_data[6,3])), as.double(pull(exp1__guess_FA_figure_data[6,4]))) %>%
          transform(ResponseOption = factor(ResponseOption, levels=c("RFG","RFBG","RF_Ratings"))) %>%
          transform(rfg = factor(rfg, levels=c("Recollection","Familiarity","Guessing"))) %>%
          transform(StimuliFormat = factor(StimuliFormat, levels=c("Words","Pictures")))

      exp1__FA_figure <- ggplot(exp1__FA_figure_data, aes(x = StimuliFormat, y = emmean, fill = rfg)) +
          scale_fill_manual("legend", values = c("Recollection" = "#1B4251", "Familiarity" = "#6A6C93", 
                                                 "Guessing" = "#D491CA")) + 
          geom_col(position = position_dodge()) +
          geom_errorbar(aes(ymin = emmean-SE, ymax = emmean+SE), width = 0.2, size = 0.3, 
                        position = position_dodge(0.9)) +
          facet_wrap(~ResponseOption, strip.position = "bottom") +
          labs(x = "Response-option condition", y = "Mean proportion of FAs") +
          scale_y_continuous(expand = c(0, 0), limits = c(0, 1)) + 
          theme_classic() +
          theme(
              strip.placement = "outside",
              strip.background = element_rect(fill = "white", size = 0.5, linetype = "solid", colour = "black"),
              axis.title.x = element_text(vjust=-4),    # Move x-axis label further away from the figure.
              axis.title.y = element_text(vjust=6),     # Move y-axis label further away from the figure.
              axis.text.x = element_text(size = 9),
              axis.text.y = element_text(size = 9),
              legend.background = element_rect(fill = "white", size = 0.2, linetype = "solid", colour = "black"),
              legend.title = element_blank(),
              legend.position = c(0.5, 0.896),
              legend.margin = margin(6, 6, 6, 6),
              legend.spacing.y = unit(-1, "pt"),
              plot.background = element_rect(size = 0.5, linetype = 'solid', colour = "black"),
              plot.margin = margin(20, 20, 24, 30))
```


The ANOVA on the proportion of FAs also highlights the role of stimuli-format on the memorability of items, with a significant main effect of stimuli-format `r exp1__apa_anova_prop_FA$full$StimuliFormat` showing words (`r exp1__words_prop_FA_mean`) produced more FAs than pictures (`r exp1__pics_prop_FA_mean`), `r exp1__pics_words_FA_ttest`. There was no significant main effect of response-option condition, `r exp1__apa_anova_prop_FA$full$ResponseOption`, or significant interaction, `r exp1__apa_anova_prop_FA$full$ResponseOption_StimuliFormat`. Click here to see output: [Appendix B - ANOVA Prop FAs][].

```{r, echo=FALSE, cache=TRUE}
##    Recog:
      exp1__apa_anova_prop_recog <- papaja:::apa_print.afex_aov(exp1__anova_prop_recog)
##    Main effects:
      exp1__apa_anova_prop_recog$full$StimuliFormat <- exp1__apa_anova_prop_recog$full$StimuliFormat
      exp1__apa_anova_prop_recog$full$ResponseOption <- exp1__apa_anova_prop_recog$full$ResponseOption
      exp1__apa_anova_prop_recog$full$ResponseOption_StimuliFormat <- 
          exp1__apa_anova_prop_recog$full$ResponseOption_StimuliFormat

##    Pairwise (stim-format):
      exp1__apa_anova_prop_recog_stim_format_mmeans <- 
          papaja:::apa_print.emmGrid(exp1__anova_prop_recog_stim_format_mmeans)
      exp1__pics_prop_recog_mean <- exp1__apa_anova_prop_recog_stim_format_mmeans$estimate$Pictures %>% 
          str_remove("\\,.*")
      exp1__words_prop_recog_mean <- exp1__apa_anova_prop_recog_stim_format_mmeans$estimate$Words %>% 
          str_remove("\\,.*")
      exp1__apa_anova_prop_recog_stim_format_pairwise <- 
          papaja:::apa_print.emmGrid(exp1__anova_prop_recog_stim_format_pairwise)
      exp1__pics_words_recog_ttest <- exp1__apa_anova_prop_recog_stim_format_pairwise$full %>% 
          str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")
```

A similar pattern was again reflected in the ANOVA on overall performance accuracy; a significant main effect of stimuli-format `r exp1__apa_anova_prop_recog$full$StimuliFormat` revealed that pictures (`r exp1__pics_prop_recog_mean`) showed an increased overall task performance accuracy  compared with words (`r exp1__words_prop_recog_mean`), `r exp1__pics_words_recog_ttest`. There was no significant main effect of response-option condition, `r exp1__apa_anova_prop_recog$full$ResponseOption`, or significant interaction, `r exp1__apa_anova_prop_recog$full$ResponseOption_StimuliFormat`. Click here to see output: [Appendix C - ANOVA Overall recognition][].

```{r echo=FALSE, results = FALSE, cache=FALSE}
      table_numbering("exp1__dprime_and_c_caption", "Mean d' and c scores by 
                      stimuli-format and response-option condition.", display = FALSE)
```

### Discrimination (d') and response bias (c)
To assess the roles of discrimination and response bias, separate 2 (stimuli format: words, pictures) x 3 (response-option condition: RFG-judgements, RFBG-judgements, RF-ratings) mixed ANOVAs were conducted on d (d-prime; measure of sensitivity)  and c-scores (decision criterion; see `r table_numbering("exp1__dprime_and_c_caption", display = "cite")`).

`r table_numbering("dprime_and_c_caption")`
```{r, echo=FALSE, cache=TRUE}
      exp1__table_dprime_and_c %>%
          kable("latex", booktabs = T) %>%
          kable_styling(latex_options = "hold_position") %>%
          pack_rows("Stimuli-format", 1, 2) %>%
          pack_rows("Response-option", 3, 5) %>%
          column_spec(1, width = "4cm")
```

```{r, echo=FALSE, cache=TRUE}
##    d':
      exp1__apa_anova_prop_dprime <- papaja:::apa_print.afex_aov(exp1__anova_prop_dprime)

##    Main effects:
      exp1__apa_anova_prop_dprime$full$StimuliFormat <- exp1__apa_anova_prop_dprime$full$StimuliFormat
      exp1__apa_anova_prop_dprime$full$ResponseOption <- exp1__apa_anova_prop_dprime$full$ResponseOption
      exp1__apa_anova_prop_dprime$full$ResponseOption_StimuliFormat <- 
          exp1__apa_anova_prop_dprime$full$ResponseOption_StimuliFormat

##    Pairwise (stim-format):
      exp1__apa_anova_prop_dprime_stim_format_mmeans <- 
          papaja:::apa_print.emmGrid(exp1__anova_prop_dprime_stim_format_mmeans)
      exp1__pics_prop_dprime_mean <- exp1__apa_anova_prop_dprime_stim_format_mmeans$estimate$Pictures %>% 
          str_remove("\\,.*")
      exp1__words_prop_dprime_mean <- exp1__apa_anova_prop_dprime_stim_format_mmeans$estimate$Words %>% 
          str_remove("\\,.*")
      exp1__apa_anova_prop_dprime_stim_format_pairwise <- 
          papaja:::apa_print.emmGrid(exp1__anova_prop_dprime_stim_format_pairwise)
      exp1__pics_words_dprime_ttest <- exp1__apa_anova_prop_dprime_stim_format_pairwise$full %>% 
          str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")
```

The ANOVA on d' scores was consistent with the hits, FAs, and overall recognition findings; there was a significant main effect of stimuli-format, `r exp1__apa_anova_prop_dprime$full$StimuliFormat` showing pictures (`r exp1__pics_prop_dprime_mean`) facilitated better discrimination between hits and FAs than words (`r exp1__words_prop_dprime_mean`), `r exp1__pics_words_dprime_ttest`. There was again no significant main effect of response-option condition, `r exp1__apa_anova_prop_dprime$full$ResponseOption`, or significant interaction, `r exp1__apa_anova_prop_dprime$full$ResponseOption_StimuliFormat`. Click here to see output: [Appendix D - ANOVA d' (discrimination)][].

```{r, echo=FALSE, cache=TRUE}
##    d':
      exp1__apa_anova_prop_c <- papaja:::apa_print.afex_aov(exp1__anova_prop_c)

##    Main effects:
      exp1__apa_anova_prop_c$full$StimuliFormat <- exp1__apa_anova_prop_c$full$StimuliFormat
      exp1__apa_anova_prop_c$full$ResponseOption <- exp1__apa_anova_prop_c$full$ResponseOption
      exp1__apa_anova_prop_c$full$ResponseOption_StimuliFormat <- 
          exp1__apa_anova_prop_c$full$ResponseOption_StimuliFormat
  
##    Pairwise (resp-option):
      exp1__apa_anova_prop_c_resp_option_mmeans <- 
          papaja:::apa_print.emmGrid(exp1__anova_prop_c_resp_option_mmeans)
      exp1__rfg_c_mean <- exp1__apa_anova_prop_c_resp_option_mmeans$estimate$RFG %>% str_remove("\\,.*")
      exp1__rfbg_c_mean <- exp1__apa_anova_prop_c_resp_option_mmeans$estimate$RFBG %>% str_remove("\\,.*")
      exp1__rfr_c_mean <- exp1__apa_anova_prop_c_resp_option_mmeans$estimate$RF_Ratings %>% str_remove("\\,.*")
      exp1__apa_anova_prop_c_resp_option_pairwise <- 
          papaja:::apa_print.emmGrid(exp1__anova_prop_c_resp_option_pairwise)
      exp1__rfg_rfr_c_ttest <- exp1__apa_anova_prop_c_resp_option_pairwise$full$RFG_RF_Ratings %>% 
          str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")
```

In the ANOVA on c-scores, there was no significant main effect of stimuli-format, `r exp1__apa_anova_prop_c$full$StimuliFormat`, indicating response bias was unaffected regardless of whether participants were responding to words or pictures. There was, however, a significant main effect of response-option condition, `r exp1__apa_anova_prop_c$full$ResponseOption`; those in the RF-Ratings condition (`r exp1__rfr_c_mean`) showed higher c-scores (and thus a more conservative response bias) than those in the RFG condition (`r exp1__rfg_c_mean`), `r exp1__rfg_rfr_c_ttest`, suggesting participants were less likely to respond "Old" when they were required to provide more detailed follow-up recognition judgements (Recollection: 0-5 / Familiarity: 0-5), compared to simply selecting one of three options (R,F, or G). There were no significant interaction effects, `r exp1__apa_anova_prop_c$full$ResponseOption_StimuliFormat`. Click here to see output: [Appendix E - ANOVA c (bias)][].

### Hits assigned Recollection, Familiarity, and Guessing
To determine the effects of stimuli-format and response-option on accurate recognition memory judgements, separate 2 (stimuli format: words, pictures) x 3 (response-option condition: RFG-judgements, RFBG-judgements, RF-ratings) mixed ANOVAs were conducted on the mean proportion of hits assigned Recollection, Familiarity, and Guessing (see `r figure_numbering("exp1__prop_hit_caption", display = "cite")`). 
```{r echo=FALSE, results = FALSE, cache=FALSE}
      figure_numbering("exp1__prop_hit_caption", "Proportion of hits assigned 
                       Recollection, Familiarity, and Guessing, by stimuli-format and 
                       response-option condition.", display = FALSE)
```

```{r fig.width=7, fig.height=5.5, echo=FALSE}
      exp1__hit_figure
```
`r figure_numbering("exp1__prop_hit_caption")`

#### Recollection

```{r, echo=FALSE, cache=TRUE}
##    Recollection hits:
      exp1__apa_anova_prop_rec_hit <- papaja:::apa_print.afex_aov(exp1__anova_prop_rec_hit)

##    Main effects:
      exp1__apa_anova_prop_rec_hit$full$StimuliFormat <- exp1__apa_anova_prop_rec_hit$full$StimuliFormat
      exp1__apa_anova_prop_rec_hit$full$ResponseOption <- exp1__apa_anova_prop_rec_hit$full$ResponseOption
      exp1__apa_anova_prop_rec_hit$full$ResponseOption_StimuliFormat <-
          exp1__apa_anova_prop_rec_hit$full$ResponseOption_StimuliFormat

##    Pairwise (stim-format):
      exp1__apa_anova_prop_rec_hit_stim_format_mmeans <- 
          papaja:::apa_print.emmGrid(exp1__anova_prop_rec_hit_stim_format_mmeans)
      exp1__pics_prop_rec_hit_mean <- exp1__apa_anova_prop_rec_hit_stim_format_mmeans$estimate$Pictures %>% 
          str_remove("\\,.*")
      exp1__words_prop_rec_hit_mean <- exp1__apa_anova_prop_rec_hit_stim_format_mmeans$estimate$Words %>% 
          str_remove("\\,.*")
      exp1__apa_anova_prop_rec_hit_stim_format_pairwise <- 
          papaja:::apa_print.emmGrid(exp1__anova_prop_rec_hit_stim_format_pairwise)
      exp1__pics_words_rec_hit_ttest <- exp1__apa_anova_prop_rec_hit_stim_format_pairwise$full %>% 
          str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")

##    Pairwise (resp-option):
      exp1__apa_anova_prop_rec_hit_resp_option_mmeans <- 
          papaja:::apa_print.emmGrid(exp1__anova_prop_rec_hit_resp_option_mmeans)
      exp1__rfg_rec_hit_mean <- exp1__apa_anova_prop_rec_hit_resp_option_mmeans$estimate$RFG %>% 
          str_remove("\\,.*")
      exp1__rfbg_rec_hit_mean <- exp1__apa_anova_prop_rec_hit_resp_option_mmeans$estimate$RFBG %>% 
          str_remove("\\,.*")
      exp1__rfr_rec_hit_mean <- exp1__apa_anova_prop_rec_hit_resp_option_mmeans$estimate$RF_Ratings %>% 
          str_remove("\\,.*")
      exp1__apa_anova_prop_rec_hit_resp_option_pairwise <- 
          papaja:::apa_print.emmGrid(exp1__anova_prop_rec_hit_resp_option_pairwise)

      exp1__rfg_rfbg_rec_hit_ttest <- exp1__apa_anova_prop_rec_hit_resp_option_pairwise$full$RFG_RFBG %>%
          str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")
      exp1__rfg_rfr_rec_hit_ttest <- exp1__apa_anova_prop_rec_hit_resp_option_pairwise$full$RFG_RF_Ratings %>%
          str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")  
      exp1__rfbg_rfr_rec_hit_ttest <- exp1__apa_anova_prop_rec_hit_resp_option_pairwise$full$RFBG_RF_Ratings %>%
          str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")  
```

The ANOVA on Recollected hits revealed a significant main effect of stimuli-format, `r exp1__apa_anova_prop_rec_hit$full$StimuliFormat`, with pictures (`r exp1__pics_prop_rec_hit_mean`) showing a higher proportion of Recollected hits than words (`r exp1__words_prop_rec_hit_mean`), `r exp1__pics_words_rec_hit_ttest` - consistent with the previous findings to suggest an enhanced memorability in pictures compared to words. There was also a significant main effect of response-option, `r exp1__apa_anova_prop_rec_hit$full$ResponseOption`; the RF-Ratings group (`r exp1__rfr_rec_hit_mean`) showed significantly more Recollected hits compared to both the RFG-group (`r exp1__rfg_rec_hit_mean`), `r exp1__rfg_rfr_rec_hit_ttest`, and the RFBG-group (`r exp1__rfbg_rec_hit_mean`), `r exp1__rfbg_rfr_rec_hit_ttest`. There were no significant interaction effects, `r exp1__apa_anova_prop_rec_hit$full$ResponseOption_StimuliFormat`. Click here to see output: [Appendix F - ANOVA Rec hits][].

#### Familiarity

```{r, echo=FALSE, cache=TRUE}
##    Familiarity hits:
      exp1__apa_anova_prop_fam_hit <- papaja:::apa_print.afex_aov(exp1__anova_prop_fam_hit)
##    Main effects:
      exp1__apa_anova_prop_fam_hit$full$StimuliFormat <- exp1__apa_anova_prop_fam_hit$full$StimuliFormat
      exp1__apa_anova_prop_fam_hit$full$ResponseOption <- exp1__apa_anova_prop_fam_hit$full$ResponseOption
      exp1__apa_anova_prop_fam_hit$full$ResponseOption_StimuliFormat <- 
          exp1__apa_anova_prop_fam_hit$full$ResponseOption_StimuliFormat

##    Pairwise (stim-format):
      exp1__apa_anova_prop_fam_hit_stim_format_mmeans <- 
          papaja:::apa_print.emmGrid(exp1__anova_prop_fam_hit_stim_format_mmeans)
      exp1__pics_prop_fam_hit_mean <- exp1__apa_anova_prop_fam_hit_stim_format_mmeans$estimate$Pictures %>% 
          str_remove("\\,.*")
      exp1__words_prop_fam_hit_mean <- exp1__apa_anova_prop_fam_hit_stim_format_mmeans$estimate$Words %>% 
          str_remove("\\,.*")
      exp1__apa_anova_prop_fam_hit_stim_format_pairwise <- 
          papaja:::apa_print.emmGrid(exp1__anova_prop_fam_hit_stim_format_pairwise)
      exp1__pics_words_fam_hit_ttest <- exp1__apa_anova_prop_fam_hit_stim_format_pairwise$full %>% 
          str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")

##    Pairwise (resp-option):
      exp1__apa_anova_prop_fam_hit_resp_option_mmeans <- 
          papaja:::apa_print.emmGrid(exp1__anova_prop_fam_hit_resp_option_mmeans)
      exp1__rfg_fam_hit_mean <- exp1__apa_anova_prop_fam_hit_resp_option_mmeans$estimate$RFG %>% 
          str_remove("\\,.*")
      exp1__rfbg_fam_hit_mean <- exp1__apa_anova_prop_fam_hit_resp_option_mmeans$estimate$RFBG %>% 
          str_remove("\\,.*")
      exp1__rfr_fam_hit_mean <- exp1__apa_anova_prop_fam_hit_resp_option_mmeans$estimate$RF_Ratings %>% 
          str_remove("\\,.*")
      exp1__apa_anova_prop_fam_hit_resp_option_pairwise <- 
          papaja:::apa_print.emmGrid(exp1__anova_prop_fam_hit_resp_option_pairwise)
  
      exp1__rfg_rfbg_fam_hit_ttest <- exp1__apa_anova_prop_fam_hit_resp_option_pairwise$full$RFG_RFBG %>%
          str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")
      exp1__rfg_rfr_fam_hit_ttest <- exp1__apa_anova_prop_fam_hit_resp_option_pairwise$full$RFG_RF_Ratings %>%
          str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")
      exp1__rfbg_rfr_fam_hit_ttest <- exp1__apa_anova_prop_fam_hit_resp_option_pairwise$full$RFBG_RF_Ratings %>%
          str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")  
  
##    Pairwise (interaction):
      exp1__apa_anova_prop_fam_hit_interaction_mmeans <- 
          papaja:::apa_print.emmGrid(exp1__anova_prop_fam_hit_interaction_mmeans)
      exp1__rfg_words_fam_hit_mean <- exp1__apa_anova_prop_fam_hit_interaction_mmeans$estimate$RFG_Words %>% 
          str_remove("\\,.*")
      exp1__rfg_pics_fam_hit_mean <- exp1__apa_anova_prop_fam_hit_interaction_mmeans$estimate$RFG_Pictures %>% 
          str_remove("\\,.*")
      exp1__rfbg_words_fam_hit_mean <- exp1__apa_anova_prop_fam_hit_interaction_mmeans$estimate$RFBG_Words %>% 
          str_remove("\\,.*")
      exp1__rfbg_pics_fam_hit_mean <- exp1__apa_anova_prop_fam_hit_interaction_mmeans$estimate$RFBG_Pictures %>% 
          str_remove("\\,.*")
      exp1__rfr_words_fam_hit_mean <- 
          exp1__apa_anova_prop_fam_hit_interaction_mmeans$estimate$RF_Ratings_Words %>% 
          str_remove("\\,.*")
      exp1__rfr_pics_fam_hit_mean <- 
          exp1__apa_anova_prop_fam_hit_interaction_mmeans$estimate$RF_Ratings_Pictures %>% 
          str_remove("\\,.*")
  
      exp1__apa_anova_prop_fam_hit_interaction_pairwise_stimformat <-
          papaja:::apa_print.emmGrid(exp1__anova_prop_fam_hit_interaction_pairwise_stimformat)
      exp1__apa_anova_prop_fam_hit_interaction_pairwise_respoption <-
          papaja:::apa_print.emmGrid(exp1__anova_prop_fam_hit_interaction_pairwise_respoption)
```

In the ANOVA on Familiarity hits, there was again a significant main effect of stimuli-format, `r exp1__apa_anova_prop_fam_hit$full$StimuliFormat`;  words (`r exp1__words_prop_fam_hit_mean`) resulted in a higher proportion of familiarity hits than pictures (`r exp1__pics_prop_fam_hit_mean`), `r exp1__pics_words_fam_hit_ttest`, indicating that - when correctly recognised - words were not recognised in the the same context-rich nature as pictures. There was also a significant main effect of response-option, `r exp1__apa_anova_prop_fam_hit$full$ResponseOption`, with the RF-ratings group (`r exp1__rfr_fam_hit_mean`) showing more Familiarity hits than both the RFG-group (`r exp1__rfg_fam_hit_mean`), `r exp1__rfg_rfr_fam_hit_ttest`, and the RFBG-group (`r exp1__rfbg_fam_hit_mean`), `r exp1__rfbg_rfr_fam_hit_ttest`. The RFBG-group (`r exp1__rfbg_fam_hit_mean`) also showed significantly more Familiarity hits compared with the RFG-group (`r exp1__rfg_fam_hit_mean`), `r exp1__rfg_rfbg_fam_hit_ttest`

There was also a significant interaction, `r exp1__apa_anova_prop_fam_hit$full$ResponseOption_StimuliFormat` (see `r figure_numbering("exp1__fam_hit_interaction_figure_caption", display = "cite")`). Within response-option conditions, words resulted in more Familiarity hits than pictures in both the RFG group (words: `r exp1__rfg_words_fam_hit_mean`; pictures: `r exp1__rfg_pics_fam_hit_mean`), `r exp1__apa_anova_prop_fam_hit_interaction_pairwise_stimformat$statistic$RFG_Words_Pictures`; and RFBG group (words: `r exp1__rfbg_words_fam_hit_mean`; pictures: `r exp1__rfbg_pics_fam_hit_mean`), `r exp1__apa_anova_prop_fam_hit_interaction_pairwise_stimformat$statistic$RFBG_Words_Pictures`. Conversely, the RF-Ratings group showed the opposite pattern, with more Familiarity hits produced for pictures (`r exp1__rfr_pics_fam_hit_mean`) than words (`r exp1__rfr_words_fam_hit_mean`), `r exp1__apa_anova_prop_fam_hit_interaction_pairwise_stimformat$statistic$RF_Ratings_Words_Pictures`. 

Between response-option conditions, word stimuli produced significantly more Familiarity hits in the RF-Ratings group (`r exp1__rfr_words_fam_hit_mean`) compared tothe RFG group (`r exp1__rfg_words_fam_hit_mean`), `r exp1__apa_anova_prop_fam_hit_interaction_pairwise_respoption$statistic$Words_RFG_RF_Ratings`. For pictures, a higher number of Familiarity hits was evident in the RF-Ratings group (`r exp1__rfr_pics_fam_hit_mean`) compared to both the RFG group (`r exp1__rfg_pics_fam_hit_mean`), `r exp1__apa_anova_prop_fam_hit_interaction_pairwise_respoption$statistic$Pictures_RFG_RF_Ratings` and RFBG group (`r exp1__rfbg_pics_fam_hit_mean`), `r exp1__apa_anova_prop_fam_hit_interaction_pairwise_respoption$statistic$Pictures_RFBG_RF_Ratings`. The RFBG group (`r exp1__rfbg_pics_fam_hit_mean`) also showed a significantly higher number of Familiarity hits compared to the RFG group (`r exp1__rfg_pics_fam_hit_mean`), `r exp1__apa_anova_prop_fam_hit_interaction_pairwise_respoption$statistic$Pictures_RFG_RFBG`. Click here to see output: [Appendix G - ANOVA Fam hits][].  

&nbsp;

```{r echo=FALSE, results = FALSE, cache=FALSE}
    figure_numbering("exp1__fam_hit_interaction_figure_caption", "Interaction plot 
                     between stimuli-format and response-option condition for the 
                     mean proportion of hits assigned 'Familiarity'.", 
                     display = FALSE)
```

```{r fig.width=7, fig.height=5.5, echo=FALSE}
    exp1__fam_hit_interaction_figure
```
`r figure_numbering("exp1__fam_hit_interaction_figure_caption")`


#### Guessing  

```{r, echo=FALSE, cache=TRUE}
##  Guessing hits:
    exp1__apa_anova_prop_guess_hit <- papaja:::apa_print.afex_aov(exp1__anova_prop_guess_hit)

##  Main effects:
    exp1__apa_anova_prop_guess_hit$full$StimuliFormat <- exp1__apa_anova_prop_guess_hit$full$StimuliFormat
    exp1__apa_anova_prop_guess_hit$full$ResponseOption <- exp1__apa_anova_prop_guess_hit$full$ResponseOption
  exp1__apa_anova_prop_guess_hit$full$ResponseOption_StimuliFormat <- exp1__apa_anova_prop_guess_hit$full$ResponseOption_StimuliFormat
  
##  Pairwise (stim-format):
    exp1__apa_anova_prop_guess_hit_stim_format_mmeans <- papaja:::apa_print.emmGrid(exp1__anova_prop_guess_hit_stim_format_mmeans)
    exp1__pics_prop_guess_hit_mean <- exp1__apa_anova_prop_guess_hit_stim_format_mmeans$estimate$Pictures %>% str_remove("\\,.*")
    exp1__words_prop_guess_hit_mean <- exp1__apa_anova_prop_guess_hit_stim_format_mmeans$estimate$Words %>% str_remove("\\,.*")
    exp1__apa_anova_prop_guess_hit_stim_format_pairwise <- papaja:::apa_print.emmGrid(exp1__anova_prop_guess_hit_stim_format_pairwise)
    exp1__pics_words_guess_hit_ttest <- exp1__apa_anova_prop_guess_hit_stim_format_pairwise$full %>%
      str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")
  
##  Pairwise (resp-option):
    exp1__apa_anova_prop_guess_hit_resp_option_mmeans <- papaja:::apa_print.emmGrid(exp1__anova_prop_guess_hit_resp_option_mmeans)
   exp1__rfg_guess_hit_mean <- exp1__apa_anova_prop_guess_hit_resp_option_mmeans$estimate$RFG %>% str_remove("\\,.*")
    exp1__rfbg_guess_hit_mean <- exp1__apa_anova_prop_guess_hit_resp_option_mmeans$estimate$RFBG %>% str_remove("\\,.*")
    exp1__rfr_guess_hit_mean <- exp1__apa_anova_prop_guess_hit_resp_option_mmeans$estimate$RF_Ratings %>% str_remove("\\,.*")
    exp1__apa_anova_prop_guess_hit_resp_option_pairwise <- papaja:::apa_print.emmGrid(exp1__anova_prop_guess_hit_resp_option_pairwise)
    
    exp1__rfg_rfbg_guess_hit_ttest <- exp1__apa_anova_prop_guess_hit_resp_option_pairwise$full$RFG_RFBG %>%
      str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")
   exp1__rfg_rfr_guess_hit_ttest <- exp1__apa_anova_prop_guess_hit_resp_option_pairwise$full$RFG_RF_Ratings %>%
      str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")
    exp1__rfbg_rfr_guess_hit_ttest <- exp1__apa_anova_prop_guess_hit_resp_option_pairwise$full$RFBG_RF_Ratings %>%
      str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")  

##  Pairwise (interaction):
    exp1__apa_anova_prop_guess_hit_interaction_mmeans <- papaja:::apa_print.emmGrid(exp1__anova_prop_guess_hit_interaction_mmeans)
    exp1__rfg_words_guess_hit_mean <- exp1__apa_anova_prop_guess_hit_interaction_mmeans$estimate$RFG_Words %>% str_remove("\\,.*")
    exp1__rfg_pics_guess_hit_mean <- exp1__apa_anova_prop_guess_hit_interaction_mmeans$estimate$RFG_Pictures %>% str_remove("\\,.*")
    exp1__rfbg_words_guess_hit_mean <- exp1__apa_anova_prop_guess_hit_interaction_mmeans$estimate$RFBG_Words %>% str_remove("\\,.*")
    exp1__rfbg_pics_guess_hit_mean <- exp1__apa_anova_prop_guess_hit_interaction_mmeans$estimate$RFBG_Pictures %>% str_remove("\\,.*")
    exp1__rfr_words_guess_hit_mean <- exp1__apa_anova_prop_guess_hit_interaction_mmeans$estimate$RF_Ratings_Words %>% str_remove("\\,.*")
  exp1__rfr_pics_guess_hit_mean <- exp1__apa_anova_prop_guess_hit_interaction_mmeans$estimate$RF_Ratings_Pictures %>% str_remove("\\,.*")
   
    exp1__apa_anova_prop_guess_hit_interaction_pairwise_stimformat <-
      papaja:::apa_print.emmGrid(exp1__anova_prop_guess_hit_interaction_pairwise_stimformat)
    exp1__apa_anova_prop_guess_hit_interaction_pairwise_respoption <-
      papaja:::apa_print.emmGrid(exp1__anova_prop_guess_hit_interaction_pairwise_respoption)
```

The ANOVA on Guessing hits again showed a significant main effect of stimuli-format, `r exp1__apa_anova_prop_guess_hit$full$StimuliFormat`, with words (`r exp1__words_prop_guess_hit_mean`) showing more Guessing hits than pictures (`r exp1__pics_prop_guess_hit_mean`), `r exp1__pics_words_guess_hit_ttest` - a finding that aligns with the results for hits assigned Recollection and Familiarity, whereby words appear to not be recognised in the the same context-rich nature as pictures. There was also a significant main effect of response-option, `r exp1__apa_anova_prop_guess_hit$full$ResponseOption`, with the RF-Ratings group (`r exp1__rfr_guess_hit_mean`) showing significantly fewer Guessing hits than both the RFG (`r exp1__rfg_guess_hit_mean`), `r exp1__rfg_rfr_guess_hit_ttest`, and RFBG (`r exp1__rfbg_guess_hit_mean`) groups, `r exp1__rfbg_rfr_guess_hit_ttest`. Despite 'Guessing' responses being permissable in any of the response-option groups, it seems when two independent rating scales were required participants were less likely to report a "Guess". This could be because those in the RF-Ratings condition selected "New" more often than "Old" when they were having a complete guess, or instead, subjects might have opted to report lower levels of Recollection and Familiarity ratings (i.e., 1-3), rather than responding 0 on both scales. 

There was also a significant interaction,`r exp1__apa_anova_prop_guess_hit$full$ResponseOption_StimuliFormat`, (see `r figure_numbering("exp1__guess_hit_interaction_figure_caption", display = "cite")`). Within response-option conditions, words resulted in more Guessing hits than pictures in both the RFG group (words: `r exp1__rfg_words_guess_hit_mean`; pictures: `r exp1__rfg_pics_guess_hit_mean`), `r exp1__apa_anova_prop_guess_hit_interaction_pairwise_stimformat$statistic$RFG_Words_Pictures`; and RFBG group (words: `r exp1__rfbg_words_guess_hit_mean`; pictures: `r exp1__rfbg_pics_guess_hit_mean`), `r exp1__apa_anova_prop_guess_hit_interaction_pairwise_stimformat$statistic$RFBG_Words_Pictures`. 

Between response-option conditions, word stimuli produced significantly fewer Guessing hits in the RF-Ratings group (`r exp1__rfr_words_guess_hit_mean`) compared to both the RFG group (`r exp1__rfg_words_guess_hit_mean`), `r exp1__apa_anova_prop_guess_hit_interaction_pairwise_respoption$statistic$Words_RFG_RF_Ratings`, and the RFBG group (`r exp1__rfbg_words_guess_hit_mean`), `r exp1__apa_anova_prop_guess_hit_interaction_pairwise_respoption$statistic$Words_RFBG_RF_Ratings`. A similar pattern was also evident for pictures, with significantlyfewer of Guessing hits in the RF-Ratings group (`r exp1__rfr_pics_guess_hit_mean`) compared to both the RFG group (`r exp1__rfg_pics_guess_hit_mean`), `r exp1__apa_anova_prop_guess_hit_interaction_pairwise_respoption$statistic$Pictures_RFG_RF_Ratings` and RFBG group (`r exp1__rfbg_pics_guess_hit_mean`), `r exp1__apa_anova_prop_guess_hit_interaction_pairwise_respoption$statistic$Pictures_RFBG_RF_Ratings`. Click here to see output: [Appendix H - ANOVA guess hits][].

```{r echo=FALSE, results = FALSE, cache=FALSE}
    figure_numbering("exp1__guess_hit_interaction_figure_caption", "Interaction plot
                     between stimuli-format and response-option condition for the 
                     mean proportion of hits assigned 'Guessing'.", display = FALSE)
```

```{r fig.width=7, fig.height=5.5, echo=FALSE}
    exp1__guess_hit_interaction_figure
```
`r figure_numbering("exp1__guess_hit_interaction_figure_caption")`

### False alarms (FAs) assigned Recollection, Familiarity, and Guessing
To determine the effects of stimuli-format and response-option on false recognition memory judgements, separate 2 (stimuli format: words, pictures) x 3 (response-option condition: RFG-judgements, RFBG-judgements, RF-ratings) mixed ANOVAs were conducted on the mean proportion of FAs assigned Recollection, Familiarity, and Guessing (see `r figure_numbering("exp1__prop_FA_caption", display = "cite")`). 

&nbsp;

```{r echo=FALSE, results = FALSE, cache=FALSE}
    figure_numbering("exp1__prop_FA_caption", "Proportion of FAs assigned 
                     Recollection, Familiarity, and Guessing, by stimuli-format and 
                     response-option condition.", display = FALSE)
```

```{r fig.width=7, fig.height=5.5, echo=FALSE}
    exp1__FA_figure
```
`r figure_numbering("exp1__prop_FA_caption")`


#### Recollection (FAs)

```{r, echo=FALSE, cache=TRUE}
##  Rec FAs:
    exp1__apa_anova_prop_rec_FA <- papaja:::apa_print.afex_aov(exp1__anova_prop_rec_FA)

##  Main effects:
    exp1__apa_anova_prop_rec_FA$full$StimuliFormat <- exp1__apa_anova_prop_rec_FA$full$StimuliFormat
    exp1__apa_anova_prop_rec_FA$full$ResponseOption <- exp1__apa_anova_prop_rec_FA$full$ResponseOption
    exp1__apa_anova_prop_rec_FA$full$ResponseOption_StimuliFormat <- exp1__apa_anova_prop_rec_FA$full$ResponseOption_StimuliFormat

##  Pairwise (resp-option):
    exp1__apa_anova_prop_rec_FA_resp_option_mmeans <- papaja:::apa_print.emmGrid(exp1__anova_prop_rec_FA_resp_option_mmeans)
    exp1__rfg_rec_FA_mean <- exp1__apa_anova_prop_rec_FA_resp_option_mmeans$estimate$RFG %>% str_remove("\\,.*")
    exp1__rfbg_rec_FA_mean <- exp1__apa_anova_prop_rec_FA_resp_option_mmeans$estimate$RFBG %>% str_remove("\\,.*")
    exp1__rfr_rec_FA_mean <- exp1__apa_anova_prop_rec_FA_resp_option_mmeans$estimate$RF_Ratings %>% str_remove("\\,.*")
    exp1__apa_anova_prop_rec_FA_resp_option_pairwise <- papaja:::apa_print.emmGrid(exp1__anova_prop_rec_FA_resp_option_pairwise)
    
    exp1__rfg_rfbg_rec_FA_ttest <- exp1__apa_anova_prop_rec_FA_resp_option_pairwise$full$RFG_RFBG %>%
      str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")  # T-test.
    exp1__rfg_rfr_rec_FA_ttest <- exp1__apa_anova_prop_rec_FA_resp_option_pairwise$full$RFG_RF_Ratings %>%
      str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")
    exp1__rfbg_rfr_rec_FA_ttest <- exp1__apa_anova_prop_rec_FA_resp_option_pairwise$full$RFBG_RF_Ratings %>%
      str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")
```

In the ANOVA on Recollection FAs, there was no significant main effect of stimuli-format, `r exp1__apa_anova_prop_rec_FA$full$StimuliFormat`, but there was a significant main effect of response-option, `r exp1__apa_anova_prop_rec_FA$full$ResponseOption`, with those in the RF-ratings group (`r exp1__rfr_rec_FA_mean`) showing more Recollection FAs than both the RFG-group (`r exp1__rfg_rec_FA_mean`), `r exp1__rfg_rfr_rec_FA_ttest`, and the RFBG-group (`r exp1__rfbg_rec_FA_mean`), `r exp1__rfbg_rfr_rec_FA_ttest`). 

This could indicate that when subjects were required to individually report Recollection and Familiarity on two 0-5 rating scales, they were more likely to experience (or report) false recognition (accompanied by non-existent contextual details) than when only three (RFG) or four (RFBG) response-options were provided. There were no significant interaction effects, `r exp1__apa_anova_prop_rec_FA$full$ResponseOption_StimuliFormat`.
Click here to see output: [Appendix I - ANOVA Rec FA][].



#### Familiarity (FAs)
   
```{r, echo=FALSE, cache=TRUE}
##  Fam FAs:
    exp1__apa_anova_prop_fam_FA <- papaja:::apa_print.afex_aov(exp1__anova_prop_fam_FA)

##  Main effects:
    exp1__apa_anova_prop_fam_FA$full$StimuliFormat <- exp1__apa_anova_prop_fam_FA$full$StimuliFormat
    exp1__apa_anova_prop_fam_FA$full$ResponseOption <- exp1__apa_anova_prop_fam_FA$full$ResponseOption
    exp1__apa_anova_prop_fam_FA$full$ResponseOption_StimuliFormat <- exp1__apa_anova_prop_fam_FA$full$ResponseOption_StimuliFormat
```

The ANOVA on Familiarity FAs did not yield any significant results; with no significant main effect of stimuli-format, `r exp1__apa_anova_prop_fam_FA$full$StimuliFormat`, no significant main effect of response-option, `r exp1__apa_anova_prop_fam_FA$full$ResponseOption`, and no significant interaction effects, `r exp1__apa_anova_prop_fam_FA$full$ResponseOption_StimuliFormat`. Click here to see output: [Appendix J - ANOVA Fam FA][].

#### Guessing (FAs)

```{r, echo=FALSE, cache=TRUE}
##  Rec FAs:
    exp1__apa_anova_prop_guess_FA <- papaja:::apa_print.afex_aov(exp1__anova_prop_guess_FA)

##  Main effects:
    exp1__apa_anova_prop_guess_FA$full$StimuliFormat <- exp1__apa_anova_prop_guess_FA$full$StimuliFormat
    exp1__apa_anova_prop_guess_FA$full$ResponseOption <- exp1__apa_anova_prop_guess_FA$full$ResponseOption
    exp1__apa_anova_prop_guess_FA$full$ResponseOption_StimuliFormat <- exp1__apa_anova_prop_guess_FA$full$ResponseOption_StimuliFormat

##  Pairwise (resp-option):
    exp1__apa_anova_prop_guess_FA_resp_option_mmeans <- papaja:::apa_print.emmGrid(exp1__anova_prop_guess_FA_resp_option_mmeans)
    exp1__rfg_guess_FA_mean <- exp1__apa_anova_prop_guess_FA_resp_option_mmeans$estimate$RFG %>% str_remove("\\,.*")
    exp1__rfbg_guess_FA_mean <- exp1__apa_anova_prop_guess_FA_resp_option_mmeans$estimate$RFBG %>% str_remove("\\,.*")
    exp1__rfr_guess_FA_mean <- exp1__apa_anova_prop_guess_FA_resp_option_mmeans$estimate$RF_Ratings %>% str_remove("\\,.*")
    exp1__apa_anova_prop_guess_FA_resp_option_pairwise <- papaja:::apa_print.emmGrid(exp1__anova_prop_guess_FA_resp_option_pairwise)               

    exp1__rfg_rfbg_guess_FA_ttest <- exp1__apa_anova_prop_guess_FA_resp_option_pairwise$full$RFG_RFBG %>%
      str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")  # T-test.
    exp1__rfg_rfr_guess_FA_ttest <- exp1__apa_anova_prop_guess_FA_resp_option_pairwise$full$RFG_RF_Ratings %>%
      str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")
    exp1__rfbg_rfr_guess_FA_ttest <- exp1__apa_anova_prop_guess_FA_resp_option_pairwise$full$RFBG_RF_Ratings %>%
      str_remove("^(?:[^\\$]*\\$){6}([^\\$]*)")
```

Finally, the ANOVA on Guessing FAs also showed no significant main effect of stimuli-format, `r exp1__apa_anova_prop_guess_FA$full$StimuliFormat`, but there was a significant main effect of response-option, `r exp1__apa_anova_prop_guess_FA$full$ResponseOption`, with the with the RF-ratings group (`r exp1__rfr_guess_FA_mean`) showing significantly fewer Guessing FAs than both the RFG (`r exp1__rfg_guess_FA_mean`), `r exp1__rfg_rfr_guess_FA_ttest`, and RFBG groups (`r exp1__rfbg_guess_FA_mean`), `r exp1__rfbg_rfr_guess_FA_ttest`. This again aligns with previous results, suggesting that those in the RF-Ratings group were less likely to report guesses than the other groups, whether accurate or not. There were no significant interaction effects, `r exp1__apa_anova_prop_guess_FA$full$ResponseOption_StimuliFormat`. Click here to see output: [Appendix K - ANOVA Guess FA][].