## Notes

- Two-way repeated measures ANOVAs.
  - Main effect of stimuli format (word / drawing / photo);
  - Main effect of distinctiveness (low / high);
  - Interaction. 

- Contrasts:
  - Stim format pairwise (3 tests);
  - Distinctiveness pairwise (1 test);
  - Interaction (*15 tests*):

```{r, echo=FALSE, cache=FALSE}
    exp5__anova__PROP.GUESS.FA__interaction.pairwise %>%
        kable("latex", booktabs = T) %>%
        kable_styling(latex_options = "hold_position")
print("P value adjustment: bonferroni method for 15 tests")
``` 
  

1) Manipulation check (1st Bonferroni pool)

    - Are distinctive words actually more distinctive?
    - If its not significant, might as well stop analysis.
    - low word vs high word.
    


2) Have I established a PSE? (2 + 3 in same Bonferroni pool)
    
    - Must demonstrate a PSE first before we can even begin to check whether any of the sub-conditions can eliminate it. 
        - Main effect of stim format + contrasts:
        - all 3(?)
    - Main effect might not be the only indication of this though (if l
    - Have to do planned contrasts to see if High > Low relationship holds to words. 
    
    (wouldn't do all 3 contrasts. only ever do 2 comparisons (or at least start with 2). if words bigger than        pics) 

3) Have I managed to eliminate PSE in the same way Ensor has?

    - Distinctive words vs. grey drawings (reverse PSE)
    - Distinctive words vs. colour drawings (PSE - reduced)
    
    
4) Have I extended it to photos? (3rd Bonferroni pool)

    - Do they behave differently to each other? Are photos more distinctive than drawings?
        - drawings high vs photos high


\newpage
## Results summary
```{r, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.show='hide'}

    results_summary <- tribble(
      ~"Variable", ~"Stim Format", ~"Distinctiveness", ~"Interaction",
      "Proportion of total hits", "Signif", "", "",
            "", "Photos > drawings and words;", "", "",
            "", "Drawings > Words;", "", "",
            "","","","",
      "Proportion of total FAs", "Signif", "Signif", "Signif",
            "", "Words > drawings and photos;", "Low > High", "",
            "", "Drawings > Photos;", "", "",
            "","","","",
      "Overall recognition", "Signif", "Signif", "Signif",
            "", "Photos > drawings and words;", "High > Low", "", 
            "", "Drawings > Words;", "", "",
                  "","","","",
      "d'", "Signif", "Signif", "Signif",
                  "","","","",
      "c", "Signif", "Signif", "Signif",
                  "","","","",
      "Proportion of Rec hits", "Signif", "Signif", "Signif",
            "", "", "High > Low", "",
                  "","","","",
      "Proportion of Fam hits", "Signif", "Signif", "",
            "", "", "Low > High", "",
                  "","","","",
      "Proportion of Guess hits", "Signif", "Signif (if outliers removed)", "Signif (if outliers removed)",
            "", "", "", "",
                  "","","","",
      "Proportion of Rec FAs", "", "Signif", "",
            "", "", "Low > High", "",
                  "","","","",
      "Proportion of Fam FAs", "Signif", "Signif", "Signif",
            "", "", "Low > High", "",
                  "","","","",
      "Proportion of Guess FAs", "Signif", "Signif", "Signif (if outliers removed)",
            "", "", "Low > High", "",
                  "","","","",
    )
```

```{r, echo=FALSE, cache=FALSE}
    results_summary %>%
        kable("latex", booktabs = T) %>%
        kable_styling(latex_options = c("hold_position", "scale_down")) %>%
        row_spec(1, bold = TRUE) %>%
        row_spec(4, bold = TRUE) %>%
        row_spec(7, bold = TRUE) %>%
        row_spec(10, bold = TRUE) %>%
  row_spec(11, bold = TRUE) %>%
  row_spec(12, bold = TRUE) %>%
  row_spec(14, bold = TRUE) %>%
  row_spec(16, bold = TRUE) %>%
  row_spec(18, bold = TRUE) %>%
  row_spec(20, bold = TRUE) %>%
  row_spec(22, bold = TRUE)
``` 









#----------------------------------------------------------------------------------------------------------------
#   Normality assumption:
#----------------------------------------------------------------------------------------------------------------
#   If your sample size is greater than 50, the normal QQ plot is preferred because at larger sample sizes the 
#   Shapiro-Wilk test becomes very sensitive even to a minor deviation from normality. 
#   exp5__anova__PROP.HITS_data %>%
#   group_by(stim_format) %>%
#   shapiro_test(hit)


ggqqplot(exp5__anova__PROP.FA_data, "FA", facet.by = "stim_format")
    
ggdensity(exp5__anova__PROP.HITS_data, "hit", facet.by = "stim_format")
    
    
    words_shap <- exp5__anova__PROP.HITS_data %>% 
      filter(stim_format == "Words") %>% 
      select(hit) %>% 
      mutate_at(vars(hit), as.numeric)
    
    shapiro.test(words_shap$hit)
    
    drawings_shap <- exp5__anova__PROP.HITS_data %>% 
      filter(stim_format == "Drawings") %>% 
      select(hit) %>% 
      mutate_at(vars(hit), as.numeric)
    
    shapiro.test(drawings_shap$hit)
    
    photos_shap <- exp5__anova__PROP.HITS_data %>% 
      filter(stim_format == "Photos") %>% 
      select(hit) %>% 
      mutate_at(vars(hit), as.numeric)
    
    shapiro.test(photos_shap$hit)
    
#----------------------------------------------------------------------------------------------------------------
#   Assumption of sphericity:
#----------------------------------------------------------------------------------------------------------------
    res.aov <- anova_test(data = exp5__anova__PROP.HITS_data, dv = hit, wid = id, within = stim_format)
    get_anova_table(res.aov)


    
    


##  Planned contrasts:
    ##  (1) = location of distinctive word value, 2nd row.
    ##  (-1) = location of variable for comparison. 
    planned_contrasts <- list(DistWord__vs__GreyWord= c(-1,1,0,0,0,0),
                              DistWord__vs__GreyDrawing = c(0,1,-1,0,0,0),
                              DistWord__vs__GreyPhoto = c(0,1,0,0,-1,0),
                              DistWord__vs__ColDrawing = c(0,1,0,-1,0,0),
                              DistWord__vs__ColPhoto = c(0,1,0,0,0,-1))
    
    exp5__anova__PROP.HITS__planned_contrasts <- emmeans(exp5__anova__PROP.HITS, list(~ stim_format), 
                                                         contr = planned_contrasts, adjust = "bonferroni")
    
    
    
    write.csv(exp5__anova__PROP.HITS_data,'~/Desktop/exp5__anova__PROP.HITS_data.csv', row.names = FALSE)

    
    a <- pairs(emmeans(exp5__anova__PROP.HITS, ~ stim_format))
    
    install.packages("effectsize")
    library(effectsize)
    
    b <- t_to_d(t = c(-1.369,-8.735),
       df_error = 157,
       paired = TRUE)
    
    
    -1.369
    
     
     t <- -1.369
     x <- sqrt(157)
     
     z <- t/x
    
#---------------------------------------------------------------------------------------------------------------#
#   Format results for use in report:                                                                           
#---------------------------------------------------------------------------------------------------------------#
    exp5__apa__anova__PROP.HITS__stim.format.means <-     ##  All means:
        papaja:::apa_print.emmGrid(exp5__anova__PROP.HITS__stim.format.means)
    exp5__apa__anova__PROP.HITS__grey.word.mean <-        ##  Grey words mean:
        exp5__apa__anova__PROP.HITS__stim.format.means$estimate$Greywords %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.HITS__dist.word.mean <-        ##  Distinctive words mean:
        exp5__apa__anova__PROP.HITS__stim.format.means$estimate$Distinctivewords %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.HITS__grey.drawing.mean <-     ##  Grey drawings mean:
        exp5__apa__anova__PROP.HITS__stim.format.means$estimate$Greydrawings %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.HITS__colour.drawing.mean <-   ##  Colour drawings mean:
        exp5__apa__anova__PROP.HITS__stim.format.means$estimate$Colourdrawings %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.HITS__grey.photo.mean <-       ##  Grey photos mean:
        exp5__apa__anova__PROP.HITS__stim.format.means$estimate$Greyphotos %>% str_remove("\\,.*")    
     exp5__apa__anova__PROP.HITS__colour.photo.mean <-    ##  Colour photos mean:
        exp5__apa__anova__PROP.HITS__stim.format.means$estimate$Colourphotos %>% str_remove("\\,.*")   
    
    exp5__apa__anova__PROP.HITS__stim.format.contrasts <- 
        papaja:::apa_print.emmGrid(exp5__anova__PROP.HITS__planned_contrasts$` of stim_format`)
    exp5__apa__anova__PROP.HITS__dist.word.vs.grey.word <-
        exp5__apa__anova__PROP.HITS__stim.format.contrasts$statistic$DistWord_vs_GreyWord
    exp5__apa__anova__PROP.HITS__dist.word.vs.grey.drawing <-
        exp5__apa__anova__PROP.HITS__stim.format.contrasts$statistic$DistWord_vs_GreyDrawing
    exp5__apa__anova__PROP.HITS__dist.word.vs.grey.photo <-
        exp5__apa__anova__PROP.HITS__stim.format.contrasts$statistic$DistWord_vs_GreyPhoto
    exp5__apa__anova__PROP.HITS__dist.word.vs.colour.drawing <-
        exp5__apa__anova__PROP.HITS__stim.format.contrasts$statistic$DistWord_vs_ColDrawing
    exp5__apa__anova__PROP.HITS__dist.word.vs.colour.photo <-
        exp5__apa__anova__PROP.HITS__stim.format.contrasts$statistic$DistWord_vs_ColPhoto
```    


**Were the distinctive words actually distinctive compared to normal words?**
Distinctive words (`r exp5__apa__anova__PROP.HITS__dist.word.mean`) vs. grey words (`r exp5__apa__anova__PROP.HITS__grey.word.mean`), `r exp5__apa__anova__PROP.HITS__dist.word.vs.grey.word`. 

**Were the distinctive words close to grey drawings or photos?**
Distinctive words (`r exp5__apa__anova__PROP.HITS__dist.word.mean`) vs. grey drawings (`r exp5__apa__anova__PROP.HITS__grey.drawing.mean`), `r exp5__apa__anova__PROP.HITS__dist.word.vs.grey.drawing`. 

Distinctive words (`r exp5__apa__anova__PROP.HITS__dist.word.mean`) vs. grey photos (`r exp5__apa__anova__PROP.HITS__grey.photo.mean`), `r exp5__apa__anova__PROP.HITS__dist.word.vs.grey.photo`. 

**Were the distinctive words close to colour drawings or photos?**
Distinctive words (`r exp5__apa__anova__PROP.HITS__dist.word.mean`) vs. colour drawings (`r exp5__apa__anova__PROP.HITS__colour.drawing.mean`), `r exp5__apa__anova__PROP.HITS__dist.word.vs.colour.drawing`.

Distinctive words (`r exp5__apa__anova__PROP.HITS__dist.word.mean`) vs. colour photos (`r exp5__apa__anova__PROP.HITS__colour.photo.mean`), `r exp5__apa__anova__PROP.HITS__dist.word.vs.colour.photo`.


```{r, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.show='hide'}
#################################################################################################################
##    Experiment 5 - Prop FA:                                                                                ##
#################################################################################################################  Prep data for analysis:                                                 
    exp5__anova__PROP.FA_data <- exp5__final_data %>%
        select(id, prop_grey_word_FA, prop_distinctive_word_FA, prop_grey_drawing_FA, 
               prop_col_drawing_FA, prop_grey_photo_FA, prop_col_photo_FA) %>%
        rename("Grey words" = "prop_grey_word_FA", "Distinctive words" = "prop_distinctive_word_FA",
               "Grey drawings" = "prop_grey_drawing_FA", "Colour drawings" = "prop_col_drawing_FA",
               "Grey photos" = "prop_grey_photo_FA", "Colour photos" = "prop_col_photo_FA") %>%
        gather(key = "stim_format", value = "FA", "Grey words", "Distinctive words", "Grey drawings", 
               "Colour drawings", "Grey photos", "Colour photos") %>%
        transform(stim_format = factor(stim_format, levels=c("Grey words", "Distinctive words", 
                                                             "Grey drawings", "Colour drawings", 
                                                             "Grey photos", "Colour photos")))
#----------------------------------------------------------------------------------------------------------------
#   Run 1-way repeated measures ANOVA:
#----------------------------------------------------------------------------------------------------------------
    exp5__anova__PROP.FA <- aov_ez('id', 'FA', exp5__anova__PROP.FA_data, within = "stim_format")

##  Format ANOVA main effect for use in report:
    exp5__apa__anova__PROP.FA <- papaja:::apa_print.afex_aov(exp5__anova__PROP.FA)
    exp5__apa__anova__PROP.FA__stim.format.main.effect <- exp5__apa__anova__PROP.FA$full$stim_format %>%
        str_extract("^(?:[^\\,]*\\,){3}([^\\,]*)")
#---------------------------------------------------------------------------------------------------------------#
#   Run post-hoc contrasts                                                                                      
#---------------------------------------------------------------------------------------------------------------#
##  Stimuli format:
    exp5__anova__PROP.FA__stim.format.means <- emmeans(exp5__anova__PROP.FA, ~ stim_format)
##  Planned contrasts:
    exp5__anova__PROP.FA__planned_contrasts <- emmeans(exp5__anova__PROP.FA, list(~ stim_format), 
                                                         contr = planned_contrasts, adjust = "bonferroni")
#---------------------------------------------------------------------------------------------------------------#
#   Format results for use in report:                                                                           
#---------------------------------------------------------------------------------------------------------------#
    exp5__apa__anova__PROP.FA__stim.format.means <-     ##  All means:
        papaja:::apa_print.emmGrid(exp5__anova__PROP.FA__stim.format.means)
    exp5__apa__anova__PROP.FA__grey.word.mean <-        ##  Grey words mean:
        exp5__apa__anova__PROP.FA__stim.format.means$estimate$Greywords %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.FA__dist.word.mean <-        ##  Distinctive words mean:
        exp5__apa__anova__PROP.FA__stim.format.means$estimate$Distinctivewords %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.FA__grey.drawing.mean <-     ##  Grey drawings mean:
        exp5__apa__anova__PROP.FA__stim.format.means$estimate$Greydrawings %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.FA__colour.drawing.mean <-   ##  Colour drawings mean:
        exp5__apa__anova__PROP.FA__stim.format.means$estimate$Colourdrawings %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.FA__grey.photo.mean <-       ##  Grey photos mean:
        exp5__apa__anova__PROP.FA__stim.format.means$estimate$Greyphotos %>% str_remove("\\,.*")    
     exp5__apa__anova__PROP.FA__colour.photo.mean <-    ##  Colour photos mean:
        exp5__apa__anova__PROP.FA__stim.format.means$estimate$Colourphotos %>% str_remove("\\,.*")   
    
    exp5__apa__anova__PROP.FA__stim.format.contrasts <- 
        papaja:::apa_print.emmGrid(exp5__anova__PROP.FA__planned_contrasts$` of stim_format`)
    exp5__apa__anova__PROP.FA__dist.word.vs.grey.word <-
        exp5__apa__anova__PROP.FA__stim.format.contrasts$statistic$DistWord_vs_GreyWord
    exp5__apa__anova__PROP.FA__dist.word.vs.grey.drawing <-
        exp5__apa__anova__PROP.FA__stim.format.contrasts$statistic$DistWord_vs_GreyDrawing
    exp5__apa__anova__PROP.FA__dist.word.vs.grey.photo <-
        exp5__apa__anova__PROP.FA__stim.format.contrasts$statistic$DistWord_vs_GreyPhoto
    exp5__apa__anova__PROP.FA__dist.word.vs.colour.drawing <-
        exp5__apa__anova__PROP.FA__stim.format.contrasts$statistic$DistWord_vs_ColDrawing
    exp5__apa__anova__PROP.FA__dist.word.vs.colour.photo <-
        exp5__apa__anova__PROP.FA__stim.format.contrasts$statistic$DistWord_vs_ColPhoto
```    

**Were the distinctive words actually distinctive compared to normal words?**
Distinctive words (`r exp5__apa__anova__PROP.FA__dist.word.mean`) vs. grey words (`r exp5__apa__anova__PROP.FA__grey.word.mean`), `r exp5__apa__anova__PROP.FA__dist.word.vs.grey.word`. 

**Were the distinctive words close to grey drawings or photos?**
Distinctive words (`r exp5__apa__anova__PROP.FA__dist.word.mean`) vs. grey drawings (`r exp5__apa__anova__PROP.FA__grey.drawing.mean`), `r exp5__apa__anova__PROP.FA__dist.word.vs.grey.drawing`. 

Distinctive words (`r exp5__apa__anova__PROP.FA__dist.word.mean`) vs. grey photos (`r exp5__apa__anova__PROP.FA__grey.photo.mean`), `r exp5__apa__anova__PROP.FA__dist.word.vs.grey.photo`. 

**Were the distinctive words close to colour drawings or photos?**
Distinctive words (`r exp5__apa__anova__PROP.FA__dist.word.mean`) vs. colour drawings (`r exp5__apa__anova__PROP.FA__colour.drawing.mean`), `r exp5__apa__anova__PROP.FA__dist.word.vs.colour.drawing`.

Distinctive words (`r exp5__apa__anova__PROP.FA__dist.word.mean`) vs. colour photos (`r exp5__apa__anova__PROP.FA__colour.photo.mean`), `r exp5__apa__anova__PROP.FA__dist.word.vs.colour.photo`.

```{r, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.show='hide'}
#################################################################################################################
##    Experiment 5 - Overall recognition:                                                                      ##
#################################################################################################################  Prep data for analysis:                                                 
    exp5__anova__PROP.RECOG_data <- exp5__final_data %>%
        select(id, grey_word_recog, distinctive_word_recog, grey_drawing_recog, 
               col_drawing_recog, grey_photo_recog, col_photo_recog) %>%
        rename("Grey words" = "grey_word_recog", "Distinctive words" = "distinctive_word_recog",
               "Grey drawings" = "grey_drawing_recog", "Colour drawings" = "col_drawing_recog",
               "Grey photos" = "grey_photo_recog", "Colour photos" = "col_photo_recog") %>%
        gather(key = "stim_format", value = "recog", "Grey words", "Distinctive words", "Grey drawings", 
               "Colour drawings", "Grey photos", "Colour photos") %>%
        transform(stim_format = factor(stim_format, levels=c("Grey words", "Distinctive words", 
                                                             "Grey drawings", "Colour drawings", 
                                                             "Grey photos", "Colour photos")))
#----------------------------------------------------------------------------------------------------------------
#   Run 1-way repeated measures ANOVA:
#----------------------------------------------------------------------------------------------------------------
    exp5__anova__PROP.RECOG <- aov_ez('id', 'recog', exp5__anova__PROP.RECOG_data, within = "stim_format")

##  Format ANOVA main effect for use in report:
    exp5__apa__anova__PROP.RECOG <- papaja:::apa_print.afex_aov(exp5__anova__PROP.RECOG)
    exp5__apa__anova__PROP.RECOG__stim.format.main.effect <- exp5__apa__anova__PROP.RECOG$full$stim_format %>%
        str_extract("^(?:[^\\,]*\\,){3}([^\\,]*)")
#---------------------------------------------------------------------------------------------------------------#
#   Run post-hoc contrasts                                                                                      
#---------------------------------------------------------------------------------------------------------------#
##  Stimuli format:
    exp5__anova__PROP.RECOG__stim.format.means <- emmeans(exp5__anova__PROP.RECOG, ~ stim_format)
##  Planned contrasts:    
    exp5__anova__PROP.RECOG__planned_contrasts <- emmeans(exp5__anova__PROP.RECOG, list(~ stim_format), 
                                                         contr = planned_contrasts, adjust = "bonferroni")
#---------------------------------------------------------------------------------------------------------------#
#   Format results for use in report:                                                                           
#---------------------------------------------------------------------------------------------------------------#
    exp5__apa__anova__PROP.RECOG__stim.format.means <-     ##  All means:
        papaja:::apa_print.emmGrid(exp5__anova__PROP.RECOG__stim.format.means)
    exp5__apa__anova__PROP.RECOG__grey.word.mean <-        ##  Grey words mean:
        exp5__apa__anova__PROP.RECOG__stim.format.means$estimate$Greywords %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.RECOG__dist.word.mean <-        ##  Distinctive words mean:
        exp5__apa__anova__PROP.RECOG__stim.format.means$estimate$Distinctivewords %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.RECOG__grey.drawing.mean <-     ##  Grey drawings mean:
        exp5__apa__anova__PROP.RECOG__stim.format.means$estimate$Greydrawings %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.RECOG__colour.drawing.mean <-   ##  Colour drawings mean:
        exp5__apa__anova__PROP.RECOG__stim.format.means$estimate$Colourdrawings %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.RECOG__grey.photo.mean <-       ##  Grey photos mean:
        exp5__apa__anova__PROP.RECOG__stim.format.means$estimate$Greyphotos %>% str_remove("\\,.*")    
     exp5__apa__anova__PROP.RECOG__colour.photo.mean <-    ##  Colour photos mean:
        exp5__apa__anova__PROP.RECOG__stim.format.means$estimate$Colourphotos %>% str_remove("\\,.*")   
    
    exp5__apa__anova__PROP.RECOG__stim.format.contrasts <- 
        papaja:::apa_print.emmGrid(exp5__anova__PROP.RECOG__planned_contrasts$` of stim_format`)
    exp5__apa__anova__PROP.RECOG__dist.word.vs.grey.word <-
        exp5__apa__anova__PROP.RECOG__stim.format.contrasts$statistic$DistWord_vs_GreyWord
    exp5__apa__anova__PROP.RECOG__dist.word.vs.grey.drawing <-
        exp5__apa__anova__PROP.RECOG__stim.format.contrasts$statistic$DistWord_vs_GreyDrawing
    exp5__apa__anova__PROP.RECOG__dist.word.vs.grey.photo <-
        exp5__apa__anova__PROP.RECOG__stim.format.contrasts$statistic$DistWord_vs_GreyPhoto
    exp5__apa__anova__PROP.RECOG__dist.word.vs.colour.drawing <-
        exp5__apa__anova__PROP.RECOG__stim.format.contrasts$statistic$DistWord_vs_ColDrawing
    exp5__apa__anova__PROP.RECOG__dist.word.vs.colour.photo <-
        exp5__apa__anova__PROP.RECOG__stim.format.contrasts$statistic$DistWord_vs_ColPhoto
```    

**Were the distinctive words actually distinctive compared to normal words?**
Distinctive words (`r exp5__apa__anova__PROP.RECOG__dist.word.mean`) vs. grey words (`r exp5__apa__anova__PROP.RECOG__grey.word.mean`), `r exp5__apa__anova__PROP.RECOG__dist.word.vs.grey.word`. 

**Were the distinctive words close to grey drawings or photos?**
Distinctive words (`r exp5__apa__anova__PROP.RECOG__dist.word.mean`) vs. grey drawings (`r exp5__apa__anova__PROP.RECOG__grey.drawing.mean`), `r exp5__apa__anova__PROP.RECOG__dist.word.vs.grey.drawing`. 

Distinctive words (`r exp5__apa__anova__PROP.RECOG__dist.word.mean`) vs. grey photos (`r exp5__apa__anova__PROP.RECOG__grey.photo.mean`), `r exp5__apa__anova__PROP.RECOG__dist.word.vs.grey.photo`. 

**Were the distinctive words close to colour drawings or photos?**
Distinctive words (`r exp5__apa__anova__PROP.RECOG__dist.word.mean`) vs. colour drawings (`r exp5__apa__anova__PROP.RECOG__colour.drawing.mean`), `r exp5__apa__anova__PROP.RECOG__dist.word.vs.colour.drawing`.

Distinctive words (`r exp5__apa__anova__PROP.RECOG__dist.word.mean`) vs. colour photos (`r exp5__apa__anova__PROP.RECOG__colour.photo.mean`), `r exp5__apa__anova__PROP.RECOG__dist.word.vs.colour.photo`.


### Discrimination (d') and response bias (c)
```{r, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.show='hide'}
#################################################################################################################
##    Experiment 5 - d':                                                                                       ##
################################################################################################################# ##  Prep data for analysis:                                                 
    exp5__anova__D.PRIME_data <- exp5__final_data %>%
        select(id, exp5__grey_word_d_prime, exp5__distinctive_word_d_prime, exp5__grey_drawing_d_prime, 
               exp5__col_drawing_d_prime, exp5__grey_photo_d_prime, exp5__col_photo_d_prime) %>%
        rename("Grey words" = "exp5__grey_word_d_prime", "Distinctive words" = "exp5__distinctive_word_d_prime",
               "Grey drawings" = "exp5__grey_drawing_d_prime", "Colour drawings" = "exp5__col_drawing_d_prime",
               "Grey photos" = "exp5__grey_photo_d_prime", "Colour photos" = "exp5__col_photo_d_prime") %>%
        gather(key = "stim_format", value = "d_prime", "Grey words", "Distinctive words", "Grey drawings", 
               "Colour drawings", "Grey photos", "Colour photos") %>%
        transform(stim_format = factor(stim_format, levels=c("Grey words", "Distinctive words", 
                                                             "Grey drawings", "Colour drawings", 
                                                             "Grey photos", "Colour photos")))
#----------------------------------------------------------------------------------------------------------------
#   Run 1-way repeated measures ANOVA:
#----------------------------------------------------------------------------------------------------------------
    exp5__anova__D.PRIME <- aov_ez('id', 'd_prime', exp5__anova__D.PRIME_data, within = "stim_format")

##  Format ANOVA main effect for use in report:
    exp5__apa__anova__D.PRIME <- papaja:::apa_print.afex_aov(exp5__anova__D.PRIME)
    exp5__apa__anova__D.PRIME__stim.format.main.effect <- exp5__apa__anova__D.PRIME$full$stim_format %>%
        str_extract("^(?:[^\\,]*\\,){3}([^\\,]*)")
#---------------------------------------------------------------------------------------------------------------#
#   Run post-hoc contrasts                                                                                      
#---------------------------------------------------------------------------------------------------------------#
##  Stimuli format:
    exp5__anova__D.PRIME__stim.format.means <- emmeans(exp5__anova__D.PRIME, ~ stim_format)
##  Planned contrasts:    
    exp5__anova__D.PRIME__planned_contrasts <- emmeans(exp5__anova__D.PRIME, list(~ stim_format), 
                                                         contr = planned_contrasts, adjust = "bonferroni")
#---------------------------------------------------------------------------------------------------------------#
#   Format results for use in report:                                                                           
#---------------------------------------------------------------------------------------------------------------#
    exp5__apa__anova__D.PRIME__stim.format.means <-     ##  All means:
        papaja:::apa_print.emmGrid(exp5__anova__D.PRIME__stim.format.means)
    exp5__apa__anova__D.PRIME__grey.word.mean <-        ##  Grey words mean:
        exp5__apa__anova__D.PRIME__stim.format.means$estimate$Greywords %>% str_remove("\\,.*")
    exp5__apa__anova__D.PRIME__dist.word.mean <-        ##  Distinctive words mean:
        exp5__apa__anova__D.PRIME__stim.format.means$estimate$Distinctivewords %>% str_remove("\\,.*")
    exp5__apa__anova__D.PRIME__grey.drawing.mean <-     ##  Grey drawings mean:
        exp5__apa__anova__D.PRIME__stim.format.means$estimate$Greydrawings %>% str_remove("\\,.*")
    exp5__apa__anova__D.PRIME__colour.drawing.mean <-   ##  Colour drawings mean:
        exp5__apa__anova__D.PRIME__stim.format.means$estimate$Colourdrawings %>% str_remove("\\,.*")
    exp5__apa__anova__D.PRIME__grey.photo.mean <-       ##  Grey photos mean:
        exp5__apa__anova__D.PRIME__stim.format.means$estimate$Greyphotos %>% str_remove("\\,.*")    
     exp5__apa__anova__D.PRIME__colour.photo.mean <-    ##  Colour photos mean:
        exp5__apa__anova__D.PRIME__stim.format.means$estimate$Colourphotos %>% str_remove("\\,.*")   
    
    exp5__apa__anova__D.PRIME__stim.format.contrasts <- 
        papaja:::apa_print.emmGrid(exp5__anova__D.PRIME__planned_contrasts$` of stim_format`)
    exp5__apa__anova__D.PRIME__dist.word.vs.grey.word <-
        exp5__apa__anova__D.PRIME__stim.format.contrasts$statistic$DistWord_vs_GreyWord
    exp5__apa__anova__D.PRIME__dist.word.vs.grey.drawing <-
        exp5__apa__anova__D.PRIME__stim.format.contrasts$statistic$DistWord_vs_GreyDrawing
    exp5__apa__anova__D.PRIME__dist.word.vs.grey.photo <-
        exp5__apa__anova__D.PRIME__stim.format.contrasts$statistic$DistWord_vs_GreyPhoto
    exp5__apa__anova__D.PRIME__dist.word.vs.colour.drawing <-
        exp5__apa__anova__D.PRIME__stim.format.contrasts$statistic$DistWord_vs_ColDrawing
    exp5__apa__anova__D.PRIME__dist.word.vs.colour.photo <-
        exp5__apa__anova__D.PRIME__stim.format.contrasts$statistic$DistWord_vs_ColPhoto
```    

**Were the distinctive words actually distinctive compared to normal words?**
Distinctive words (`r exp5__apa__anova__D.PRIME__dist.word.mean`) vs. grey words (`r exp5__apa__anova__D.PRIME__grey.word.mean`), `r exp5__apa__anova__D.PRIME__dist.word.vs.grey.word`. 

**Were the distinctive words close to grey drawings or photos?**
Distinctive words (`r exp5__apa__anova__D.PRIME__dist.word.mean`) vs. grey drawings (`r exp5__apa__anova__D.PRIME__grey.drawing.mean`), `r exp5__apa__anova__D.PRIME__dist.word.vs.grey.drawing`. 

Distinctive words (`r exp5__apa__anova__D.PRIME__dist.word.mean`) vs. grey photos (`r exp5__apa__anova__D.PRIME__grey.photo.mean`), `r exp5__apa__anova__D.PRIME__dist.word.vs.grey.photo`. 

**Were the distinctive words close to colour drawings or photos?**
Distinctive words (`r exp5__apa__anova__D.PRIME__dist.word.mean`) vs. colour drawings (`r exp5__apa__anova__D.PRIME__colour.drawing.mean`), `r exp5__apa__anova__D.PRIME__dist.word.vs.colour.drawing`.

Distinctive words (`r exp5__apa__anova__D.PRIME__dist.word.mean`) vs. colour photos (`r exp5__apa__anova__D.PRIME__colour.photo.mean`), `r exp5__apa__anova__D.PRIME__dist.word.vs.colour.photo`.

```{r, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.show='hide'}
#################################################################################################################
##    Experiment 5 - c:                                                                                       ##
################################################################################################################# ##  Prep data for analysis:                                                 
    exp5__anova__C_data <- exp5__final_data %>%
        select(id, grey_word_c, distinctive_word_c, grey_drawing_c, 
               col_drawing_c, grey_photo_c, col_photo_c) %>%
        rename("Grey words" = "grey_word_c", "Distinctive words" = "distinctive_word_c",
               "Grey drawings" = "grey_drawing_c", "Colour drawings" = "col_drawing_c",
               "Grey photos" = "grey_photo_c", "Colour photos" = "col_photo_c") %>%
        gather(key = "stim_format", value = "c", "Grey words", "Distinctive words", "Grey drawings", 
               "Colour drawings", "Grey photos", "Colour photos") %>%
        transform(stim_format = factor(stim_format, levels=c("Grey words", "Distinctive words", 
                                                             "Grey drawings", "Colour drawings", 
                                                             "Grey photos", "Colour photos")))
#----------------------------------------------------------------------------------------------------------------
#   Run 1-way repeated measures ANOVA:
#----------------------------------------------------------------------------------------------------------------
    exp5__anova__C <- aov_ez('id', 'c', exp5__anova__C_data, within = "stim_format")

##  Format ANOVA main effect for use in report:
    exp5__apa__anova__C <- papaja:::apa_print.afex_aov(exp5__anova__C)
    exp5__apa__anova__C__stim.format.main.effect <- exp5__apa__anova__C$full$stim_format %>%
        str_extract("^(?:[^\\,]*\\,){3}([^\\,]*)")
#---------------------------------------------------------------------------------------------------------------#
#   Run post-hoc contrasts                                                                                      
#---------------------------------------------------------------------------------------------------------------#
##  Stimuli format:
    exp5__anova__C__stim.format.means <- emmeans(exp5__anova__C, ~ stim_format)
##  Planned contrasts:    
    exp5__anova__C__planned_contrasts <- emmeans(exp5__anova__C, list(~ stim_format), 
                                                         contr = planned_contrasts, adjust = "bonferroni")
#---------------------------------------------------------------------------------------------------------------#
#   Format results for use in report:                                                                           
#---------------------------------------------------------------------------------------------------------------#
    exp5__apa__anova__C__stim.format.means <-     ##  All means:
        papaja:::apa_print.emmGrid(exp5__anova__C__stim.format.means)
    exp5__apa__anova__C__grey.word.mean <-        ##  Grey words mean:
        exp5__apa__anova__C__stim.format.means$estimate$Greywords %>% str_remove("\\,.*")
    exp5__apa__anova__C__dist.word.mean <-        ##  Distinctive words mean:
        exp5__apa__anova__C__stim.format.means$estimate$Distinctivewords %>% str_remove("\\,.*")
    exp5__apa__anova__C__grey.drawing.mean <-     ##  Grey drawings mean:
        exp5__apa__anova__C__stim.format.means$estimate$Greydrawings %>% str_remove("\\,.*")
    exp5__apa__anova__C__colour.drawing.mean <-   ##  Colour drawings mean:
        exp5__apa__anova__C__stim.format.means$estimate$Colourdrawings %>% str_remove("\\,.*")
    exp5__apa__anova__C__grey.photo.mean <-       ##  Grey photos mean:
        exp5__apa__anova__C__stim.format.means$estimate$Greyphotos %>% str_remove("\\,.*")    
     exp5__apa__anova__C__colour.photo.mean <-    ##  Colour photos mean:
        exp5__apa__anova__C__stim.format.means$estimate$Colourphotos %>% str_remove("\\,.*")   
    
    exp5__apa__anova__C__stim.format.contrasts <- 
        papaja:::apa_print.emmGrid(exp5__anova__C__planned_contrasts$` of stim_format`)
    exp5__apa__anova__C__dist.word.vs.grey.word <-
        exp5__apa__anova__C__stim.format.contrasts$statistic$DistWord_vs_GreyWord
    exp5__apa__anova__C__dist.word.vs.grey.drawing <-
        exp5__apa__anova__C__stim.format.contrasts$statistic$DistWord_vs_GreyDrawing
    exp5__apa__anova__C__dist.word.vs.grey.photo <-
        exp5__apa__anova__C__stim.format.contrasts$statistic$DistWord_vs_GreyPhoto
    exp5__apa__anova__C__dist.word.vs.colour.drawing <-
        exp5__apa__anova__C__stim.format.contrasts$statistic$DistWord_vs_ColDrawing
    exp5__apa__anova__C__dist.word.vs.colour.photo <-
        exp5__apa__anova__C__stim.format.contrasts$statistic$DistWord_vs_ColPhoto
```    

**Were the distinctive words actually distinctive compared to normal words?**
Distinctive words (`r exp5__apa__anova__C__dist.word.mean`) vs. grey words (`r exp5__apa__anova__C__grey.word.mean`), `r exp5__apa__anova__C__dist.word.vs.grey.word`. 

**Were the distinctive words close to grey drawings or photos?**
Distinctive words (`r exp5__apa__anova__C__dist.word.mean`) vs. grey drawings (`r exp5__apa__anova__C__grey.drawing.mean`), `r exp5__apa__anova__C__dist.word.vs.grey.drawing`. 

Distinctive words (`r exp5__apa__anova__C__dist.word.mean`) vs. grey photos (`r exp5__apa__anova__C__grey.photo.mean`), `r exp5__apa__anova__C__dist.word.vs.grey.photo`. 

**Were the distinctive words close to colour drawings or photos?**
Distinctive words (`r exp5__apa__anova__C__dist.word.mean`) vs. colour drawings (`r exp5__apa__anova__C__colour.drawing.mean`), `r exp5__apa__anova__C__dist.word.vs.colour.drawing`.

Distinctive words (`r exp5__apa__anova__C__dist.word.mean`) vs. colour photos (`r exp5__apa__anova__C__colour.photo.mean`), `r exp5__apa__anova__C__dist.word.vs.colour.photo`.

### Hits assigned Recollection, Familiarity, and Guessing
#### Recollection (hits)
```{r, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.show='hide'}
#################################################################################################################
##    Experiment 5 - Rec hits:                                                                                 ##
################################################################################################################# ##  Prep data for analysis:                                                 
    exp5__anova__PROP.REC.HIT_data <- exp5__final_data %>%
        select(id, prop_grey_word_hit_rec, prop_distinctive_word_hit_rec, prop_grey_drawing_hit_rec, 
               prop_col_drawing_hit_rec, prop_grey_photo_hit_rec, prop_col_photo_hit_rec) %>%
        rename("Grey words" = "prop_grey_word_hit_rec", "Distinctive words" = "prop_distinctive_word_hit_rec",
               "Grey drawings" = "prop_grey_drawing_hit_rec", "Colour drawings" = "prop_col_drawing_hit_rec",
               "Grey photos" = "prop_grey_photo_hit_rec", "Colour photos" = "prop_col_photo_hit_rec") %>%
        gather(key = "stim_format", value = "rec_hit", "Grey words", "Distinctive words", "Grey drawings", 
               "Colour drawings", "Grey photos", "Colour photos") %>%
        transform(stim_format = factor(stim_format, levels=c("Grey words", "Distinctive words", 
                                                             "Grey drawings", "Colour drawings", 
                                                             "Grey photos", "Colour photos")))
#----------------------------------------------------------------------------------------------------------------
#   Run 1-way repeated measures ANOVA:
#----------------------------------------------------------------------------------------------------------------
    exp5__anova__PROP.REC.HIT <- aov_ez('id', 'rec_hit', exp5__anova__PROP.REC.HIT_data, within = "stim_format")

##  Format ANOVA main effect for use in report:
    exp5__apa__anova__PROP.REC.HIT <- papaja:::apa_print.afex_aov(exp5__anova__PROP.REC.HIT)
    exp5__apa__anova__PROP.REC.HIT__stim.format.main.effect <- 
      exp5__apa__anova__PROP.REC.HIT$full$stim_format %>% str_extract("^(?:[^\\,]*\\,){3}([^\\,]*)")
#---------------------------------------------------------------------------------------------------------------#
#   Run post-hoc contrasts                                                                                      
#---------------------------------------------------------------------------------------------------------------#
##  Stimuli format:
    exp5__anova__PROP.REC.HIT__stim.format.means <- emmeans(exp5__anova__PROP.REC.HIT, ~ stim_format)
##  Planned contrasts:    
    exp5__anova__PROP.REC.HIT__planned_PROP.REC.HITontrasts <- emmeans(exp5__anova__PROP.REC.HIT, 
                                                                       list(~ stim_format), 
                                                                       contr = planned_contrasts,
                                                                       adjust = "bonferroni")
#---------------------------------------------------------------------------------------------------------------#
#   Format results for use in report:                                                                           
#---------------------------------------------------------------------------------------------------------------#
    exp5__apa__anova__PROP.REC.HIT__stim.format.means <-     ##  All means:
        papaja:::apa_print.emmGrid(exp5__anova__PROP.REC.HIT__stim.format.means)
    exp5__apa__anova__PROP.REC.HIT__grey.word.mean <-        ##  Grey words mean:
        exp5__apa__anova__PROP.REC.HIT__stim.format.means$estimate$Greywords %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.REC.HIT__dist.word.mean <-        ##  Distinctive words mean:
        exp5__apa__anova__PROP.REC.HIT__stim.format.means$estimate$Distinctivewords %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.REC.HIT__grey.drawing.mean <-     ##  Grey drawings mean:
        exp5__apa__anova__PROP.REC.HIT__stim.format.means$estimate$Greydrawings %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.REC.HIT__PROP.REC.HITolour.drawing.mean <-   ##  Colour drawings mean:
        exp5__apa__anova__PROP.REC.HIT__stim.format.means$estimate$Colourdrawings %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.REC.HIT__grey.photo.mean <-       ##  Grey photos mean:
        exp5__apa__anova__PROP.REC.HIT__stim.format.means$estimate$Greyphotos %>% str_remove("\\,.*")    
     exp5__apa__anova__PROP.REC.HIT__PROP.REC.HITolour.photo.mean <-    ##  Colour photos mean:
        exp5__apa__anova__PROP.REC.HIT__stim.format.means$estimate$Colourphotos %>% str_remove("\\,.*")   
    
    exp5__apa__anova__PROP.REC.HIT__stim.format.contrasts <- 
        papaja:::apa_print.emmGrid(exp5__anova__PROP.REC.HIT__planned_PROP.REC.HITontrasts$` of stim_format`)
    exp5__apa__anova__PROP.REC.HIT__dist.word.vs.grey.word <-
        exp5__apa__anova__PROP.REC.HIT__stim.format.contrasts$statistic$DistWord_vs_GreyWord
    exp5__apa__anova__PROP.REC.HIT__dist.word.vs.grey.drawing <-
        exp5__apa__anova__PROP.REC.HIT__stim.format.contrasts$statistic$DistWord_vs_GreyDrawing
    exp5__apa__anova__PROP.REC.HIT__dist.word.vs.grey.photo <-
        exp5__apa__anova__PROP.REC.HIT__stim.format.contrasts$statistic$DistWord_vs_GreyPhoto
    exp5__apa__anova__PROP.REC.HIT__dist.word.vs.colour.drawing <-
        exp5__apa__anova__PROP.REC.HIT__stim.format.contrasts$statistic$DistWord_vs_PROP.REC.HITolDrawing
    exp5__apa__anova__PROP.REC.HIT__dist.word.vs.colour.photo <-
        exp5__apa__anova__PROP.REC.HIT__stim.format.contrasts$statistic$DistWord_vs_PROP.REC.HITolPhoto
```    

**Were the distinctive words actually distinctive compared to normal words?**
Distinctive words (`r exp5__apa__anova__PROP.REC.HIT__dist.word.mean`) vs. grey words (`r exp5__apa__anova__PROP.REC.HIT__grey.word.mean`), `r exp5__apa__anova__PROP.REC.HIT__dist.word.vs.grey.word`. 

**Were the distinctive words close to grey drawings or photos?**
Distinctive words (`r exp5__apa__anova__PROP.REC.HIT__dist.word.mean`) vs. grey drawings (`r exp5__apa__anova__PROP.REC.HIT__grey.drawing.mean`), `r exp5__apa__anova__PROP.REC.HIT__dist.word.vs.grey.drawing`. 

Distinctive words (`r exp5__apa__anova__PROP.REC.HIT__dist.word.mean`) vs. grey photos (`r exp5__apa__anova__PROP.REC.HIT__grey.photo.mean`), `r exp5__apa__anova__PROP.REC.HIT__dist.word.vs.grey.photo`. 

**Were the distinctive words close to colour drawings or photos?**
Distinctive words (`r exp5__apa__anova__PROP.REC.HIT__dist.word.mean`) vs. colour drawings (`r exp5__apa__anova__PROP.REC.HIT__PROP.REC.HITolour.drawing.mean`), `r exp5__apa__anova__PROP.REC.HIT__dist.word.vs.colour.drawing`.

Distinctive words (`r exp5__apa__anova__PROP.REC.HIT__dist.word.mean`) vs. colour photos (`r exp5__apa__anova__PROP.REC.HIT__PROP.REC.HITolour.photo.mean`), `r exp5__apa__anova__PROP.REC.HIT__dist.word.vs.colour.photo`.

#### Familiarity (hits)
```{r, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.show='hide'}
#################################################################################################################
##    Experiment 5 - Fam hits:                                                                                 ##
################################################################################################################# ##  Prep data for analysis:                                                 
    exp5__anova__PROP.FAM.HIT_data <- exp5__final_data %>%
        select(id, prop_grey_word_hit_fam, prop_distinctive_word_hit_fam, prop_grey_drawing_hit_fam, 
               prop_col_drawing_hit_fam, prop_grey_photo_hit_fam, prop_col_photo_hit_fam) %>%
        rename("Grey words" = "prop_grey_word_hit_fam", "Distinctive words" = "prop_distinctive_word_hit_fam",
               "Grey drawings" = "prop_grey_drawing_hit_fam", "Colour drawings" = "prop_col_drawing_hit_fam",
               "Grey photos" = "prop_grey_photo_hit_fam", "Colour photos" = "prop_col_photo_hit_fam") %>%
        gather(key = "stim_format", value = "fam_hit", "Grey words", "Distinctive words", "Grey drawings", 
               "Colour drawings", "Grey photos", "Colour photos") %>%
        transform(stim_format = factor(stim_format, levels=c("Grey words", "Distinctive words", 
                                                             "Grey drawings", "Colour drawings", 
                                                             "Grey photos", "Colour photos")))
#----------------------------------------------------------------------------------------------------------------
#   Run 1-way repeated measures ANOVA:
#----------------------------------------------------------------------------------------------------------------
    exp5__anova__PROP.FAM.HIT <- aov_ez('id', 'fam_hit', exp5__anova__PROP.FAM.HIT_data, within = "stim_format")

##  Format ANOVA main effect for use in report:
    exp5__apa__anova__PROP.FAM.HIT <- papaja:::apa_print.afex_aov(exp5__anova__PROP.FAM.HIT)
    exp5__apa__anova__PROP.FAM.HIT__stim.format.main.effect <- 
      exp5__apa__anova__PROP.FAM.HIT$full$stim_format %>% str_extract("^(?:[^\\,]*\\,){3}([^\\,]*)")
#---------------------------------------------------------------------------------------------------------------#
#   Run post-hoc contrasts                                                                                      
#---------------------------------------------------------------------------------------------------------------#
##  Stimuli format:
    exp5__anova__PROP.FAM.HIT__stim.format.means <- emmeans(exp5__anova__PROP.FAM.HIT, ~ stim_format)
##  Planned contrasts:    
    exp5__anova__PROP.FAM.HIT__planned_PROP.FAM.HITontrasts <- emmeans(exp5__anova__PROP.FAM.HIT, 
                                                                       list(~ stim_format), 
                                                                       contr = planned_contrasts,
                                                                       adjust = "bonferroni")
#---------------------------------------------------------------------------------------------------------------#
#   Format results for use in report:                                                                           
#---------------------------------------------------------------------------------------------------------------#
    exp5__apa__anova__PROP.FAM.HIT__stim.format.means <-     ##  All means:
        papaja:::apa_print.emmGrid(exp5__anova__PROP.FAM.HIT__stim.format.means)
    exp5__apa__anova__PROP.FAM.HIT__grey.word.mean <-        ##  Grey words mean:
        exp5__apa__anova__PROP.FAM.HIT__stim.format.means$estimate$Greywords %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.FAM.HIT__dist.word.mean <-        ##  Distinctive words mean:
        exp5__apa__anova__PROP.FAM.HIT__stim.format.means$estimate$Distinctivewords %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.FAM.HIT__grey.drawing.mean <-     ##  Grey drawings mean:
        exp5__apa__anova__PROP.FAM.HIT__stim.format.means$estimate$Greydrawings %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.FAM.HIT__PROP.FAM.HITolour.drawing.mean <-   ##  Colour drawings mean:
        exp5__apa__anova__PROP.FAM.HIT__stim.format.means$estimate$Colourdrawings %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.FAM.HIT__grey.photo.mean <-       ##  Grey photos mean:
        exp5__apa__anova__PROP.FAM.HIT__stim.format.means$estimate$Greyphotos %>% str_remove("\\,.*")    
     exp5__apa__anova__PROP.FAM.HIT__PROP.FAM.HITolour.photo.mean <-    ##  Colour photos mean:
        exp5__apa__anova__PROP.FAM.HIT__stim.format.means$estimate$Colourphotos %>% str_remove("\\,.*")   
    
    exp5__apa__anova__PROP.FAM.HIT__stim.format.contrasts <- 
        papaja:::apa_print.emmGrid(exp5__anova__PROP.FAM.HIT__planned_PROP.FAM.HITontrasts$` of stim_format`)
    exp5__apa__anova__PROP.FAM.HIT__dist.word.vs.grey.word <-
        exp5__apa__anova__PROP.FAM.HIT__stim.format.contrasts$statistic$DistWord_vs_GreyWord
    exp5__apa__anova__PROP.FAM.HIT__dist.word.vs.grey.drawing <-
        exp5__apa__anova__PROP.FAM.HIT__stim.format.contrasts$statistic$DistWord_vs_GreyDrawing
    exp5__apa__anova__PROP.FAM.HIT__dist.word.vs.grey.photo <-
        exp5__apa__anova__PROP.FAM.HIT__stim.format.contrasts$statistic$DistWord_vs_GreyPhoto
    exp5__apa__anova__PROP.FAM.HIT__dist.word.vs.colour.drawing <-
        exp5__apa__anova__PROP.FAM.HIT__stim.format.contrasts$statistic$DistWord_vs_PROP.FAM.HITolDrawing
    exp5__apa__anova__PROP.FAM.HIT__dist.word.vs.colour.photo <-
        exp5__apa__anova__PROP.FAM.HIT__stim.format.contrasts$statistic$DistWord_vs_PROP.FAM.HITolPhoto
```    

**Were the distinctive words actually distinctive compared to normal words?**
Distinctive words (`r exp5__apa__anova__PROP.FAM.HIT__dist.word.mean`) vs. grey words (`r exp5__apa__anova__PROP.FAM.HIT__grey.word.mean`), `r exp5__apa__anova__PROP.FAM.HIT__dist.word.vs.grey.word`. 

**Were the distinctive words close to grey drawings or photos?**
Distinctive words (`r exp5__apa__anova__PROP.FAM.HIT__dist.word.mean`) vs. grey drawings (`r exp5__apa__anova__PROP.FAM.HIT__grey.drawing.mean`), `r exp5__apa__anova__PROP.FAM.HIT__dist.word.vs.grey.drawing`. 

Distinctive words (`r exp5__apa__anova__PROP.FAM.HIT__dist.word.mean`) vs. grey photos (`r exp5__apa__anova__PROP.FAM.HIT__grey.photo.mean`), `r exp5__apa__anova__PROP.FAM.HIT__dist.word.vs.grey.photo`. 

**Were the distinctive words close to colour drawings or photos?**
Distinctive words (`r exp5__apa__anova__PROP.FAM.HIT__dist.word.mean`) vs. colour drawings (`r exp5__apa__anova__PROP.FAM.HIT__PROP.FAM.HITolour.drawing.mean`), `r exp5__apa__anova__PROP.FAM.HIT__dist.word.vs.colour.drawing`.

Distinctive words (`r exp5__apa__anova__PROP.FAM.HIT__dist.word.mean`) vs. colour photos (`r exp5__apa__anova__PROP.FAM.HIT__PROP.FAM.HITolour.photo.mean`), `r exp5__apa__anova__PROP.FAM.HIT__dist.word.vs.colour.photo`.

#### Guessing (hits)
```{r, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.show='hide'}
#################################################################################################################
##    Experiment 5 - GUESS hits:                                                                               ##
################################################################################################################# ##  Prep data for analysis:                                                 
    exp5__anova__PROP.GUESS.HIT_data <- exp5__final_data %>%
        select(id, prop_grey_word_hit_guess, prop_distinctive_word_hit_guess, prop_grey_drawing_hit_guess, 
               prop_col_drawing_hit_guess, prop_grey_photo_hit_guess, prop_col_photo_hit_guess) %>%
        rename("Grey words" = "prop_grey_word_hit_guess", 
               "Distinctive words" = "prop_distinctive_word_hit_guess", 
               "Grey drawings" = "prop_grey_drawing_hit_guess", "Colour drawings" = "prop_col_drawing_hit_guess",
               "Grey photos" = "prop_grey_photo_hit_guess", "Colour photos" = "prop_col_photo_hit_guess") %>%
        gather(key = "stim_format", value = "GUESS_hit", "Grey words", "Distinctive words", "Grey drawings", 
               "Colour drawings", "Grey photos", "Colour photos") %>%
        transform(stim_format = factor(stim_format, levels=c("Grey words", "Distinctive words", 
                                                             "Grey drawings", "Colour drawings", 
                                                             "Grey photos", "Colour photos")))
#----------------------------------------------------------------------------------------------------------------
#   Run 1-way repeated measures ANOVA:
#----------------------------------------------------------------------------------------------------------------
    exp5__anova__PROP.GUESS.HIT <- aov_ez('id', 'GUESS_hit', exp5__anova__PROP.GUESS.HIT_data, 
                                          within = "stim_format")

##  Format ANOVA main effect for use in report:
    exp5__apa__anova__PROP.GUESS.HIT <- papaja:::apa_print.afex_aov(exp5__anova__PROP.GUESS.HIT)
    exp5__apa__anova__PROP.GUESS.HIT__stim.format.main.effect <- 
        exp5__apa__anova__PROP.GUESS.HIT$full$stim_format %>% str_extract("^(?:[^\\,]*\\,){3}([^\\,]*)")
#---------------------------------------------------------------------------------------------------------------#
#   Run post-hoc contrasts                                                                                      
#---------------------------------------------------------------------------------------------------------------#
##  Stimuli format:
    exp5__anova__PROP.GUESS.HIT__stim.format.means <- emmeans(exp5__anova__PROP.GUESS.HIT, ~ stim_format)
##  Planned contrasts:    
    exp5__anova__PROP.GUESS.HIT__planned_PROP.GUESS.HITontrasts <- emmeans(exp5__anova__PROP.GUESS.HIT, 
                                                                       list(~ stim_format), 
                                                                       contr = planned_contrasts,
                                                                       adjust = "bonferroni")
#---------------------------------------------------------------------------------------------------------------#
#   Format results for use in report:                                                                           
#---------------------------------------------------------------------------------------------------------------#
    exp5__apa__anova__PROP.GUESS.HIT__stim.format.means <-     ##  All means:
        papaja:::apa_print.emmGrid(exp5__anova__PROP.GUESS.HIT__stim.format.means)
    exp5__apa__anova__PROP.GUESS.HIT__grey.word.mean <-        ##  Grey words mean:
        exp5__apa__anova__PROP.GUESS.HIT__stim.format.means$estimate$Greywords %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.GUESS.HIT__dist.word.mean <-        ##  Distinctive words mean:
        exp5__apa__anova__PROP.GUESS.HIT__stim.format.means$estimate$Distinctivewords %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.GUESS.HIT__grey.drawing.mean <-     ##  Grey drawings mean:
        exp5__apa__anova__PROP.GUESS.HIT__stim.format.means$estimate$Greydrawings %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.GUESS.HIT__PROP.GUESS.HITolour.drawing.mean <-   ##  Colour drawings mean:
        exp5__apa__anova__PROP.GUESS.HIT__stim.format.means$estimate$Colourdrawings %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.GUESS.HIT__grey.photo.mean <-       ##  Grey photos mean:
        exp5__apa__anova__PROP.GUESS.HIT__stim.format.means$estimate$Greyphotos %>% str_remove("\\,.*")    
     exp5__apa__anova__PROP.GUESS.HIT__PROP.GUESS.HITolour.photo.mean <-    ##  Colour photos mean:
        exp5__apa__anova__PROP.GUESS.HIT__stim.format.means$estimate$Colourphotos %>% str_remove("\\,.*")   
    
    exp5__apa__anova__PROP.GUESS.HIT__stim.format.contrasts <- 
        papaja:::apa_print.emmGrid(exp5__anova__PROP.GUESS.HIT__planned_PROP.GUESS.HITontrasts$` of stim_format`)
    exp5__apa__anova__PROP.GUESS.HIT__dist.word.vs.grey.word <-
        exp5__apa__anova__PROP.GUESS.HIT__stim.format.contrasts$statistic$DistWord_vs_GreyWord
    exp5__apa__anova__PROP.GUESS.HIT__dist.word.vs.grey.drawing <-
        exp5__apa__anova__PROP.GUESS.HIT__stim.format.contrasts$statistic$DistWord_vs_GreyDrawing
    exp5__apa__anova__PROP.GUESS.HIT__dist.word.vs.grey.photo <-
        exp5__apa__anova__PROP.GUESS.HIT__stim.format.contrasts$statistic$DistWord_vs_GreyPhoto
    exp5__apa__anova__PROP.GUESS.HIT__dist.word.vs.colour.drawing <-
        exp5__apa__anova__PROP.GUESS.HIT__stim.format.contrasts$statistic$DistWord_vs_PROP.GUESS.HITolDrawing
    exp5__apa__anova__PROP.GUESS.HIT__dist.word.vs.colour.photo <-
        exp5__apa__anova__PROP.GUESS.HIT__stim.format.contrasts$statistic$DistWord_vs_PROP.GUESS.HITolPhoto
```    

**Were the distinctive words actually distinctive compared to normal words?**
Distinctive words (`r exp5__apa__anova__PROP.GUESS.HIT__dist.word.mean`) vs. grey words (`r exp5__apa__anova__PROP.GUESS.HIT__grey.word.mean`), `r exp5__apa__anova__PROP.GUESS.HIT__dist.word.vs.grey.word`. 

**Were the distinctive words close to grey drawings or photos?**
Distinctive words (`r exp5__apa__anova__PROP.GUESS.HIT__dist.word.mean`) vs. grey drawings (`r exp5__apa__anova__PROP.GUESS.HIT__grey.drawing.mean`), `r exp5__apa__anova__PROP.GUESS.HIT__dist.word.vs.grey.drawing`. 

Distinctive words (`r exp5__apa__anova__PROP.GUESS.HIT__dist.word.mean`) vs. grey photos (`r exp5__apa__anova__PROP.GUESS.HIT__grey.photo.mean`), `r exp5__apa__anova__PROP.GUESS.HIT__dist.word.vs.grey.photo`. 

**Were the distinctive words close to colour drawings or photos?**
Distinctive words (`r exp5__apa__anova__PROP.GUESS.HIT__dist.word.mean`) vs. colour drawings (`r exp5__apa__anova__PROP.GUESS.HIT__PROP.GUESS.HITolour.drawing.mean`), `r exp5__apa__anova__PROP.GUESS.HIT__dist.word.vs.colour.drawing`.

Distinctive words (`r exp5__apa__anova__PROP.GUESS.HIT__dist.word.mean`) vs. colour photos (`r exp5__apa__anova__PROP.GUESS.HIT__PROP.GUESS.HITolour.photo.mean`), `r exp5__apa__anova__PROP.GUESS.HIT__dist.word.vs.colour.photo`.

### FAs assigned Recollection, Familiarity, and Guessing
#### Recollection (FAs)
```{r, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.show='hide'}
#################################################################################################################
##    Experiment 5 - GUESS FAs:                                                                               ##
################################################################################################################# 
##  Prep data for analysis:                                                 
    exp5__anova__PROP.REC.FA_data <- exp5__final_data %>%
        select(id, prop_grey_word_FA_rec, prop_distinctive_word_FA_rec, prop_grey_drawing_FA_rec, 
               prop_col_drawing_FA_rec, prop_grey_photo_FA_rec, prop_col_photo_FA_rec) %>%
        rename("Grey words" = "prop_grey_word_FA_rec", 
               "Distinctive words" = "prop_distinctive_word_FA_rec", 
               "Grey drawings" = "prop_grey_drawing_FA_rec", "Colour drawings" = "prop_col_drawing_FA_rec",
               "Grey photos" = "prop_grey_photo_FA_rec", "Colour photos" = "prop_col_photo_FA_rec") %>%
        gather(key = "stim_format", value = "rec_FA", "Grey words", "Distinctive words", "Grey drawings", 
               "Colour drawings", "Grey photos", "Colour photos") %>%
        transform(stim_format = factor(stim_format, levels=c("Grey words", "Distinctive words", 
                                                             "Grey drawings", "Colour drawings", 
                                                             "Grey photos", "Colour photos")))
#----------------------------------------------------------------------------------------------------------------
#   Run 1-way repeated measures ANOVA:
#----------------------------------------------------------------------------------------------------------------
    exp5__anova__PROP.REC.FA <- aov_ez('id', 'rec_FA', exp5__anova__PROP.REC.FA_data, 
                                          within = "stim_format")

##  Format ANOVA main effect for use in report:
    exp5__apa__anova__PROP.REC.FA <- papaja:::apa_print.afex_aov(exp5__anova__PROP.REC.FA)
    exp5__apa__anova__PROP.REC.FA__stim.format.main.effect <- 
        exp5__apa__anova__PROP.REC.FA$full$stim_format %>% str_extract("^(?:[^\\,]*\\,){3}([^\\,]*)")
#---------------------------------------------------------------------------------------------------------------#
#   Run post-hoc contrasts                                                                                      
#--------------------------------------------------------------------------------------------------------------#
##  Stimuli format:
    exp5__anova__PROP.REC.FA__stim.format.means <- emmeans(exp5__anova__PROP.REC.FA, ~ stim_format)
##  Planned contrasts:    
    exp5__anova__PROP.REC.FA__planned_PROP.REC.contrasts <- emmeans(exp5__anova__PROP.REC.FA, 
                                                                       list(~ stim_format), 
                                                                       contr = planned_contrasts,
                                                                       adjust = "bonferroni")
#---------------------------------------------------------------------------------------------------------------#
#   Format results for use in report:                                                                           
#---------------------------------------------------------------------------------------------------------------#
    exp5__apa__anova__PROP.REC.FA__stim.format.means <-     ##  All means:
        papaja:::apa_print.emmGrid(exp5__anova__PROP.REC.FA__stim.format.means)
    exp5__apa__anova__PROP.REC.FA__grey.word.mean <-        ##  Grey words mean:
        exp5__apa__anova__PROP.REC.FA__stim.format.means$estimate$Greywords %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.REC.FA__dist.word.mean <-        ##  Distinctive words mean:
        exp5__apa__anova__PROP.REC.FA__stim.format.means$estimate$Distinctivewords %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.REC.FA__grey.drawing.mean <-     ##  Grey drawings mean:
        exp5__apa__anova__PROP.REC.FA__stim.format.means$estimate$Greydrawings %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.REC.FA__PROP.REC.FAolour.drawing.mean <-   ##  Colour drawings mean:
        exp5__apa__anova__PROP.REC.FA__stim.format.means$estimate$Colourdrawings %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.REC.FA__grey.photo.mean <-       ##  Grey photos mean:
        exp5__apa__anova__PROP.REC.FA__stim.format.means$estimate$Greyphotos %>% str_remove("\\,.*")    
     exp5__apa__anova__PROP.REC.FA__PROP.REC.FAolour.photo.mean <-    ##  Colour photos mean:
        exp5__apa__anova__PROP.REC.FA__stim.format.means$estimate$Colourphotos %>% str_remove("\\,.*")   
    
    exp5__apa__anova__PROP.REC.FA__stim.format.contrasts <- 
        papaja:::apa_print.emmGrid(exp5__anova__PROP.REC.FA__planned_PROP.REC.contrasts$` of stim_format`)
    exp5__apa__anova__PROP.REC.FA__dist.word.vs.grey.word <-
        exp5__apa__anova__PROP.REC.FA__stim.format.contrasts$statistic$DistWord_vs_GreyWord
    exp5__apa__anova__PROP.REC.FA__dist.word.vs.grey.drawing <-
        exp5__apa__anova__PROP.REC.FA__stim.format.contrasts$statistic$DistWord_vs_GreyDrawing
    exp5__apa__anova__PROP.REC.FA__dist.word.vs.grey.photo <-
        exp5__apa__anova__PROP.REC.FA__stim.format.contrasts$statistic$DistWord_vs_GreyPhoto
    exp5__apa__anova__PROP.REC.FA__dist.word.vs.colour.drawing <-
        exp5__apa__anova__PROP.REC.FA__stim.format.contrasts$statistic$DistWord_vs_ColDrawing
    exp5__apa__anova__PROP.REC.FA__dist.word.vs.colour.photo <-
        exp5__apa__anova__PROP.REC.FA__stim.format.contrasts$statistic$DistWord_vs_ColPhoto
```    

**Were the distinctive words actually distinctive compared to normal words?**
Distinctive words (`r exp5__apa__anova__PROP.REC.FA__dist.word.mean`) vs. grey words (`r exp5__apa__anova__PROP.REC.FA__grey.word.mean`), `r exp5__apa__anova__PROP.REC.FA__dist.word.vs.grey.word`. 

**Were the distinctive words close to grey drawings or photos?**
Distinctive words (`r exp5__apa__anova__PROP.REC.FA__dist.word.mean`) vs. grey drawings (`r exp5__apa__anova__PROP.REC.FA__grey.drawing.mean`), `r exp5__apa__anova__PROP.REC.FA__dist.word.vs.grey.drawing`. 

Distinctive words (`r exp5__apa__anova__PROP.REC.FA__dist.word.mean`) vs. grey photos (`r exp5__apa__anova__PROP.REC.FA__grey.photo.mean`), `r exp5__apa__anova__PROP.REC.FA__dist.word.vs.grey.photo`. 

**Were the distinctive words close to colour drawings or photos?**
Distinctive words (`r exp5__apa__anova__PROP.REC.FA__dist.word.mean`) vs. colour drawings (`r exp5__apa__anova__PROP.REC.FA__PROP.REC.FAolour.drawing.mean`), `r exp5__apa__anova__PROP.REC.FA__dist.word.vs.colour.drawing`.

Distinctive words (`r exp5__apa__anova__PROP.REC.FA__dist.word.mean`) vs. colour photos (`r exp5__apa__anova__PROP.REC.FA__PROP.REC.FAolour.photo.mean`), `r exp5__apa__anova__PROP.REC.FA__dist.word.vs.colour.photo`.

#### Familiarity (FAs)
```{r, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.show='hide'}
#################################################################################################################
##    Experiment 5 - GUESS FAs:                                                                               ##
################################################################################################################# 
##  Prep data for analysis:                                                 
    exp5__anova__PROP.FAM.FA_data <- exp5__final_data %>%
        select(id, prop_grey_word_FA_fam, prop_distinctive_word_FA_fam, prop_grey_drawing_FA_fam, 
               prop_col_drawing_FA_fam, prop_grey_photo_FA_fam, prop_col_photo_FA_fam) %>%
        rename("Grey words" = "prop_grey_word_FA_fam", 
               "Distinctive words" = "prop_distinctive_word_FA_fam", 
               "Grey drawings" = "prop_grey_drawing_FA_fam", "Colour drawings" = "prop_col_drawing_FA_fam",
               "Grey photos" = "prop_grey_photo_FA_fam", "Colour photos" = "prop_col_photo_FA_fam") %>%
        gather(key = "stim_format", value = "fam_FA", "Grey words", "Distinctive words", "Grey drawings", 
               "Colour drawings", "Grey photos", "Colour photos") %>%
        transform(stim_format = factor(stim_format, levels=c("Grey words", "Distinctive words", 
                                                             "Grey drawings", "Colour drawings", 
                                                             "Grey photos", "Colour photos")))
#----------------------------------------------------------------------------------------------------------------
#   Run 1-way repeated measures ANOVA:
#----------------------------------------------------------------------------------------------------------------
    exp5__anova__PROP.FAM.FA <- aov_ez('id', 'fam_FA', exp5__anova__PROP.FAM.FA_data, 
                                          within = "stim_format")

##  Format ANOVA main effect for use in report:
    exp5__apa__anova__PROP.FAM.FA <- papaja:::apa_print.afex_aov(exp5__anova__PROP.FAM.FA)
    exp5__apa__anova__PROP.FAM.FA__stim.format.main.effect <- 
        exp5__apa__anova__PROP.FAM.FA$full$stim_format %>% str_extract("^(?:[^\\,]*\\,){3}([^\\,]*)")
#---------------------------------------------------------------------------------------------------------------#
#   Run post-hoc contrasts                                                                                      
#--------------------------------------------------------------------------------------------------------------#
##  Stimuli format:
    exp5__anova__PROP.FAM.FA__stim.format.means <- emmeans(exp5__anova__PROP.FAM.FA, ~ stim_format)
##  Planned contrasts:    
    exp5__anova__PROP.FAM.FA__planned_PROP.FAM.contrasts <- emmeans(exp5__anova__PROP.FAM.FA, 
                                                                       list(~ stim_format), 
                                                                       contr = planned_contrasts,
                                                                       adjust = "bonferroni")
#---------------------------------------------------------------------------------------------------------------#
#   Format results for use in report:                                                                           
#---------------------------------------------------------------------------------------------------------------#
    exp5__apa__anova__PROP.FAM.FA__stim.format.means <-     ##  All means:
        papaja:::apa_print.emmGrid(exp5__anova__PROP.FAM.FA__stim.format.means)
    exp5__apa__anova__PROP.FAM.FA__grey.word.mean <-        ##  Grey words mean:
        exp5__apa__anova__PROP.FAM.FA__stim.format.means$estimate$Greywords %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.FAM.FA__dist.word.mean <-        ##  Distinctive words mean:
        exp5__apa__anova__PROP.FAM.FA__stim.format.means$estimate$Distinctivewords %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.FAM.FA__grey.drawing.mean <-     ##  Grey drawings mean:
        exp5__apa__anova__PROP.FAM.FA__stim.format.means$estimate$Greydrawings %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.FAM.FA__PROP.FAM.FAolour.drawing.mean <-   ##  Colour drawings mean:
        exp5__apa__anova__PROP.FAM.FA__stim.format.means$estimate$Colourdrawings %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.FAM.FA__grey.photo.mean <-       ##  Grey photos mean:
        exp5__apa__anova__PROP.FAM.FA__stim.format.means$estimate$Greyphotos %>% str_remove("\\,.*")    
     exp5__apa__anova__PROP.FAM.FA__PROP.FAM.FAolour.photo.mean <-    ##  Colour photos mean:
        exp5__apa__anova__PROP.FAM.FA__stim.format.means$estimate$Colourphotos %>% str_remove("\\,.*")   
    
    exp5__apa__anova__PROP.FAM.FA__stim.format.contrasts <- 
        papaja:::apa_print.emmGrid(exp5__anova__PROP.FAM.FA__planned_PROP.FAM.contrasts$` of stim_format`)
    exp5__apa__anova__PROP.FAM.FA__dist.word.vs.grey.word <-
        exp5__apa__anova__PROP.FAM.FA__stim.format.contrasts$statistic$DistWord_vs_GreyWord
    exp5__apa__anova__PROP.FAM.FA__dist.word.vs.grey.drawing <-
        exp5__apa__anova__PROP.FAM.FA__stim.format.contrasts$statistic$DistWord_vs_GreyDrawing
    exp5__apa__anova__PROP.FAM.FA__dist.word.vs.grey.photo <-
        exp5__apa__anova__PROP.FAM.FA__stim.format.contrasts$statistic$DistWord_vs_GreyPhoto
    exp5__apa__anova__PROP.FAM.FA__dist.word.vs.colour.drawing <-
        exp5__apa__anova__PROP.FAM.FA__stim.format.contrasts$statistic$DistWord_vs_ColDrawing
    exp5__apa__anova__PROP.FAM.FA__dist.word.vs.colour.photo <-
        exp5__apa__anova__PROP.FAM.FA__stim.format.contrasts$statistic$DistWord_vs_ColPhoto
```    

**Were the distinctive words actually distinctive compared to normal words?**
Distinctive words (`r exp5__apa__anova__PROP.FAM.FA__dist.word.mean`) vs. grey words (`r exp5__apa__anova__PROP.FAM.FA__grey.word.mean`), `r exp5__apa__anova__PROP.FAM.FA__dist.word.vs.grey.word`. 

**Were the distinctive words close to grey drawings or photos?**
Distinctive words (`r exp5__apa__anova__PROP.FAM.FA__dist.word.mean`) vs. grey drawings (`r exp5__apa__anova__PROP.FAM.FA__grey.drawing.mean`), `r exp5__apa__anova__PROP.FAM.FA__dist.word.vs.grey.drawing`. 

Distinctive words (`r exp5__apa__anova__PROP.FAM.FA__dist.word.mean`) vs. grey photos (`r exp5__apa__anova__PROP.FAM.FA__grey.photo.mean`), `r exp5__apa__anova__PROP.FAM.FA__dist.word.vs.grey.photo`. 

**Were the distinctive words close to colour drawings or photos?**
Distinctive words (`r exp5__apa__anova__PROP.FAM.FA__dist.word.mean`) vs. colour drawings (`r exp5__apa__anova__PROP.FAM.FA__PROP.FAM.FAolour.drawing.mean`), `r exp5__apa__anova__PROP.FAM.FA__dist.word.vs.colour.drawing`.

Distinctive words (`r exp5__apa__anova__PROP.FAM.FA__dist.word.mean`) vs. colour photos (`r exp5__apa__anova__PROP.FAM.FA__PROP.FAM.FAolour.photo.mean`), `r exp5__apa__anova__PROP.FAM.FA__dist.word.vs.colour.photo`.

#### Guessing (FAs)
```{r, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.show='hide'}
#################################################################################################################
##    Experiment 5 - GUESS FAs:                                                                               ##
################################################################################################################# 
##  Prep data for analysis:                                                 
    exp5__anova__PROP.GUESS.FA_data <- exp5__final_data %>%
        select(id, prop_grey_word_FA_guess, prop_distinctive_word_FA_guess, prop_grey_drawing_FA_guess, 
               prop_col_drawing_FA_guess, prop_grey_photo_FA_guess, prop_col_photo_FA_guess) %>%
        rename("Grey words" = "prop_grey_word_FA_guess", 
               "Distinctive words" = "prop_distinctive_word_FA_guess", 
               "Grey drawings" = "prop_grey_drawing_FA_guess", "Colour drawings" = "prop_col_drawing_FA_guess",
               "Grey photos" = "prop_grey_photo_FA_guess", "Colour photos" = "prop_col_photo_FA_guess") %>%
        gather(key = "stim_format", value = "guess_FA", "Grey words", "Distinctive words", "Grey drawings", 
               "Colour drawings", "Grey photos", "Colour photos") %>%
        transform(stim_format = factor(stim_format, levels=c("Grey words", "Distinctive words", 
                                                             "Grey drawings", "Colour drawings", 
                                                             "Grey photos", "Colour photos")))
#----------------------------------------------------------------------------------------------------------------
#   Run 1-way repeated measures ANOVA:
#----------------------------------------------------------------------------------------------------------------
    exp5__anova__PROP.GUESS.FA <- aov_ez('id', 'guess_FA', exp5__anova__PROP.GUESS.FA_data, 
                                          within = "stim_format")

##  Format ANOVA main effect for use in report:
    exp5__apa__anova__PROP.GUESS.FA <- papaja:::apa_print.afex_aov(exp5__anova__PROP.GUESS.FA)
    exp5__apa__anova__PROP.GUESS.FA__stim.format.main.effect <- 
        exp5__apa__anova__PROP.GUESS.FA$full$stim_format %>% str_extract("^(?:[^\\,]*\\,){3}([^\\,]*)")
#---------------------------------------------------------------------------------------------------------------#
#   Run post-hoc contrasts                                                                                      
#--------------------------------------------------------------------------------------------------------------#
##  Stimuli format:
    exp5__anova__PROP.GUESS.FA__stim.format.means <- emmeans(exp5__anova__PROP.GUESS.FA, ~ stim_format)
##  Planned contrasts:    
    exp5__anova__PROP.GUESS.FA__planned_PROP.GUESS.contrasts <- emmeans(exp5__anova__PROP.GUESS.FA, 
                                                                       list(~ stim_format), 
                                                                       contr = planned_contrasts,
                                                                       adjust = "bonferroni")
#---------------------------------------------------------------------------------------------------------------#
#   Format results for use in report:                                                                           
#---------------------------------------------------------------------------------------------------------------#
    exp5__apa__anova__PROP.GUESS.FA__stim.format.means <-                 ##  All means:
        papaja:::apa_print.emmGrid(exp5__anova__PROP.GUESS.FA__stim.format.means)
    exp5__apa__anova__PROP.GUESS.FA__grey.word.mean <-                    ##  Grey words mean:
        exp5__apa__anova__PROP.GUESS.FA__stim.format.means$estimate$Greywords %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.GUESS.FA__dist.word.mean <-                    ##  Distinctive words mean:
        exp5__apa__anova__PROP.GUESS.FA__stim.format.means$estimate$Distinctivewords %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.GUESS.FA__grey.drawing.mean <-                 ##  Grey drawings mean:
        exp5__apa__anova__PROP.GUESS.FA__stim.format.means$estimate$Greydrawings %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.GUESS.FA__PROP.GUESS.FAolour.drawing.mean <-   ##  Colour drawings mean:
        exp5__apa__anova__PROP.GUESS.FA__stim.format.means$estimate$Colourdrawings %>% str_remove("\\,.*")
    exp5__apa__anova__PROP.GUESS.FA__grey.photo.mean <-                   ##  Grey photos mean:
        exp5__apa__anova__PROP.GUESS.FA__stim.format.means$estimate$Greyphotos %>% str_remove("\\,.*")    
     exp5__apa__anova__PROP.GUESS.FA__PROP.GUESS.FAolour.photo.mean <-    ##  Colour photos mean:
        exp5__apa__anova__PROP.GUESS.FA__stim.format.means$estimate$Colourphotos %>% str_remove("\\,.*")   
    
    exp5__apa__anova__PROP.GUESS.FA__stim.format.contrasts <- 
        papaja:::apa_print.emmGrid(exp5__anova__PROP.GUESS.FA__planned_PROP.GUESS.contrasts$` of stim_format`)
    exp5__apa__anova__PROP.GUESS.FA__dist.word.vs.grey.word <-
        exp5__apa__anova__PROP.GUESS.FA__stim.format.contrasts$statistic$DistWord_vs_GreyWord
    exp5__apa__anova__PROP.GUESS.FA__dist.word.vs.grey.drawing <-
        exp5__apa__anova__PROP.GUESS.FA__stim.format.contrasts$statistic$DistWord_vs_GreyDrawing
    exp5__apa__anova__PROP.GUESS.FA__dist.word.vs.grey.photo <-
        exp5__apa__anova__PROP.GUESS.FA__stim.format.contrasts$statistic$DistWord_vs_GreyPhoto
    exp5__apa__anova__PROP.GUESS.FA__dist.word.vs.colour.drawing <-
        exp5__apa__anova__PROP.GUESS.FA__stim.format.contrasts$statistic$DistWord_vs_ColDrawing
    exp5__apa__anova__PROP.GUESS.FA__dist.word.vs.colour.photo <-
        exp5__apa__anova__PROP.GUESS.FA__stim.format.contrasts$statistic$DistWord_vs_ColPhoto
```    

**Were the distinctive words actually distinctive compared to normal words?**
Distinctive words (`r exp5__apa__anova__PROP.GUESS.FA__dist.word.mean`) vs. grey words (`r exp5__apa__anova__PROP.GUESS.FA__grey.word.mean`), `r exp5__apa__anova__PROP.GUESS.FA__dist.word.vs.grey.word`. 

**Were the distinctive words close to grey drawings or photos?**
Distinctive words (`r exp5__apa__anova__PROP.GUESS.FA__dist.word.mean`) vs. grey drawings (`r exp5__apa__anova__PROP.GUESS.FA__grey.drawing.mean`), `r exp5__apa__anova__PROP.GUESS.FA__dist.word.vs.grey.drawing`. 

Distinctive words (`r exp5__apa__anova__PROP.GUESS.FA__dist.word.mean`) vs. grey photos (`r exp5__apa__anova__PROP.GUESS.FA__grey.photo.mean`), `r exp5__apa__anova__PROP.GUESS.FA__dist.word.vs.grey.photo`. 

**Were the distinctive words close to colour drawings or photos?**
Distinctive words (`r exp5__apa__anova__PROP.GUESS.FA__dist.word.mean`) vs. colour drawings (`r exp5__apa__anova__PROP.GUESS.FA__PROP.GUESS.FAolour.drawing.mean`), `r exp5__apa__anova__PROP.GUESS.FA__dist.word.vs.colour.drawing`.

Distinctive words (`r exp5__apa__anova__PROP.GUESS.FA__dist.word.mean`) vs. colour photos (`r exp5__apa__anova__PROP.GUESS.FA__PROP.GUESS.FAolour.photo.mean`), `r exp5__apa__anova__PROP.GUESS.FA__dist.word.vs.colour.photo`.


\newpage

One-way repeated measures ANOVAs (6 x stim types).  
Followed-up with planned t-tests (Bonferroni correction for 5 tests):

- DistWord__vs__GreyWord (more distinctive than normal words?);
- DistWord__vs__GreyDrawing and DistWord__vs__GreyPhoto (as distinctive as grey drawings/photos?);
- DistWord__vs__ColDrawing and DistWord__vs__ColPhoto (as distinctive as colour drawings/photos?).

### Are the distinctive words actually more distinctive than regular words?

```{r, echo=FALSE}
exp5__summary <- tribble(
  ~"Variable", ~"GreyWords",  ~"DistinctiveWords", ~"Result", ~"Supports?",
    "Overall hits", 
                  exp5__apa__anova__PROP.HITS__grey.word.mean, 
                  exp5__apa__anova__PROP.HITS__dist.word.mean, 
                  exp5__apa__anova__PROP.HITS__dist.word.vs.grey.word,
                  "No",
    "Overall FAs",  
                  exp5__apa__anova__PROP.FA__grey.word.mean,
                  exp5__apa__anova__PROP.FA__dist.word.mean,
                  exp5__apa__anova__PROP.FA__dist.word.vs.grey.word,
                  "Yes",
    "Overall Recognition", 
                  exp5__apa__anova__PROP.RECOG__grey.word.mean,
                  exp5__apa__anova__PROP.RECOG__dist.word.mean,
                  exp5__apa__anova__PROP.RECOG__dist.word.vs.grey.word,
                  "Yes",
    "d'",
                  exp5__apa__anova__D.PRIME__grey.word.mean,
                  exp5__apa__anova__D.PRIME__dist.word.mean,
                  exp5__apa__anova__D.PRIME__dist.word.vs.grey.word,
                  "Yes - facilitated better discrimination between hits and FAs",
    "c",
                  exp5__apa__anova__C__grey.word.mean,
                  exp5__apa__anova__C__dist.word.mean,
                  exp5__apa__anova__C__dist.word.vs.grey.word,
                  "Not sure",
    "Rec hits",
                  exp5__apa__anova__PROP.REC.HIT__grey.word.mean,
                  exp5__apa__anova__PROP.REC.HIT__dist.word.mean,
                  exp5__apa__anova__PROP.REC.HIT__dist.word.vs.grey.word,
                  "Yes",
    "Fam hits",
                  exp5__apa__anova__PROP.FAM.HIT__grey.word.mean,
                  exp5__apa__anova__PROP.FAM.HIT__dist.word.mean,
                  exp5__apa__anova__PROP.FAM.HIT__dist.word.vs.grey.word,
                  "Yes",
    "Guess hits",
                  exp5__apa__anova__PROP.GUESS.HIT__grey.word.mean,
                  exp5__apa__anova__PROP.GUESS.HIT__dist.word.mean,
                  exp5__apa__anova__PROP.GUESS.HIT__dist.word.vs.grey.word,
                  "",
    "Rec FAs",
                  exp5__apa__anova__PROP.REC.FA__grey.word.mean,
                  exp5__apa__anova__PROP.REC.FA__dist.word.mean,
                  exp5__apa__anova__PROP.REC.FA__dist.word.vs.grey.word,
                  "Almost",
    "Fam FAs",
                  exp5__apa__anova__PROP.FAM.FA__grey.word.mean,
                  exp5__apa__anova__PROP.FAM.FA__dist.word.mean,
                  exp5__apa__anova__PROP.FAM.FA__dist.word.vs.grey.word,
                  "",
    "Guess FAs",
                  exp5__apa__anova__PROP.GUESS.FA__grey.word.mean,
                  exp5__apa__anova__PROP.GUESS.FA__dist.word.mean,
                  exp5__apa__anova__PROP.GUESS.FA__dist.word.vs.grey.word,
                  ""
)
```

```{r, echo=FALSE, cache=FALSE}
exp5__summary %>%
      kable("latex", booktabs = T) %>%
        kable_styling(latex_options = c("hold_position", "scale_down")) %>%
        column_spec(1, width = "4cm")
```
We might have expected more Overall Hits.  
But most of the other results suggest distinctive words are better recognised. 

Less likely to respond Old to distinctive words

### Was recognition of distinctive words better than grey drawings?
```{r, echo=FALSE}
exp5__summary2 <- tribble(
  ~"Variable", ~"DistinctiveWords",  ~"GreyDrawings", ~"Result", ~"Supports?",
    "Overall hits", 
                  exp5__apa__anova__PROP.HITS__dist.word.mean, 
                  exp5__apa__anova__PROP.HITS__grey.drawing.mean, 
                  exp5__apa__anova__PROP.HITS__dist.word.vs.grey.word,
                  "Almost (same)",
    "Overall FAs",  
                  exp5__apa__anova__PROP.FA__dist.word.mean,
                  exp5__apa__anova__PROP.FA__grey.drawing.mean,
                  exp5__apa__anova__PROP.FA__dist.word.vs.grey.word,
                  "Yes (better)",
    "Overall Recognition", 
                  exp5__apa__anova__PROP.RECOG__dist.word.mean,
                  exp5__apa__anova__PROP.RECOG__grey.drawing.mean,
                  exp5__apa__anova__PROP.RECOG__dist.word.vs.grey.word,
                  "No",
    "d'",
                  exp5__apa__anova__D.PRIME__dist.word.mean,
                  exp5__apa__anova__D.PRIME__grey.drawing.mean,
                  exp5__apa__anova__D.PRIME__dist.word.vs.grey.word,
                  "No",
    "c",
                  exp5__apa__anova__C__dist.word.mean,
                  exp5__apa__anova__C__grey.drawing.mean,
                  exp5__apa__anova__C__dist.word.vs.grey.word,
                  "Not sure",
    "Rec hits",
                  exp5__apa__anova__PROP.REC.HIT__dist.word.mean,
                  exp5__apa__anova__PROP.REC.HIT__grey.drawing.mean,
                  exp5__apa__anova__PROP.REC.HIT__dist.word.vs.grey.word,
                  "No",
    "Fam hits",
                  exp5__apa__anova__PROP.FAM.HIT__dist.word.mean,
                  exp5__apa__anova__PROP.FAM.HIT__grey.drawing.mean,
                  exp5__apa__anova__PROP.FAM.HIT__dist.word.vs.grey.word,
                  "No",
    "Guess hits",
                  exp5__apa__anova__PROP.GUESS.HIT__dist.word.mean,
                  exp5__apa__anova__PROP.GUESS.HIT__grey.drawing.mean,
                  exp5__apa__anova__PROP.GUESS.HIT__dist.word.vs.grey.word,
                  "",
    "Rec FAs",
                  exp5__apa__anova__PROP.REC.FA__dist.word.mean,
                  exp5__apa__anova__PROP.REC.FA__grey.drawing.mean,
                  exp5__apa__anova__PROP.REC.FA__dist.word.vs.grey.word,
                  "Almost",
    "Fam FAs",
                  exp5__apa__anova__PROP.FAM.FA__dist.word.mean,
                  exp5__apa__anova__PROP.FAM.FA__grey.drawing.mean,
                  exp5__apa__anova__PROP.FAM.FA__dist.word.vs.grey.word,
                  "",
    "Guess FAs",
                  exp5__apa__anova__PROP.GUESS.FA__dist.word.mean,
                  exp5__apa__anova__PROP.GUESS.FA__grey.drawing.mean,
                  exp5__apa__anova__PROP.GUESS.FA__dist.word.vs.grey.word,
                  ""
)
```

```{r, echo=FALSE, cache=FALSE}
exp5__summary2 %>%
      kable("latex", booktabs = T) %>%
        kable_styling(latex_options = c("hold_position", "scale_down")) %>%
        column_spec(1, width = "4cm")
```


Less likely to respond Old to distinctive words







